\documentclass[acmlarge,nonacm,screen]{acmart}

% --- URL line-breaking: allow url to break at slashes and hyphens
% (mitigates overfull \hbox warnings on long DOI / GitHub / arXiv URLs).
\PassOptionsToPackage{hyphens}{url}

\usepackage{booktabs}
\usepackage{listings}
\usepackage{xcolor}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{multirow}
\usepackage{algorithm}
\usepackage{algpseudocode}  % ACM-recommended algorithmicx variant
% Provide an explicit \Return so we can write `\State \Return ...`
\algrenewcommand\algorithmicrequire{\textbf{Require:}}
\algrenewcommand\algorithmicensure{\textbf{Ensure:}}
\usepackage{tikz}
\usetikzlibrary{shapes,arrows,positioning,fit,arrows.meta,calc}

% Note: an earlier revision tried to use tikz `external` library to cache
% rendered figures into tikz-cache/. That approach is incompatible with
% this manuscript because lstlisting blocks contain Chinese characters
% (e.g. \"// 计算个人所得税\" in the N6 example, ~line 3273), and the
% external library re-runs main.tex in a clean subprocess that does not
% inherit acmart's utf8 input handling, causing
% \"Invalid UTF-8 byte sequence\" fatal errors during cache generation.
% We therefore rely on direct in-document TikZ rendering, which works
% identically on local pdflatex and on Overleaf without further setup.
% Float control: [H] forces a table/figure to its exact source location,
% preventing tables from being re-floated past adjacent lstlistings (which
% are not floats), which would otherwise scramble the document order.
\usepackage{float}
% Soft fallback for the rest of the document: \FloatBarrier prevents
% any pending floats from leaking past it.
\usepackage{placeins}

% --- Typographic refinement: microtype reduces overfull \hbox warnings
% via character protrusion and font expansion. Font expansion requires
% a scalable Type-1 font set; cm-super (TeX Live package) provides this
% for the default Computer Modern family used by acmart, and Overleaf
% ships cm-super by default. If you ever see "pdfTeX error: auto
% expansion is only possible with scalable fonts" on a stripped-down
% TeX install, run `sudo tlmgr install cm-super`.
\usepackage{microtype}

% --- tabularx: provides the X column type that auto-wraps to fill
% the remaining width. Used by tables whose right column carries
% long descriptive prose (e.g. tab:tech-stack), which would
% otherwise overflow a fixed `l` column on the narrow ACM
% acmlarge single-column layout.
\usepackage{tabularx}
% Make X-columns ragged-right so they break on word boundaries
% rather than emitting underfull \hbox warnings; \arraybackslash
% restores `\\` as the row terminator inside X columns.
\newcolumntype{Y}{>{\raggedright\arraybackslash}X}

% --- Loosen line-breaking on long inline strings (paths, identifiers).
% \emergencystretch lets TeX stretch a line by up to 3em rather than
% emitting an overfull \hbox warning on hard-to-break paragraphs.
\setlength{\emergencystretch}{3em}
% Tolerate slightly looser inter-word spacing rather than over-running
% the right margin (ACM template runs a tight 1-column layout).
\tolerance=2000
\hbadness=2000

% --- Table of contents depth: only \section and \subsection are listed.
% acmart's default tocdepth is 3, which would expose all of the
% \subsubsection rows used to break long subsections (e.g. the 17
% subsubsections under Section~7 Experimental Evaluation alone) and
% inflate the TOC to 3--4 pages. Capping at depth 2 cuts the TOC by
% ~40% while preserving every section and subsection title; the
% subsubsection numbering and headings still appear in the body of the
% paper, only the front-matter listing is shortened.
%
% Implementation note: acmart redefines \l@subsection / \l@subsubsection
% to call \@tocline directly, bypassing LaTeX's standard \ifnum > tocdepth
% guard --- so plain \setcounter{tocdepth}{2} is silently ignored. The
% canonical fix is to redefine \l@subsubsection itself so that it ignores
% its arguments and produces no output. We must do this AFTER acmart has
% loaded (it sets its own definition in the .cls file) but BEFORE
% \maketitle runs, otherwise acmart's first-page metadata block can leak
% the [2] argument count into the running head.
\setcounter{tocdepth}{2}

\lstset{
  basicstyle=\ttfamily\small,
  breaklines=true,
  frame=single,
  language=Java,
  keywordstyle=\color{blue},
  commentstyle=\color{gray},
  stringstyle=\color{red},
  numbers=left,
  numberstyle=\tiny,
  tabsize=2,
}

\settopmatter{printacmref=false}
\renewcommand\footnotetextcopyrightpermission[1]{}
% Note: page style is left to acmart/nonacm defaults (no manual override),
% per the ACM template rule "no manual page header/footer adjustments".

\begin{document}

\title[CleanTest-Agent]{CleanTest-Agent: A Multi-Agent Skill-Orchestrated System for Unit Test Training Data Quality Assurance}

\author{Yong Yang}
\authornote{Source code, datasets, the trained Filter 3 checkpoint
  metadata, and a reproducible end-to-end notebook are released
  under the MIT license at
  \url{https://github.com/jimmy0717/cleantest-agent}; a
  pip-installable distribution is at
  \url{https://pypi.org/project/cleantest-agent/}. See
  Section~\ref{sec:availability} for the full availability
  statement.}
\affiliation{%
  \institution{Beihang University}
  \department{School of Software}
  \city{Beijing}
  \country{China}
}
\email{yang_qhd@buaa.edu.cn}

\renewcommand{\shortauthors}{Yang}

\begin{abstract}
The quality of training data directly impacts the performance of AI-based unit test generation models. Recent studies have shown that up to 43.52\% of widely-used training datasets contain noisy samples, including syntax errors, irrelevant test-focal method pairs, and low-coverage tests. While the CleanTest framework (FSE 2025 Distinguished Paper) proposed effective rule-based filtering, its implementation exists as monolithic Python scripts that are difficult to integrate into modern AI-assisted development workflows.

In this paper, we present \textbf{CleanTest-Agent}, a multi-agent skill-orchestrated system that transforms the CleanTest data cleaning pipeline into composable, reusable \textit{Agent Skills} compatible with coding assistants such as CodeBuddy~\cite{codebuddy}, Claude Code~\cite{claudecode}, and Cursor~\cite{cursor}. Our system employs a three-stage pipeline: (1)~a syntax noise filter using tree-sitter AST parsing with Aho-Corasick multi-pattern matching, (2)~a relevance filter combining AST-based method signature matching with LLM semantic judgment for borderline cases, and (3)~a coverage filter that uses ground-truth JaCoCo~\cite{jacoco} labels when available (label mode) and otherwise predicts coverage with a fine-tuned \textbf{Qwen2.5-Coder-0.5B}~\cite{hui2024qwen} regression model (model mode), replacing the CodeGPT backbone of the original CleanTest paper with a stronger and more recent open-weights small code model.

We evaluate CleanTest-Agent on the LessIsMore-FSE2025 release of Methods2Test (593{,}953 deduplicated samples for the full-scale rule-based pipeline; a 500-sample stratified subset for the four-way comparison against real DeepSeek-V4-Flash API calls). On the 500-sample subset our hybrid approach reaches F1 = 0.965, while the best pure-LLM baseline (few-shot DeepSeek-V4-Flash) reaches only F1 = 0.387; the full rule-based pipeline processes the 593{,}953 samples in under three minutes with Aho-Corasick optimisation (11.5$\times$ speedup over na\"ive string matching). For the optional Filter 3 model mode we additionally fine-tune Qwen2.5-Coder-0.5B on a stratified 80/10/10 split of \texttt{filter\_train.csv} (469{,}174 samples) on a single A800 80\,GB and report held-out MAE 0.031 (a $\approx 2.6\times$ reduction over the CodeGPT baseline reported in the original paper). These results demonstrate that systematic software design --- combining rule-based analysis, a small fine-tuned regressor, and selective LLM enhancement --- substantially outperforms pure-LLM approaches in specialised code analysis tasks.
\end{abstract}

\keywords{unit test generation, data quality, multi-agent systems, code analysis, LLM, software engineering}

\begin{CCSXML}
<ccs2012>
   <concept>
       <concept_id>10011007.10011006.10011050</concept_id>
       <concept_desc>Software and its engineering~Software testing and debugging</concept_desc>
       <concept_significance>500</concept_significance>
   </concept>
   <concept>
       <concept_id>10010147.10010178.10010187</concept_id>
       <concept_desc>Computing methodologies~Multi-agent systems</concept_desc>
       <concept_significance>300</concept_significance>
   </concept>
</ccs2012>
\end{CCSXML}

\ccsdesc[500]{Software and its engineering~Software testing and debugging}
\ccsdesc[300]{Computing methodologies~Multi-agent systems}

% Suppress subsubsection rows in the TOC. We do this here (after acmart's
% own \l@subsubsection definition has been processed by \begin{document},
% but before \maketitle / \tableofcontents) so the running head and
% page-1 metadata block render normally and only the TOC listing is
% silenced. Subsubsection headings, numbering, and \ref{} resolution in
% the body remain unaffected.
\makeatletter
\renewcommand{\l@subsubsection}[2]{}
\makeatother

\maketitle

\tableofcontents
\newpage

% ============================================================================
\section{Introduction}
\label{sec:introduction}
% ============================================================================

The advent of large language models (LLMs) has notably advanced automated unit test generation, with models such as CodeBERT~\cite{feng2020codebert}, CodeT5~\cite{wang2021codet5}, StarCoder~\cite{li2023starcoder}, and CodeLlama~\cite{roziere2023code} showing strong capabilities in generating test cases from focal methods. These models are typically fine-tuned on large-scale datasets like Methods2Test~\cite{tufano2022methods2test} and ATLAS~\cite{watson2020atlas}, which contain hundreds of thousands of focal method--test case pairs extracted from open-source Java projects.

However, the quality of these training datasets has been largely overlooked. Zhang et al.~\cite{zhang2025cleantest} recently conducted a detailed study revealing that \textbf{43.52\% of the Methods2Test dataset contains noisy samples} --- a finding that earned the FSE 2025 Distinguished Paper Award. They identified eight distinct noise types: ambiguous data types, unnecessary annotations, empty exception handling statements, missing implementation (empty functions), syntax errors, non-English literals, no relevance (irrelevant test-focal pairs), and low code coverage. Training on such noisy data degrades model performance across all evaluation metrics.

The CleanTest framework proposed by Zhang et al. provides an effective three-filter pipeline: a rule-based syntax filter, a relevance filter, and a CodeGPT-based coverage prediction filter. However, the original implementation exists as standalone Python scripts that are tightly coupled to specific file paths and data formats. This monolithic design presents several challenges:

\begin{enumerate}
    \item \textbf{Poor reusability}: The scripts cannot be easily invoked by AI coding assistants or integrated into automated workflows.
    \item \textbf{Limited extensibility}: Adding new noise types requires modifying core scripts rather than composing new modules.
    \item \textbf{No interactive feedback}: Users cannot inspect intermediate results or adjust filtering thresholds during execution.
    \item \textbf{Performance bottlenecks}: The original annotation matching uses linear scan over 21,954 patterns, making it prohibitively slow for large datasets.
\end{enumerate}

In this paper, we present \textbf{CleanTest-Agent}, a system that addresses these challenges through a multi-agent skill-orchestrated architecture. Our key contributions are:

\begin{enumerate}
    \item \textbf{Skill-based architecture}: We decompose the CleanTest pipeline into four composable Agent Skills (pipeline orchestrator, syntax filter, relevance filter, coverage filter), each following the standard \texttt{SKILL.md} protocol compatible with multiple coding assistants.

    \item \textbf{Hybrid rule-LLM approach}: We enhance the rule-based filters with selective LLM consultation for borderline cases, achieving higher accuracy while keeping costs minimal. The LLM is invoked only on relevance-borderline samples; using the original CleanTest paper's No-Relevance ratio (12.70\,\% of Methods2Test) as a conservative upper bound, this caps LLM calls at $\leq 12.7\,\%$ of the input. Under our priority-ordered pipeline the actual call rate is lower (5.03\,\% of unique samples reach Filter 2 in the full-dataset run), since annotation-flagged samples are dropped before relevance is assessed.

    \item \textbf{Aho-Corasick optimization}: We replace the na\"ive linear annotation matching with an Aho-Corasick automaton, achieving an \textbf{11.5$\times$ speedup} (30 minutes $\to$ 2.6 minutes on 593,953 samples).

    \item \textbf{Empirical evaluation}: We compare four approaches (rule-based, zero-shot LLM, few-shot LLM, hybrid) and demonstrate that our hybrid approach achieves the best F1 (0.965) while the pure LLM approach achieves only 0.387, validated with real DeepSeek-V4-Flash API calls.
\end{enumerate}

The remainder of this paper is organized as follows. Section~\ref{sec:background} reviews related work on unit test generation, data quality, LLM-based code analysis, and agent skill architectures. Section~\ref{sec:requirements} presents a requirements analysis including stakeholder analysis, use cases, functional and non-functional requirements, and a traceability matrix. Section~\ref{sec:model-driven} defines the model-driven approach and contrasts it with the pure-LLM approach. Section~\ref{sec:design} details the system design including architecture, filter specifications, and the pipeline algorithm. Section~\ref{sec:implementation} covers the implementation with technology choices, design decisions, and testing strategy. Section~\ref{sec:evaluation} presents the experimental evaluation through four research questions, including a case study on real samples and an ablation study. Section~\ref{sec:discussion} discusses findings, lessons learned, connections to course topics, and threats to validity. Section~\ref{sec:conclusion} concludes the paper and outlines future work directions. Section~\ref{sec:availability} states code, data, and reproducibility links. Appendices provide LLM prompt templates, CI/CD configuration, the full noise report, noise type examples with real Java code, a complete API reference, and skill directory structure documentation.

All artefacts described in this paper --- including the
Python package \texttt{cleantest-agent}, the four SKILL.md skill
bundles, the 36-case pytest suite, the GitHub Actions CI matrix, the
tag-driven PyPI publish workflow with sigstore signing, the curated
Filter 3 model-mode metrics, and the LaTeX sources of this paper
---  are released under the MIT license and available at
\url{https://github.com/jimmy0717/cleantest-agent}~\cite{yang2026cleantestagent}.

\subsection{Scope and Context}

This work was conducted as the final project for the \textit{Software Requirements Analysis and System Design} course at the School of Software, Beihang University. The project requirements specify:
\begin{itemize}
    \item A research report of at least 50 pages in English (ACM/IEEE template).
    \item A 10-page presentation for a 3-minute in-class talk.
    \item A reproducible, testable codebase with CI/CD.
    \item Use of an intelligent model-driven method with experimental comparison against pure-LLM approaches.
    \item If using a Code Assistant, submission of plugin or skills-level usage documentation.
\end{itemize}

CleanTest-Agent fulfills all of these requirements: it applies software requirements analysis and system design principles to a real-world problem, implements a model-driven approach with Agent Skills, provides experimental evaluation, and includes 36 test cases with GitHub Actions CI/CD.


% ============================================================================
\section{Background and Related Work}
\label{sec:background}
% ============================================================================

\subsection{Unit Test Generation}

Automated unit test generation has been one of the most active research areas in software engineering over the past two decades. We classify existing approaches into four generations, reflecting the evolution of underlying techniques.

\subsubsection{Search-Based Test Generation}

The first generation of automated test generation tools relied on metaheuristic search algorithms. \textbf{EvoSuite}~\cite{fraser2011evosuite} is the most widely-used search-based test generation tool for Java. It employs a genetic algorithm to evolve whole test suites that maximize structural coverage criteria such as branch coverage, line coverage, and mutation score. EvoSuite generates JUnit test classes with assertions derived from runtime observations. While effective for achieving high structural coverage (reported as often 70--80\% branch coverage on real-world projects in the original paper), EvoSuite-generated tests are frequently criticized for being ``unnatural'' --- they contain long sequences of API calls with minimal readability, making them difficult for developers to understand and maintain.

\textbf{Randoop}~\cite{pacheco2007randoop} takes a different approach: feedback-directed random testing. It generates random sequences of method calls, using runtime feedback to prune invalid sequences and retain those that extend coverage. Randoop is fast but produces even less readable tests than EvoSuite, and its assertion quality is limited to basic regression checks (e.g., \texttt{assertEquals} on return values observed during generation).

\subsubsection{Symbolic Execution-Based Approaches}

Tools like \textbf{Pex}~\cite{tillmann2008pex} (for .NET) and \textbf{KLEE}~\cite{cadar2008klee} (for C) use symbolic execution to systematically explore program paths. By treating inputs as symbolic variables and solving path constraints with SMT solvers, these tools can achieve near-perfect coverage on small to medium-sized programs. However, symbolic execution suffers from the \textit{path explosion problem} in complex programs with loops, recursion, or complex data structures, limiting its practical applicability to real-world Java projects.

\subsubsection{Neural Test Generation}

The third generation leverages deep learning models trained on large corpora of human-written tests. \textbf{AthenaTest}~\cite{tufano2022athenatest} was among the first to apply transformer architectures to test case generation, demonstrating that sequence-to-sequence models can learn to generate syntactically correct and semantically meaningful test methods from focal methods.

\textbf{Methods2Test}~\cite{tufano2022methods2test} introduced the largest publicly available dataset for this task: 586,468 focal methods paired with 780,944 test cases, extracted from 91,385 open-source Java projects hosted on GitHub. The dataset maps each test method to its corresponding focal method using heuristics based on naming conventions and call graphs. Tufano et al. showed that transformer models fine-tuned on Methods2Test can generate test cases that compile and pass at non-trivial rates. However, the paper did not examine the quality of the training data itself.

\textbf{ATLAS}~\cite{watson2020atlas} focused specifically on test oracle generation --- the assertion portion of test cases. Watson et al. constructed a dataset of 188,154 focal method and test case pairs from over 9,000 GitHub projects, where each test case includes only a single assert statement. ATLAS demonstrated that even the assertion component can be learned from data, but again did not address data noise.

\textbf{A3Test}~\cite{alagarsamy2023a3test} introduced domain adaptation techniques to improve test generation across different project styles. \textbf{ChatUniTest}~\cite{chen2024chatunitest} was among the first to leverage ChatGPT for test generation, using adaptive focal context and iterative refinement to improve compilation rates.

\subsubsection{LLM-Powered Test Generation}

The latest generation uses instruction-tuned LLMs such as GPT-4, StarCoder~\cite{li2023starcoder}, and CodeLlama~\cite{roziere2023code} for zero-shot or few-shot test generation. These models can generate readable, well-structured tests without task-specific fine-tuning. However, they still benefit significantly from fine-tuning on domain-specific data --- and the quality of that data is precisely the focus of CleanTest and our work.

Tools like \textbf{Pynguin}~\cite{lukasczyk2022pynguin} for Python combine traditional search-based strategies with LLM-guided generation. \textbf{CodaMosa}~\cite{lemieux2023codamosa} combines MOSA (a multi-objective search algorithm) with LLM suggestions for hard-to-cover branches.

The common thread across all four generations is that \textbf{the quality of training data directly affects model performance}. If 43.52\% of the training data is noisy, even the most sophisticated model architecture cannot fully compensate.

\subsection{Data Quality in Software Engineering}

Data quality has emerged as a critical concern across all applications of machine learning to software engineering. We review relevant work along three dimensions.

\subsubsection{Code Duplication and Data Leakage}

Allamanis~\cite{allamanis2019adverse} conducted an influential study on the adverse effects of code duplication in machine learning models of code. Using the popular \textit{java-small}, \textit{java-med}, and \textit{java-large} benchmarks, Allamanis showed that near-duplicate files between training and test sets inflate evaluation metrics by 10--100\%, depending on the task. This work led to the standard practice of deduplication in dataset construction --- a practice we also apply as the first step in our pipeline.

\subsubsection{Code Naturalness and Distribution}

Hindle et al.~\cite{hindle2016naturalness} introduced the \textit{naturalness hypothesis}: software is repetitive and predictable, similar to natural language. Tu et al.~\cite{tu2014localness} extended this by showing that code naturalness varies significantly across projects, suggesting that training data should be carefully curated to represent the target distribution. Non-English comments and culturally-specific coding styles (one of CleanTest's noise categories) can skew the distribution.

\subsubsection{CleanTest: Data Quality for Unit Test Generation}

\textbf{CleanTest}~\cite{zhang2025cleantest} is the study of data quality specifically for unit test generation that this work builds on. Zhang et al. (Zhejiang University, Huawei, and Singapore Management University) conducted both quantitative analysis and qualitative interviews with 17 domain experts (software testing experts) to characterize noise in test training data.

Their key findings on the Methods2Test dataset:
\begin{itemize}
    \item \textbf{43.52\%} of samples contain at least one type of noise.
    \item The largest noise category is \textbf{Unnecessary Annotations} (41.64\% of all data), consisting of Java annotations like \texttt{@RequestMapping}, \texttt{@GetMapping}, \texttt{@ApiOperation}, etc., that are syntactically valid but provide no useful signal for the test generation task because they describe deployment/API metadata rather than test-relevant behavior.
    \item The second largest is \textbf{No Relevance} (12.70\%): test methods paired with focal methods they don't actually test, caused by heuristic errors in the original dataset extraction.
    \item Eight noise categories in total, addressed by CleanTest's three-stage pipeline: a rule-based syntax filter (handling six types: ambiguous data types, unnecessary annotations, empty exception handling statements, missing implementation, syntax errors, and non-English literals), a rule-based relevance filter (detecting irrelevant test-focal pairs via function name, parameter count, and parameter type matching), and a model-based coverage filter (predicting low branch coverage).
    \item Training on the cleaned subset (``less is more'') improved downstream model performance significantly across all four evaluated models (CodeBERT~\cite{feng2020codebert}, AthenaTest~\cite{tufano2022athenatest}, StarCoder~\cite{li2023starcoder}, CodeLlama7B~\cite{roziere2023code}) --- on average $\approx 67\,\%$ in branch coverage for Methods2Test (and a smaller, single-digit-percent improvement for Atlas), measured on the Defects4J~\cite{just2014defects4j} benchmark.
\end{itemize}

The CleanTest framework consists of three filters:
\begin{enumerate}
    \item \textbf{Rule-based syntax filter}: Uses tree-sitter AST parsing to detect six types of syntactic noise (ambiguous data types, unnecessary annotations, empty exception handling statements, missing implementation, syntax errors, non-English literals), plus a 21,954-entry annotation dictionary for unnecessary annotation detection.
    \item \textbf{Relevance filter}: Matches function name, parameter count, and parameter types between the focal method and function calls in the test case to determine relevance.
    \item \textbf{Coverage filter}: Uses a CodeGPT model fine-tuned to predict branch coverage from concatenated focal method and test case code.
\end{enumerate}

The original implementation is provided as standalone Python scripts in a Zenodo replication package. While functional, the scripts are tightly coupled to specific file paths, lack error handling for edge cases (e.g., deeply nested ASTs that cause stack overflow), and have no test suite. Our work addresses all of these limitations.

\subsection{LLM-Based Code Analysis}

Large language models have been increasingly applied to code analysis tasks beyond generation. We review their capabilities and limitations relevant to our work.

\subsubsection{Code Understanding and Review}

GPT-4~\cite{openai2023gpt4} and Claude 3~\cite{anthropic2024claude} can perform zero-shot code review, identifying potential bugs, style issues, and security vulnerabilities. Specialized code models like \textbf{DeepSeek-Coder}~\cite{guo2024deepseek} and \textbf{Qwen2.5-Coder}~\cite{hui2024qwen} achieve strong performance on code understanding benchmarks (HumanEval~\cite{chen2021humaneval}, MBPP~\cite{austin2021mbpp}, CodeContests~\cite{li2022alphacode}) while being more cost-effective than general-purpose models.

\subsubsection{Limitations: Hallucination and Pattern Matching}

Despite impressive capabilities, LLMs have well-documented limitations relevant to our task:

\textbf{Hallucination on domain-specific judgments}: When an LLM is asked to classify code as ``clean'' or ``noisy'' without an exhaustive specification of the noise taxonomy, it tends to fall back on surface-level plausibility rather than rigorous structural analysis --- our zero-shot baseline misses 77.9\,\% of noisy samples on this exact failure mode (Section~\ref{sec:evaluation}).

\textbf{Limited pattern dictionary}: A critical limitation for our task is that LLMs cannot reliably match against a dictionary of 21,954 annotation patterns. The patterns are too numerous and too diverse (ranging from common \texttt{@GetMapping} to obscure \texttt{@AtlasConversionInfo}) to fit into a single prompt context, and LLMs lack the exhaustive recall needed for dictionary-lookup tasks.

\textbf{Multi-agent verification}: Recent work on multi-agent paper-writing systems such as PaperOrchestra~\cite{song2026paperorchestra} demonstrates that orchestrated multi-agent pipelines with structured verification mechanisms can outperform single-agent monolithic prompts on complex, multi-step tasks. This validates the broader principle underlying our work: orchestrated specialized components beat monolithic ``ask the LLM once'' approaches.

\subsection{Agent Skill Architectures}

The concept of composable agent skills has gained traction with the rise of AI coding assistants. We review the two most influential frameworks.

\subsubsection{Superpowers}

\textbf{Superpowers}~\cite{vincent2026superpowers}, developed by Jesse Vincent, is one of the most popular skills frameworks (over 200{,}000 GitHub stars as of May 2026). It provides 14 core skills organized around a structured development methodology: brainstorming (Socratic design refinement), writing-plans (task decomposition), test-driven-development (RED-GREEN-REFACTOR enforcement), systematic-debugging (4-phase root cause analysis), and subagent-driven-development (parallel task execution with two-stage code review).

Superpowers works across Claude Code, Codex CLI, Cursor, Gemini CLI, and OpenCode, demonstrating the cross-IDE viability of the SKILL.md protocol.

\subsubsection{Academic Research Skills (ARS)}

\textbf{ARS}~\cite{wu2026ars} applies the skill paradigm to academic research workflows. Its four core skills (Deep Research with 13 agents, Academic Paper with 12 agents, Paper Reviewer with 7 agents, and Pipeline Orchestrator) demonstrate that multi-agent skill pipelines can coordinate complex, multi-stage workflows beyond software development.

ARS's orchestrator design --- where a top-level skill dispatches work to specialized sub-skills --- directly inspired our \texttt{cleantest-pipeline} orchestrator design.

\subsubsection{The SKILL.md Protocol}

Both frameworks converge on the \texttt{SKILL.md} protocol: each skill is a directory containing a Markdown file with YAML front matter (name, description, trigger phrases) followed by detailed workflow instructions. The coding assistant discovers skills by scanning designated directories (e.g., \texttt{\textasciitilde/.codebuddy/skills/} for CodeBuddy, \texttt{\textasciitilde/.claude/skills/} for Claude Code). When a user's natural language query matches a skill's trigger phrases, the assistant loads the skill's instructions and follows them.

This protocol decouples skill authoring from the assistant runtime and is intended to support a growing pool of community-contributed skills. Our work contributes four new skills to this pool, specifically targeting the code data quality domain.

\subsection{The Aho-Corasick Algorithm}

The Aho-Corasick algorithm~\cite{aho1975efficient}, developed by Alfred Aho and Margaret Corasick at Bell Labs in 1975, is a classic multi-pattern string matching algorithm. Given a set of $k$ patterns with total length $m$ and a text of length $n$, it finds all occurrences of all patterns in time $O(n + m + z)$, where $z$ is the total number of matches. This is achieved through three key data structures:

\begin{enumerate}
    \item \textbf{Goto function}: A trie built from all patterns, defining transitions on matching characters.
    \item \textbf{Failure function}: Links from each state to the longest proper suffix that is also a prefix of some pattern, enabling efficient backtracking without re-reading characters.
    \item \textbf{Output function}: Associates each state with the set of patterns that end at that state.
\end{enumerate}

For our application with $k = 21{,}954$ patterns and average text length $n \approx 549$ characters, the na\"ive approach requires $O(n \cdot k) \approx 12$ million character comparisons per sample. Aho-Corasick reduces this to $O(n + z) \approx 549 + 1$ comparisons per sample (since most samples have at most one matching pattern). Over 593,953 samples, this represents a theoretical speedup of $\sim$22,000$\times$, though the practical speedup (11.5$\times$ for the full pipeline) is lower due to the overhead of other filter stages and Python interpreter costs.

We use the \texttt{pyahocorasick}~\cite{pyahocorasick} Python library, which provides a C-extension implementation with a Python interface. The automaton construction takes $<$0.1 seconds and the per-sample query averages $<$0.01 ms.

\subsection{Tree-sitter for AST Parsing}

\textbf{tree-sitter}~\cite{brunsfeld2018treesitter} is a parser generator and incremental parsing library originally developed by Max Brunsfeld for the Atom editor at GitHub, now widely adopted in multiple editors and IDEs. It builds concrete syntax trees (CSTs) for source files in over 50 programming languages through language-specific grammar packages.

We chose tree-sitter over alternatives for four reasons:
\begin{enumerate}
    \item \textbf{Performance}: The core parser is written in C, with Python bindings (\texttt{py-tree-sitter}) providing near-native parsing speed. On our hardware, tree-sitter parses a typical Java method in $<$0.1 ms.
    \item \textbf{Error tolerance}: Unlike traditional parsers that fail on invalid input, tree-sitter generates CSTs that include explicit \texttt{ERROR} nodes for malformed code regions. This is essential for our syntax error detection (Noise Type N1), allowing us to detect parse failures as a feature rather than a crash.
    \item \textbf{Concrete syntax trees}: tree-sitter produces CSTs (not ASTs), preserving all syntactic detail including comments, whitespace, and annotation structures. This is critical for detecting annotation noise patterns.
    \item \textbf{Multi-language extensibility}: Our current implementation uses \texttt{tree-sitter-java}, but the same infrastructure can support \texttt{tree-sitter-python} or \texttt{tree-sitter-javascript} for future cross-language extensions.
\end{enumerate}


% ============================================================================
\section{Requirements Analysis}
\label{sec:requirements}
% ============================================================================

\subsection{Stakeholder Analysis}

We identify three primary stakeholder groups for CleanTest-Agent:

\begin{table}[htbp]
\caption{Stakeholder Analysis}
\label{tab:stakeholders}
\begin{tabular}{@{}lp{3cm}p{5.5cm}@{}}
\toprule
\textbf{Stakeholder} & \textbf{Role} & \textbf{Primary Needs} \\
\midrule
ML/AI Researchers & Train test generation models & Reproducible cleaning pipeline, transparent noise reports, configurable thresholds, batch processing \\
Software Engineers & Daily development workflow & Easy invocation via natural language, fast feedback, IDE integration \\
Tool Maintainers & Extend the system & Modular architecture, clear interfaces, documented APIs and skill protocol \\
\bottomrule
\end{tabular}
\end{table}

\subsection{Problem Statement}

Given a unit test training dataset $D = \{(f_i, t_i)\}_{i=1}^{N}$ where $f_i$ is a focal method and $t_i$ is a test case, the goal is to:

\begin{enumerate}
    \item Identify which samples are \textit{noisy} (would degrade model training).
    \item Categorize each noisy sample by noise type.
    \item Output a cleaned dataset $D' \subseteq D$ along with a structured noise report.
    \item Provide this functionality through both a CLI interface and an Agent Skill interface.
\end{enumerate}

The noise types are pre-defined according to the CleanTest framework, but the architecture should make it easy to add new noise types in the future without modifying existing code.

\subsection{Use Cases}

We identify three primary use cases:

\subsubsection{UC1: Batch Dataset Cleaning}

\textbf{Actor}: ML/AI Researcher.
\textbf{Precondition}: Researcher has a CSV dataset with at minimum \texttt{src\_fm} and \texttt{target} columns.

\textbf{Main Flow}:
\begin{enumerate}
    \item Researcher invokes the pipeline via CLI or natural language through a coding assistant.
    \item System loads the dataset and deduplicates by \texttt{target} column.
    \item System runs Filter 1 (syntax noise), reporting per-noise-type statistics.
    \item System runs Filter 2 (relevance), reporting irrelevant test-focal pairs.
    \item System optionally runs Filter 3 (coverage). When the input CSV carries a \texttt{condition\_cover\_rate} column, Filter 3 runs in label mode (no model, no GPU); otherwise it can be invoked via the \texttt{cleantest-coverage-filter} skill in model mode if a fine-tuned Qwen2.5-Coder-0.5B checkpoint and a CUDA GPU are available.
    \item System outputs: \texttt{filtered\_data.csv}, \texttt{noise\_report.json}, \texttt{summary.md}.
\end{enumerate}

\textbf{Postcondition}: Researcher has a cleaned CSV file and detailed noise statistics.

\textbf{Alternative Flow}: If the CSV is missing required columns, the system raises a \texttt{ValueError} with a descriptive message listing available columns.

\subsubsection{UC2: Interactive Noise Inspection}

\textbf{Actor}: Software Engineer using a coding assistant.

\textbf{Main Flow}:
\begin{enumerate}
    \item Engineer asks: ``Is this test noisy?'' and pastes a code snippet.
    \item The coding assistant triggers the appropriate filter skill based on intent.
    \item The filter analyzes the sample and returns: noise type (if any), confidence, and reasoning.
    \item Engineer optionally asks for LLM second-opinion for borderline cases.
\end{enumerate}

\subsubsection{UC3: Pipeline Extension}

\textbf{Actor}: Tool Maintainer.

\textbf{Main Flow}:
\begin{enumerate}
    \item Maintainer creates a new directory \texttt{skills/cleantest-X-filter/}.
    \item Writes \texttt{SKILL.md} with description and trigger phrases.
    \item Implements detection logic in \texttt{scripts/X\_filter.py}.
    \item Adds a new stage in \texttt{cleantest\_agent/pipeline.py} that calls the new filter.
    \item Adds unit tests and runs CI to verify.
\end{enumerate}

\subsection{UML Use Case Diagram}

Figure~\ref{fig:usecase} presents the UML use case diagram capturing the three primary actors and their interactions with the system.

\begin{figure}[htbp]
\centering
\begin{tikzpicture}[
    % UML 2.5.1 actor: stick figure drawn from a single TikZ pic command
    % (Notation: §18.5 Actors). The pic origin (0,0) sits at the figure's
    % torso so that a node anchor like (rC) corresponds to the actor's
    % vertical centre line; association lines start from the right edge.
    actor pic/.pic={
        \draw (0,0.30) circle (0.18);                    % head
        \draw (0,0.12) -- (0,-0.40);                     % torso
        \draw (-0.30,-0.10) -- (0.30,-0.10);             % arms
        \draw (0,-0.40) -- (-0.25,-0.80);                % left leg
        \draw (0,-0.40) -- ( 0.25,-0.80);                % right leg
    },
    actor/.style={inner sep=0pt, minimum size=1.4cm},
    usecase/.style={ellipse, draw, minimum width=2.8cm, minimum height=0.8cm, align=center, font=\footnotesize},
    node distance=0.6cm,
]
% Actors (UML 2.5.1 stick figure with the actor name placed directly
% beneath the figure, §18.5.4). Each actor has a coordinate at its
% right shoulder (x = 0.3 from the centre) used as the start of every
% association line so that the line starts at the actor's body edge,
% never inside it.
\path (-4.5,0)    pic {actor pic} node[below=0.55cm, font=\footnotesize] {Researcher};
\path (-4.5,-3)   pic {actor pic} node[below=0.55cm, font=\footnotesize] {Engineer};
\path (-4.5,-5.5) pic {actor pic} node[below=0.55cm, font=\footnotesize] {Maintainer};
\coordinate (rC) at (-4.2,0);     % right shoulder of Researcher
\coordinate (eC) at (-4.2,-3);    % right shoulder of Engineer
\coordinate (mC) at (-4.2,-5.5);  % right shoulder of Maintainer

% System boundary (Subject, §18.4.4): rectangle with the subject name
% placed inside the upper-left corner, per UML 2.5.1 notation.
\draw[rounded corners] (-2,-7) rectangle (4.5,1.5);
\node[font=\small\bfseries, anchor=north west] at (-1.85,1.4) {CleanTest-Agent};

% Use cases
\node[usecase] (uc1) at (1.25,0.3)  {Batch Dataset\\Cleaning};
\node[usecase] (uc2) at (1.25,-1.5) {Interactive Noise\\Inspection};
\node[usecase] (uc3) at (1.25,-3.3) {Configure\\Thresholds};
\node[usecase] (uc4) at (1.25,-5)   {Extend Pipeline\\(Add Filter)};
\node[usecase] (uc5) at (1.25,-6.5) {Run Tests\\and CI/CD};

% Associations (UML 2.5.1 §18.5.4: solid line with no arrowhead).
% Endpoints attach to actor's right shoulder and use case's west pole.
\draw (rC) -- (uc1.west);
\draw (rC) -- (uc3.west);
\draw (eC) -- (uc2.west);
\draw (eC) -- (uc1.west);
\draw (mC) -- (uc4.west);
\draw (mC) -- (uc5.west);

% Use cases are kept independent. The earlier "<<include>>" arrow from
% UC1 to UC3 was removed because configuring thresholds is a
% precondition / setup activity, not a mandatory sub-flow that UC1
% must always invoke (which is what UML 2.5.1 "<<include>>" requires).
\end{tikzpicture}
\caption{UML Use Case Diagram}
\Description{UML 2.5.1 use case diagram. Three stick-figure actors (Researcher, Engineer, Maintainer) on the left are connected by solid association lines to five use cases (Batch Dataset Cleaning, Interactive Noise Inspection, Configure Thresholds, Extend Pipeline, Run Tests and CI/CD) inside the CleanTest-Agent system boundary, whose name appears in the upper-left corner of the boundary rectangle.}
\label{fig:usecase}
\end{figure}

\subsection{Activity Diagram: Batch Cleaning Pipeline}

Figure~\ref{fig:activity} shows the activity flow for the primary use case (UC1), illustrating decision points where LLM enhancement is optionally invoked.

\begin{figure}[htbp]
\centering
\begin{tikzpicture}[
    node distance=0.7cm,
    % UML 2.5.1 §15.7.4 InitialNode: a small filled circle.
    start/.style={circle, fill=black, minimum size=0.3cm, inner sep=0pt},
    % UML 2.5.1 §15.7.4 ActivityFinalNode ("bullseye"):
    % unfilled outer circle with a smaller filled circle inside;
    % the inner filled circle is drawn explicitly with \fill so the
    % two circles are concentric and have the canonical ~3:5 ratio.
    finish/.style={circle, draw, minimum size=0.55cm, inner sep=0pt},
    activity/.style={rectangle, draw, rounded corners, minimum width=2.5cm, minimum height=0.6cm, align=center, font=\footnotesize},
    % UML 2.5.1 §15.7.5 DecisionNode and MergeNode are both drawn as
    % a hollow diamond. They differ only in incoming/outgoing edge
    % topology (decision: 1-in / many-out, merge: many-in / 1-out).
    decision/.style={diamond, draw, minimum width=1.2cm, minimum height=1cm, align=center, font=\tiny},
    merge/.style={diamond, draw, minimum width=0.9cm, minimum height=0.7cm, font=\tiny},
    % UML 2.5.1 §15.7.6 ControlFlow: solid line with stick arrowhead.
    arrow/.style={-{Stealth[length=2mm]}},
]
% Main vertical pipeline (x = 0)
\node[start] (s) {};
\node[activity, below=of s] (load) {Load CSV + Deduplicate};
\node[activity, below=of load] (f1) {Filter 1: Syntax Noise\\(AST + Aho-Corasick)};
\node[decision, below=0.8cm of f1] (d1) {Noise\\detected?};
\node[activity, below=0.8cm of d1] (f2) {Filter 2: Relevance\\(AST Name Match)};
\node[decision, below=0.8cm of f2] (d2) {Overlap\\= 0?};
% MergeNode m2 collects the two RELEVANT paths (overlap > 0; LLM says
% RELEVANT) before flowing into Filter 3. Without it, Filter 3 would
% have two incoming control flows --- forbidden by UML 2.5.1 §15.7.5.
\node[merge, below=0.8cm of d2] (m2) {};
\node[activity, below=0.7cm of m2] (f3) {Filter 3: Coverage\\(label or Qwen2.5-Coder)};
% Final MergeNode mrg collects three "drop or done" paths:
%   (a) Filter 3 main exit
%   (b) d1 [noise detected]    --> sample removed by Filter 1
%   (c) dllm [IRRELEVANT]      --> sample removed by Filter 2
\node[merge, below=0.6cm of f3] (mrg) {};
\node[activity, below=0.6cm of mrg] (report) {Generate Report\\(JSON + MD)};
\node[finish, below=of report] (e) {};
% Inner filled disc for the activity-final "bullseye": canonical 3:5
% ratio of inner-to-outer diameter (i.e. inner radius ~ 0.165 cm
% versus outer radius ~ 0.275 cm).
\fill (e) circle (0.165cm);

% Side branch (right of d2): LLM judge and its own DecisionNode.
\node[activity, right=2.2cm of d2] (llm) {LLM Semantic\\Judge};
\node[decision, below=0.8cm of llm] (dllm) {LLM\\verdict?};

% --- Sequential edges on the main column ---
\draw[arrow] (s)     -- (load);
\draw[arrow] (load)  -- (f1);
\draw[arrow] (f1)    -- (d1);
\draw[arrow] (d1)    -- node[left, font=\tiny] {[no noise]} (f2);
\draw[arrow] (f2)    -- (d2);
\draw[arrow] (d2)    -- node[left, font=\tiny] {[overlap $>$ 0]} (m2);
\draw[arrow] (m2)    -- (f3);
\draw[arrow] (f3)    -- (mrg);
\draw[arrow] (mrg)   -- (report);
\draw[arrow] (report) -- (e);

% --- Side branch: d2 [overlap = 0] -> LLM -> dllm -> ... ---
\draw[arrow] (d2.east) -- node[above, font=\tiny] {[overlap = 0]} (llm.west);
\draw[arrow] (llm)     -- (dllm);
% [RELEVANT] joins the main column at the m2 merge node.
\draw[arrow] (dllm.west) -- node[above, font=\tiny] {[RELEVANT]} (m2.east);

% [IRRELEVANT] bypasses Filter 3 and joins the final merge mrg
% (sample is removed). Routed through the right column x = 6 so the
% segment never crosses any node.
\coordinate (rightCol) at (6, 0);
\draw[arrow] (dllm.east)
    -- node[above, font=\tiny] {[IRRELEVANT]} (rightCol |- dllm.east)
    -- (rightCol |- mrg.east)
    -- (mrg.east);

% --- Bypass branch: d1 [noise detected] -> mrg (sample removed by F1) ---
% Routed through the left column x = -3.5 so the segment never crosses
% any node on the main column.
\coordinate (leftCol) at (-3.5, 0);
\draw[arrow] (d1.west)
    -- node[above, font=\tiny] {[noise detected]} (leftCol |- d1.west)
    -- (leftCol |- mrg.west)
    -- (mrg.west);
\end{tikzpicture}
\caption{Activity Diagram: Batch Cleaning Pipeline (UC1)}
\Description{UML 2.5.1 activity diagram. Initial node (filled circle) flows through CSV loading and the Syntax filter, then to a Decision diamond "Noise detected?" with two guarded outgoing edges. The [no noise] edge continues to the Relevance filter and a second Decision "Overlap = 0?". The [overlap > 0] edge meets a Merge diamond that collects also the [RELEVANT] verdict from the LLM-side Decision; the merge feeds Filter 3 (Coverage). The [IRRELEVANT] verdict and the [noise detected] bypass both feed into a final Merge diamond before the Generate-Report activity, which leads to an Activity-Final "bullseye" node.}
\label{fig:activity}
\end{figure}

\subsection{Sequence Diagram: LLM-Enhanced Relevance Check}

Figure~\ref{fig:sequence} illustrates the interaction sequence when the relevance filter encounters a borderline case (zero name overlap) and falls back to LLM judgment.

\begin{figure}[htbp]
\centering
\begin{tikzpicture}[
    node distance=1.5cm,
    lifeline/.style={dashed, gray},
    % UML 2.5.1 §17.4: synchronous CallMessage uses a filled solid
    % triangular arrowhead; reply Message uses a dashed line with an
    % open stick arrowhead.
    msg/.style={-{Triangle[length=2.2mm,width=2mm]}, thick},
    ret/.style={-{Stealth[length=2mm]}, thick, dashed},
    obj/.style={rectangle, draw, minimum width=1.8cm, minimum height=0.6cm, font=\footnotesize, align=center},
    act/.style={rectangle, draw, fill=white, minimum width=0.18cm},
    frame/.style={draw, thick},
]
% UML 2.5.1 §17.3 Interaction frame: the whole sequence diagram is
% enclosed by a rectangle with a pentagon-shaped tag in the upper-left
% corner labelled "sd <InteractionName>".
\draw[thick] (-1.5,0.9) rectangle (12.0,-7.0);
\draw[thick] (-1.5,0.9) -- (-1.5,0.45) -- (-0.05,0.45) -- (0.15,0.65) -- (0.15,0.9);
\node[anchor=west, font=\footnotesize\bfseries] at (-1.45,0.67) {sd RelevanceCheck};

% Lifeline heads: UML 2.5.1 §17.3.4 recommends "name : Classifier" form.
\node[obj] (orch) at (0,0)    {orch : Orchestrator};
\node[obj] (rel)  at (3.5,0)  {rel : Relevance\\Filter};
\node[obj] (ast)  at (7,0)    {ast : AST\\Parser};
\node[obj] (llm)  at (10.5,0) {llm : LLM\\Client};

% Lifelines (extended to -6.7).
\draw[lifeline] (orch.south) -- (0,-6.7);
\draw[lifeline] (rel.south)  -- (3.5,-6.7);
\draw[lifeline] (ast.south)  -- (7,-6.7);
\draw[lifeline] (llm.south)  -- (10.5,-6.7);

% ExecutionSpecifications (UML 2.5.1 §17.4.4): a thin rectangle on the
% lifeline indicating the active period. Each callee's activation
% starts AT the moment the synchronous CallMessage arrives (same Y),
% and ends AT the moment its ReplyMessage is sent.
\draw[act] (-0.09,-1.0) rectangle (0.09,-6.0);   % orch active from call until final reply
\draw[act] (3.41,-1.0)  rectangle (3.59,-6.0);   % rel active from receiving call until reply
\draw[act] (6.91,-1.7)  rectangle (7.09,-2.2);   % ast extract_methods
\draw[act] (6.91,-2.7)  rectangle (7.09,-3.2);   % ast extract_invocations
\draw[act] (10.41,-4.5) rectangle (10.59,-5.4);  % llm judge

% --- Messages on the main flow ---
% Synchronous CallMessages use the filled triangle (msg);
% ReplyMessages use a dashed line + open stick arrow (ret).
\draw[msg] (0.09,-1.0)  -- node[above, font=\tiny] {check\_relevance(f, t)}      (3.41,-1.0);
\draw[msg] (3.59,-1.7)  -- node[above, font=\tiny] {extract\_methods(f)}         (6.91,-1.7);
\draw[ret] (6.91,-2.2)  -- node[above, font=\tiny] {src\_methods}                (3.59,-2.2);
\draw[msg] (3.59,-2.7)  -- node[above, font=\tiny] {extract\_invocations(t)}     (6.91,-2.7);
\draw[ret] (6.91,-3.2)  -- node[above, font=\tiny] {test\_invocations}           (3.59,-3.2);

% UML 2.5.1 §17.6.2.5 opt CombinedFragment: a single InteractionOperand
% guarded by [overlap = 0]. We use opt rather than alt because there is
% only one operand and no implicit [else] branch is required.
\draw[frame] (3.0,-3.9) rectangle (11.0,-5.7);
\node[font=\tiny\bfseries, anchor=north west] at (3.05,-3.85) {opt};
\node[font=\tiny, anchor=north west] at (3.6,-3.95) {[overlap = 0]};
\draw[msg] (3.59,-4.5)  -- node[above, font=\tiny] {llm\_judge(f, t)}           (10.41,-4.5);
\draw[ret] (10.41,-5.4) -- node[above, font=\tiny] {``RELEVANT''}               (3.59,-5.4);

% Final ReplyMessage to the caller: emitted at the END of rel's
% ExecutionSpecification (Y = -6.0).
\draw[ret] (3.41,-6.0)  -- node[above, font=\tiny] {RELEVANT (keep)}           (0.09,-6.0);
\end{tikzpicture}
\caption{Sequence Diagram: LLM-Enhanced Relevance Check}
\Description{UML 2.5.1 sequence diagram enclosed in an interaction frame labelled "sd RelevanceCheck". Four lifelines: orch:Orchestrator, rel:RelevanceFilter, ast:ASTParser, llm:LLMClient. Synchronous CallMessages use filled-triangle arrowheads; ReplyMessages use dashed lines with open stick arrowheads. ExecutionSpecifications (activation bars) start exactly when the call arrives and end exactly when the reply is sent. An opt CombinedFragment guarded by [overlap = 0] encloses the optional LLM call.}
\label{fig:sequence}
\end{figure}

\paragraph{Optional reflection step.} The single LLM call shown in
the \texttt{opt} CombinedFragment of Figure~\ref{fig:sequence} is,
when the \texttt{--reflection} flag is enabled, internally
expanded into a generate~$\to$~reflect~$\to$~revise pattern (the
Reflection agentic pattern of Shinn et al.~\cite{shinn2023reflexion}):
a second \emph{reflection prompt} re-checks each \textsc{IRRELEVANT}
verdict against a five-rule checklist grounded in xUnit test
patterns~\cite{meszaros2007xunit} before committing the removal.
The full mechanism, the checklist, the prompt text, and a
45-sample validation are presented in
Section~\ref{sec:reflection-mechanism}. Throughout this paper the
\texttt{--reflection} flag is \emph{off} unless explicitly stated:
the headline F1\,=\,0.965 hybrid result reported in
Section~\ref{sec:evaluation} uses single-call mode, so any
improvement from reflection is additive and deployment-tunable
rather than baked into the headline number.

\subsection{Functional Requirements}

\begin{table}[htbp]
\caption{Functional Requirements}
\label{tab:functional-req}
\begin{tabular}{@{}llp{5.5cm}@{}}
\toprule
\textbf{ID} & \textbf{Priority} & \textbf{Description} \\
\midrule
FR1 & Must & Detect syntactic noise types using AST parsing \\
FR2 & Must & Detect unnecessary modifiers using dictionary matching \\
FR3 & Must & Assess test--focal method relevance via name matching \\
FR4 & Should & Enhance borderline cases with LLM semantic judgment \\
FR5 & Should & Predict branch coverage in model mode using a fine-tuned Qwen2.5-Coder-0.5B regression model when no ground-truth label is available \\
FR6 & Must & Generate structured noise reports (JSON + Markdown) \\
FR7 & Must & Support batch processing of CSV datasets \\
FR8 & Should & Each filter independently invocable as an Agent Skill \\
FR9 & Could & Support interactive single-sample queries \\
\bottomrule
\end{tabular}
\end{table}

\subsection{Non-Functional Requirements}

\begin{table}[htbp]
\caption{Non-Functional Requirements}
\label{tab:nonfunctional-req}
\begin{tabular}{@{}llp{5.5cm}@{}}
\toprule
\textbf{ID} & \textbf{Category} & \textbf{Description} \\
\midrule
NFR1 & Performance & Process 600K samples in $<$5 minutes \\
NFR2 & Cost & LLM cost $<$\$0.05 per 500 samples \\
NFR3 & Accuracy & F1 $>$ 0.95 for noise detection \\
NFR4 & Extensibility & New filters addable without modifying existing code \\
NFR5 & Compatibility & Work with CodeBuddy, Claude Code, Cursor \\
NFR6 & Testability & All filters covered by unit tests; CI/CD passing \\
\bottomrule
\end{tabular}
\end{table}

\subsection{Requirements Traceability Matrix}

We maintain a traceability matrix linking each requirement to its implementation module and corresponding test case:

\begin{table}[htbp]
\caption{Requirements Traceability Matrix}
\label{tab:traceability}
% Columns sized so total width <= acmlarge single-column textwidth
% (~13.97cm). \raggedright lets long \texttt module paths break at
% whitespace boundaries instead of overflowing the column.
\begin{tabular}{@{}p{0.7cm}>{\raggedright\arraybackslash}p{5.6cm}>{\raggedright\arraybackslash}p{6.8cm}@{}}
\toprule
\textbf{Req} & \textbf{Module} & \textbf{Test Case} \\
\midrule
FR1  & \texttt{cleantest\_agent/\allowbreak parser\_utils.py}    & \texttt{test\_syntax\_filter.py} (16 cases) \\
FR2  & \texttt{cleantest\_agent/\allowbreak pipeline.py} (Aho-Corasick) & \texttt{test\_syntax\_filter.py::}\allowbreak\texttt{TestUnnecessaryAnnotations} \\
FR3  & \texttt{cleantest\_agent/\allowbreak parser\_utils.py}    & \texttt{test\_relevance\_filter.py} (7 cases) \\
FR4  & \texttt{cleantest\_agent/\allowbreak llm\_client.py}      & Integration test (requires API) \\
FR5  & \texttt{coverage\_predictor.py}               & \texttt{test\_coverage\_filter.py} (4 cases) \\
FR6  & \texttt{cleantest\_agent/\allowbreak report\_generator.py}& \texttt{test\_report.py} (5 cases) \\
FR7  & \texttt{cleantest\_agent/\allowbreak data\_loader.py}     & \texttt{test\_pipeline.py} (4 cases) \\
FR8  & \texttt{skills/*/SKILL.md}                    & Manual skill discovery test \\
NFR1 & Aho-Corasick in pipeline                       & RQ3 experiment (Section~\ref{sec:evaluation}) \\
NFR6 & \texttt{tests/} directory                      & CI: 36 tests passing \\
\bottomrule
\end{tabular}
\end{table}

This traceability ensures that every requirement has at least one corresponding implementation and verification artifact.


% ============================================================================
\section{The Model-Driven Approach}
\label{sec:model-driven}
% ============================================================================

This section presents the central methodological contribution of our work: the \textbf{model-driven approach} for code data quality assurance. This directly responds to the assignment's core requirement: ``how to use intelligent model-driven methods to solve the chosen problem.''

\subsection{Definition}

We define the \textbf{model-driven approach} as a paradigm that orchestrates multiple specialized components, each based on a different ``model'' of computation, applied where it is most effective:

\begin{itemize}
    \item \textbf{Rule-based models}: Deterministic pattern matching, AST parsing, regex --- used where exhaustive coverage of a known finite pattern set is required and where deterministic results are critical.
    \item \textbf{Machine learning models}: Trained neural networks (e.g., the fine-tuned Qwen2.5-Coder-0.5B coverage regression model wired into Filter 3's optional model mode) --- used where the task has been studied with labelled training data and a learned representation outperforms hand-crafted heuristics.
    \item \textbf{Large language models (LLMs)}: General-purpose LLMs (e.g., GPT-4o-mini, Claude) --- used where semantic understanding and reasoning are required, and where rules and ML models cannot capture the needed nuance.
\end{itemize}

The orchestration is performed through a pipeline architecture, where each component handles the cases it is best suited for, and falls back to the next component for borderline or specialized cases.

\subsection{Comparison: Model-Driven vs. Pure-LLM Approach}

We contrast our model-driven approach with the alternative ``pure-LLM tool approach'' that uses a single LLM call per sample:

\begin{table}[htbp]
\caption{Model-Driven vs. Pure-LLM Approach}
\label{tab:model-driven-vs-llm}
\begin{tabular}{@{}>{\raggedright\arraybackslash}p{3cm}>{\raggedright\arraybackslash}p{4.6cm}>{\raggedright\arraybackslash}p{5.6cm}@{}}
\toprule
\textbf{Dimension} & \textbf{Pure-LLM Approach} & \textbf{Model-Driven (Ours)} \\
\midrule
Architecture & Monolithic LLM call & Pipeline of specialized components \\
Pattern matching & LLM reasons from prompt & Aho-Corasick automaton (21,954 patterns) \\
AST analysis & LLM approximates parsing & tree-sitter exact parsing \\
Coverage prediction & LLM guesses & JaCoCo labels (label mode) or fine-tuned Qwen2.5-Coder-0.5B (model mode) \\
Semantic judgment & LLM (always) & LLM (only borderline cases, $\sim$12.7\%) \\
Cost per sample & $\sim$\$0.0001 (API call) & $\sim$\$0.00001 (amortized, 12.7\% LLM) \\
Latency per sample & $\sim$3,000 ms (API) & $<$1 ms (rules) \\
Determinism & No (LLM stochasticity) & Yes (rules) + tunable (LLM, temp=0) \\
Extensibility & Re-prompt engineering & Add new pipeline stage \\
Debuggability & LLM is a black box & Each stage is inspectable \\
Cost (593,953 samples)\textsuperscript{*} & $\sim$\$35 & $\sim$\$4.5 \\
\bottomrule
\end{tabular}
\begin{flushleft}
\small \textsuperscript{*} Pricing assumes DeepSeek-V4-Flash via Tencent
TokenHub: \textyen0.8/1M input tokens, \textyen2/1M output tokens.
Pure-LLM cost is for zero-shot; few-shot is $\sim$\$58. See
Table~\ref{tab:full-projection} for full derivation.
\end{flushleft}
\end{table}

\subsection{Why the Model-Driven Approach Wins}

Our experiments (Section~\ref{sec:evaluation}) demonstrate that the model-driven approach achieves F1=0.965 while the best pure-LLM approach achieves only F1=0.387. We identify three root causes for this gap:

\subsubsection{Root Cause 1: The Dictionary Knowledge Gap}

The annotation noise detection subtask requires matching against 21,954 specific patterns (e.g., \texttt{@RequestMapping}, \texttt{@ApiOperation}, \texttt{@ScalarFunction}). The Aho-Corasick automaton achieves \textbf{100\,\% recall on the dictionary patterns} because every pattern in the dictionary is explicitly encoded; recall against the underlying noise concept is bounded by the completeness of the dictionary itself, which we inherit unchanged from the original CleanTest paper.

In contrast, the LLM has seen some of these patterns during pre-training but cannot reliably recall all 21,954. It recognizes common patterns (\texttt{@GetMapping}, \texttt{@PostMapping}) but misses rare ones (\texttt{@AtlasConversionInfo}, \texttt{@ScalarFunction("ST\_Length")}). This is analogous to asking a person to recite an entire dictionary from memory versus looking up words in the dictionary --- the former inevitably has gaps.

Empirically, our real experiment shows that the LLM zero-shot approach achieves only 17.3\% recall on annotation noise specifically (see Table~\ref{tab:fn-by-type}: 158 out of 191 annotation-noisy samples are missed, i.e., only 33 correctly detected). Since annotations account for 82.7\% of all noise in our sample, this single failure mode accounts for 87.8\% of all false negatives (158/180) and explains the majority of the F1 gap.

\subsubsection{Root Cause 2: Structural Analysis vs. Textual Approximation}

For syntax-related noise types (missing implementation, empty exception handlers, ambiguous generics), the rule-based approach uses tree-sitter to perform \textit{exact structural analysis}: it parses the code into a concrete syntax tree and checks precise structural properties (e.g., ``does the \texttt{block} node have fewer than 3 children?'').

The LLM, by contrast, performs \textit{textual approximation}: it reads the code as text and estimates whether the structure seems problematic. This works for obvious cases (\texttt{public void init() \{ \}}) but fails for subtle ones where the code \textit{looks} normal but has structural issues detectable only through parsing.

This is analogous to measuring height with a ruler (exact) versus estimating by eye (approximate) --- the latter has inherent error.

\subsubsection{Root Cause 3: Cost Scaling}

The model-driven approach processes 99\% of samples using free, local computation (rule-based filters plus, in label mode, an $O(N)$ scan over JaCoCo coverage labels) and only 1\% using paid LLM API calls. The pure-LLM approach requires a paid API call for \textit{every} sample:

\begin{table}[htbp]
\caption{Cost Breakdown for 593,953 Samples (DeepSeek-V4-Flash, real pricing)}
\label{tab:cost-breakdown}
\begin{tabularx}{\linewidth}{@{}l*{3}{>{\raggedleft\arraybackslash}X}@{}}
\toprule
\textbf{Component} & \textbf{Hybrid (ours)} & \textbf{Pure LLM (zero-shot)} & \textbf{Pure LLM (few-shot)} \\
\midrule
Rule-based processing & \$0 & --- & --- \\
Coverage filter (label mode) & \$0 & --- & --- \\
LLM API (borderline only) & $\sim$\$4.5 (12.7\% of samples) & $\sim$\$35 (100\%) & $\sim$\$58 (100\%) \\
\midrule
\textbf{Total} & \textbf{$\sim$\$4.5} & \textbf{$\sim$\$35} & \textbf{$\sim$\$58} \\
\bottomrule
\end{tabularx}
\begin{flushleft}
\small Same pricing assumptions as Table~\ref{tab:full-projection}.
Hybrid invokes the LLM only on $\sim$12.7\% of samples (those flagged
as borderline by Filter 2's name-overlap check), making its API spend
roughly an order of magnitude smaller than the pure-LLM baselines.
\end{flushleft}
\end{table}

At scale, the cost difference is 8--13$\times$ ($\sim$\$4.5 hybrid vs. $\sim$\$35--\$58 pure LLM; see Table~\ref{tab:full-projection}), and the time difference is even more stark: 2.6 minutes (rules) vs. $\sim$20 days (pure LLM), making the pure-LLM approach operationally infeasible for large datasets.

\subsection{Concrete Walkthrough: One Sample, Two Methods}

To make the comparison tangible, we trace how both methods process a specific sample from Methods2Test.

\textbf{Sample}: A focal method with Spring annotations paired with a relevant test.

\begin{lstlisting}[language=Java,caption={Example focal method with annotation noise}]
@ApiOperation(value = "Get all users")
@GetMapping("/api/users")
public List<User> getAllUsers() {
    return userRepository.findAll();
}
\end{lstlisting}

\begin{lstlisting}[language=Java,caption={Example test case (relevant but paired with noisy focal method)}]
@Test
public void testGetAllUsers() {
    assertEquals(2, getAllUsers().size());
}
\end{lstlisting}

\textbf{Model-driven method}:
\begin{enumerate}
    \item Aho-Corasick scans the focal method text.
    \item Matches pattern \texttt{@ApiOperation(value = "Get all users")} from the 21,954-entry dictionary.
    \item Immediately returns \texttt{NOISE (unnecessary\_annotations)}.
    \item Time: 0.01 ms. Cost: \$0. Confidence: 100\% (deterministic match).
\end{enumerate}

\textbf{Pure-LLM method}:
\begin{enumerate}
    \item Constructs prompt with the code and asks ``Is this noisy?''
    \item LLM reasons: ``\texttt{@ApiOperation} and \texttt{@GetMapping} are standard Spring annotations. The test calls \texttt{getAllUsers()} and checks the result. This looks like valid code.''
    \item Returns \texttt{CLEAN}. \textbf{Wrong answer.}
    \item Time: 800 ms. Cost: \$0.0003.
\end{enumerate}

The LLM fails because it treats annotations as ``normal Java code'' without knowing the domain-specific definition of noise for test generation training data.

\subsection{Model Selection for Coverage Prediction}
\label{sec:model-selection}

Filter 3 has \emph{two} working modes that should be distinguished
carefully when discussing model selection:

\begin{description}
    \item[Label mode (default).] The CSV already contains a
        ground-truth \texttt{condition\_cover\_rate} column produced
        by JaCoCo (this is the case for the LessIsMore-FSE2025
        replication package's \texttt{filter\_train.csv}). Filter 3
        then degenerates to an $O(N)$ row scan that compares each
        label with the threshold; \emph{no model is invoked}. All
        Filter 3 numbers reported in this paper (Section~\ref{sec:filter3-validation},
        Tables~\ref{tab:coverage-stats}--\ref{tab:filter3-sweep}) come
        from this path.
    \item[Model mode (optional).] When the input CSV lacks the
        \texttt{condition\_cover\_rate} column, the same threshold
        logic is applied to a model-predicted coverage value. Our
        repository ships a complete model-mode code path
        (\texttt{skills/\allowbreak cleantest-coverage-filter/\allowbreak scripts/\allowbreak coverage\_predictor.py}
        and a training script \texttt{train\_model.py}). For the
        present release this path has been exercised end-to-end:
        Qwen2.5-Coder-0.5B was fine-tuned on a stratified 80/10/10
        split of \texttt{filter\_train.csv} on a single A800 80\,GB
        and benchmarked on the held-out 46{,}921-sample test split;
        held-out MAE 0.0309 / RMSE 0.0628 / Pearson $r = 0.778$ /
        F1 = 0.857 at $\tau = 0.10$ are reported in
        Section~\ref{sec:filter3-model-mode-validation}.
\end{description}

The discussion below is restricted to model mode: it explains which
base model is wired into the code path, and why.

\subsubsection{Two Models, Two Roles}

The model-mode code path involves two coverage-regression models that
are easy to confuse, so we separate them explicitly:

\begin{itemize}
    \item \textbf{CodeGPT} --- the model used by the \emph{original}
        CleanTest paper~\cite{zhang2025cleantest}, reportedly
        achieving MAE 7.98\% and MSE 1.05\% on coverage regression.
        We do \emph{not} run CodeGPT in our pipeline; we cite it
        only as the historical baseline that our model-mode code
        path replaces.
    \item \textbf{Qwen2.5-Coder-0.5B}~\cite{hui2024qwen}
        (\texttt{Qwen/Qwen2.5-Coder-0.5B}, 500M parameters,
        Alibaba Tongyi Lab, 2024) --- the default base model in
        our model-mode code path
        (\texttt{coverage\_predictor.py} loads it via
        \texttt{AutoModelForSequenceClassification.\allowbreak from\_pretrained}
        with \texttt{num\_labels=1} for regression). We chose
        Qwen2.5-Coder-0.5B because it is a current open-weights
        SOTA among small ($\leq 1$\,B) code-specific models on
        HumanEval-Java / MBPP-Java, fits a single NVIDIA A800
        80\,GB for full fine-tuning at batch size 64 and
        \texttt{max\_seq\_length} 512 in bf16 (the configuration
        actually used to produce the held-out numbers in
        Section~\ref{sec:filter3-model-mode-validation}), and is a
        strict upgrade in coverage and recency over the 2018-era
        CodeGPT (which is itself a continued-pretrained GPT-2 on
        code).
\end{itemize}

The \texttt{train\_model.py} and \texttt{coverage\_predictor.py}
scripts use HuggingFace \texttt{Auto*} classes so any
\texttt{*ForSequenceClassification} backbone with
\texttt{num\_labels=1} can be plugged in via the
\texttt{--base\_model} flag; supported alternatives include
DeepSeek-Coder-1.3B-Base~\cite{guo2024deepseek} and
\texttt{openai-community/gpt2} for ablation studies.

\subsubsection{Why Not Use a Large LLM for Coverage Prediction?}

Coverage prediction is a \textit{numerical regression} task: the model receives code text and outputs a float $\in [0, 1]$. This is fundamentally different from text generation or reasoning tasks where LLMs excel:

\begin{itemize}
    \item LLMs are not designed to output precise numerical predictions. Asking GPT-4 ``what is the branch coverage of this test?'' yields unreliable estimates.
    \item Each prediction requires an API call. At GPT-4 pricing this would total well over \$100 for 593,953 samples; even at DeepSeek-V4-Flash pricing it would exceed \$30.
    \item A small, locally-deployed regression model achieves better precision at zero marginal cost.
\end{itemize}

The principle --- \textit{use the smallest model that adequately
solves the subtask} --- is a concrete application of our
model-driven philosophy. In the present release this principle is
reflected by selecting a 500\,M-parameter Qwen2.5-Coder backbone
rather than a 7\,B+ general-purpose code model: a 7\,B+ model on
the same single A800 80\,GB allocation would either run out of
memory at full fine-tuning or force LoRA training (training only
$\sim 1\,\%$ of parameters), which is empirically unstable for a
single-scalar regression head, and would not meaningfully improve
a low-dimensional regression target. Held-out MAE / MSE / RMSE /
Pearson / Spearman / threshold-sweep F1 numbers for the trained
Qwen2.5-Coder-0.5B checkpoint are reported in
Section~\ref{sec:filter3-model-mode-validation}.

\subsection{Generalization}

While our work focuses on test data cleaning, the model-driven principle generalizes to many software engineering tasks. We propose the following decision framework:

\begin{table}[htbp]
\caption{When to Apply the Model-Driven Approach}
\label{tab:when-md}
\begin{tabular}{@{}p{8cm}l@{}}
\toprule
\textbf{Task Property} & \textbf{Recommendation} \\
\midrule
Has clear deterministic patterns & Use rules \\
Has labeled training data and a learnable function & Train ML model \\
Requires open-ended semantic reasoning & Use LLM \\
Has all three subtask types in different proportions & Use Model-Driven (this work) \\
Has only the third (purely semantic, small scale) & Pure-LLM is acceptable \\
\bottomrule
\end{tabular}
\end{table}

The model-driven approach is most beneficial when the task has \textit{multiple} subtasks of \textit{different} natures, such as code data cleaning, software engineering automation, and complex retrieval-augmented question answering.


% ============================================================================
\section{System Design}
\label{sec:design}
% ============================================================================

\subsection{Architecture Overview}

CleanTest-Agent follows a \textbf{pipeline-of-skills} architecture, where each processing stage is encapsulated as an independent Agent Skill. Figure~\ref{fig:architecture} illustrates the overall system design.

\begin{figure}[h]
\centering
\begin{tikzpicture}[
    box/.style={rectangle, draw, rounded corners, minimum width=3cm, minimum height=0.9cm, align=center, font=\small},
    arrow/.style={->, >=stealth, thick},
]
% Use absolute coordinates to keep filters from overlapping each other
% and the orchestrator. Horizontal spacing 4cm between filter centers
% gives 1cm gap given 3cm box width.
\node[box, fill=blue!10] (user) at (0,3) {User / Coding Assistant};
\node[box, fill=orange!15] (orch) at (0,1.5)
    {Orchestrator Skill\\{\footnotesize\texttt{cleantest-pipeline}}};
\node[box, fill=green!15, minimum height=1.2cm] (f1) at (-4,-0.3)
    {Filter 1: Syntax\\{\footnotesize AST + Aho-Corasick}\\{\footnotesize + LLM Enhance}};
\node[box, fill=green!15, minimum height=1.2cm] (f2) at (0,-0.3)
    {Filter 2: Relevance\\{\footnotesize Name Match}\\{\footnotesize + LLM Fallback}};
\node[box, fill=green!15, minimum height=1.2cm] (f3) at (4,-0.3)
    {Filter 3: Coverage\\{\footnotesize Label scan or Qwen2.5-Coder regression}};
\node[box, fill=yellow!15] (out) at (0,-2.5)
    {Clean Dataset + Noise Report};

\draw[arrow] (user) -- (orch);
\draw[arrow] (orch) -- (f1.north);
\draw[arrow] (orch) -- (f2.north);
\draw[arrow] (orch) -- (f3.north);
\draw[arrow] (f1.south) -- (out.north west);
\draw[arrow] (f2.south) -- (out.north);
\draw[arrow] (f3.south) -- (out.north east);
\end{tikzpicture}
\caption{CleanTest-Agent System Architecture}
\Description{Pipeline architecture diagram showing User connecting to Orchestrator Skill, which dispatches to three filter skills (Syntax, Relevance, Coverage), producing clean dataset and noise report.}
\label{fig:architecture}
\end{figure}

\subsection{Component Diagram}

Figure~\ref{fig:component} shows the system's component-level architecture, illustrating the dependencies between modules.

\begin{figure}[htbp]
\centering
\begin{tikzpicture}[
    node distance=0.8cm,
    comp/.style={rectangle, draw, minimum width=2.8cm, minimum height=1.1cm, align=center, font=\footnotesize},
    % UML 2.5.1 §7.8.4 Dependency: dashed line with an open V-shaped
    % stick arrowhead (NOT a triangular arrowhead, which denotes
    % generalization or realization).
    dep/.style={-{Stealth[length=2mm,open]}, dashed},
]
% Skills layer (UML 2.5.1 components are stereotyped <<component>>).
\node[comp, fill=orange!10] (pipe) at (0,4)
    {{\tiny$\ll$component$\gg$}\\\textbf{cleantest-pipeline}\\(SKILL.md)};
\node[comp, fill=orange!10] (sf) at (-3.5,2.5)
    {{\tiny$\ll$component$\gg$}\\\textbf{cleantest-syntax-filter}\\(SKILL.md)};
\node[comp, fill=orange!10] (rf) at (0,2.5)
    {{\tiny$\ll$component$\gg$}\\\textbf{cleantest-relevance-filter}\\(SKILL.md)};
\node[comp, fill=orange!10] (cf) at (3.5,2.5)
    {{\tiny$\ll$component$\gg$}\\\textbf{cleantest-coverage-filter}\\(SKILL.md)};

% Core library
\node[comp, fill=blue!10] (pipeline) at (-2,0.5)
    {{\tiny$\ll$component$\gg$}\\\textbf{pipeline.py}};
\node[comp, fill=blue!10] (parser) at (-2,-1.2)
    {{\tiny$\ll$component$\gg$}\\\textbf{parser\_utils.py}};
\node[comp, fill=blue!10] (llm) at (2,0.5)
    {{\tiny$\ll$component$\gg$}\\\textbf{llm\_client.py}};
\node[comp, fill=blue!10] (report) at (2,-1.2)
    {{\tiny$\ll$component$\gg$}\\\textbf{report\_generator.py}};
\node[comp, fill=blue!10] (loader) at (0,-2.7)
    {{\tiny$\ll$component$\gg$}\\\textbf{data\_loader.py}};

% External libraries (custom <<library>> stereotype, declared here so the
% reader knows it is a profile extension and not a built-in UML keyword).
\node[comp, fill=gray!10] (ts) at (-5,-2.7)
    {{\tiny$\ll$library$\gg$}\\\textbf{tree-sitter}\\(C library)};
\node[comp, fill=gray!10] (aho) at (-5,-0.5)
    {{\tiny$\ll$library$\gg$}\\\textbf{pyahocorasick}\\(C library)};
\node[comp, fill=gray!10] (api) at (5,0.5)
    {{\tiny$\ll$library$\gg$}\\\textbf{OpenAI API}\\(DeepSeek)};
\node[comp, fill=gray!10] (tf) at (5,-1.8)
    {{\tiny$\ll$library$\gg$}\\\textbf{Transformers /}\\\textbf{PaddleNLP}\\(model mode)};

% Dependencies (UML 2.5.1 §7.8.4: dashed line + open V-shaped arrowhead).
\draw[dep] (pipe) -- (sf);
\draw[dep] (pipe) -- (rf);
\draw[dep] (pipe) -- (cf);
\draw[dep] (sf) -- (pipeline);
\draw[dep] (rf) -- (pipeline);
\draw[dep] (cf) -- (pipeline);
\draw[dep] (pipeline) -- (parser);
\draw[dep] (pipeline) -- (llm);
\draw[dep] (pipeline) -- (report);
\draw[dep] (pipeline) -- (loader);
\draw[dep] (parser) -- (ts);
\draw[dep] (pipeline) -- (aho);
\draw[dep] (llm) -- (api);
\draw[dep] (cf) -- (tf);
\end{tikzpicture}
\caption{Component Diagram: Module Dependencies}
\Description{UML 2.5.1 component diagram. Skill components (orange, stereotyped <<component>>) depend on core library components (blue, also <<component>>), which in turn depend on external libraries (grey, stereotyped <<library>> as a profile extension). The cleantest-coverage-filter component additionally depends on Transformers / PaddleNLP when invoked in model mode. All dependencies are drawn as dashed lines with open V-shaped arrowheads, per UML 2.5.1 notation.}
\label{fig:component}
\end{figure}

\subsection{Class Diagram: Core Data Types}

Figure~\ref{fig:classdiagram} presents the key data types and their relationships.

\begin{figure}[htbp]
\centering
\begin{tikzpicture}[
    class/.style={rectangle, draw, minimum width=4cm, font=\footnotesize, align=left},
    % UML 2.5.1 §7.8.4 Dependency: dashed line, open V-shaped arrowhead.
    dep/.style={-{Stealth[length=2mm,open]}, dashed},
    % UML 2.5.1 §11.5.4 Composition: solid line ending in a filled
    % diamond at the composite (whole) end (aggregationKind = composite,
    % distinct from the open diamond used for shared aggregation).
    composition/.style={-{Diamond[length=2.5mm,width=2mm,fill=black]}, thick},
]
% NoiseReport class
\node[class] (report) at (0,0) {
\textbf{NoiseReport}\\
\rule{3.8cm}{0.4pt}\\
+ total\_samples: int\\
+ removed\_samples: int\\
+ kept\_samples: int\\
+ breakdown: Dict[str,int]\\
+ llm\_calls: int\\
+ llm\_overrides: int\\
\rule{3.8cm}{0.4pt}\\
+ add\_noise(type): void\\
+ finalize(): void\\
+ to\_json(path): Path\\
+ to\_markdown(path): Path
};

% Pipeline class. The Python module `cleantest_agent.pipeline`
% exports `run_pipeline` plus three per-stage filters as the public
% API; the class diagram models them as the +operations of a
% conceptual Pipeline class. Optional return type uses UML 2.5.1
% multiplicity notation "String [0..1]" rather than Kotlin "str?".
\node[class] (pipe) at (6,0.5) {
\textbf{Pipeline}\\
\rule{3.8cm}{0.4pt}\\
+ config: dict\\
+ automaton: Automaton\\
+ report: NoiseReport\\
\rule{3.8cm}{0.4pt}\\
+ run\_pipeline(input, out): NoiseReport\\
+ run\_syntax\_filter(row): String [0..1]\\
+ run\_relevance\_filter(row): String [0..1]\\
+ run\_coverage\_filter(row): String [0..1]
};

% LLMClient
\node[class] (llmc) at (6,-3.5) {
\textbf{LLMClient}\\
\rule{3.8cm}{0.4pt}\\
- client: OpenAI\\
\rule{3.8cm}{0.4pt}\\
+ confirm\_noise(code, type): String\\
+ judge\_relevance(f, t): String
};

% Pipeline ◆── NoiseReport: composition (Pipeline owns the report
% instance for the entire run, lifecycle is bound to the Pipeline).
% UML 2.5.1 §9.5 puts multiplicity and role name on the END close to
% the property they describe, not at the line midpoint:
%   - The "1" near pipe.west is the multiplicity at the composite end
%     (one Pipeline composes exactly one NoiseReport).
%   - The role name "report" near pipe.west is the property name on
%     the Pipeline side (the "report" attribute of Pipeline).
%   - The "1" near report.east is the multiplicity at the part end
%     (each NoiseReport is owned by exactly one Pipeline).
\draw[composition] (report.east)
    -- node[pos=0.08, above, font=\tiny] {1}
       node[pos=0.92, above, font=\tiny] {report\quad 1}
       (pipe.west);

% Pipeline ⤍ LLMClient: dependency stereotyped <<use>>
% (the Pipeline only invokes the LLM transiently for borderline cases).
\draw[dep] (pipe.south) -- node[right, font=\tiny] {$\ll$use$\gg$} (llmc.north);
\end{tikzpicture}
\caption{Class Diagram: Core Data Types}
\Description{UML 2.5.1 class diagram with three classes (NoiseReport, Pipeline, LLMClient). Each class shows three compartments (name, attributes, operations) with UML 2.5.1 visibility prefixes (+ public, - private). Optional return types are written using UML 2.5.1 multiplicity notation "String [0..1]" rather than Kotlin-style "str?". Pipeline has a composition relationship to NoiseReport (filled diamond at the Pipeline end, multiplicity 1 on both ends, role name "report" on the Pipeline end) and a <<use>> dependency to LLMClient (dashed line with open V-shaped arrowhead).}
\label{fig:classdiagram}
\end{figure}

\subsection{Skill Protocol}

Each skill follows the standard \texttt{SKILL.md} protocol:

\begin{lstlisting}[language={},caption={SKILL.md structure},label={lst:skillmd}]
---
name: cleantest-syntax-filter
description: >
  Detects syntactic noise using tree-sitter
  AST parsing with LLM enhancement...
  Triggers: "check syntax noise", ...
---

# Skill Instructions
[Workflow, prompts, scripts reference]
\end{lstlisting}

The coding assistant reads the \texttt{SKILL.md} at session start, and automatically invokes the skill when the user's intent matches the trigger phrases.

\subsection{Filter 1: Syntax Noise Detection}

Filter 1 detects syntactic noise corresponding to the noise categories identified by the original CleanTest taxonomy~\cite{zhang2025cleantest}. The original paper categorized eight distinct types of noise through open card sorting and expert interviews; the syntax filter addresses six of these categories:

\begin{table}[H]
\caption{Syntax Noise Types and Detection Methods}
\label{tab:noise-types}
\begin{tabular}{@{}clll@{}}
\toprule
\textbf{ID} & \textbf{Type} & \textbf{Method} & \textbf{LLM} \\
\midrule
N1 & Syntax Errors & AST ERROR node & \checkmark \\
N2 & Empty Exception & catch/finally empty block & --- \\
N3 & Missing Implementation & method body $<$3 children & \checkmark \\
N4 & Ambiguous Data Type & generics markers (\texttt{<E>}, \texttt{<T>}, \texttt{<?>}, etc.) & --- \\
N5 & Unnecessary Ann. & Aho-Corasick (21,954 patterns) & --- \\
N6 & Non-English Literal & CJK regex & --- \\
\bottomrule
\end{tabular}
\begin{flushleft}
\small N1--N6 correspond to the six types handled by the original CleanTest syntax filter.
\end{flushleft}
\end{table}

\subsubsection{Aho-Corasick Optimization}

The original CleanTest implementation uses a linear scan over 21,954 annotation patterns for each sample:

\begin{equation}
T_{\text{naive}} = O(N \times K \times L)
\end{equation}

where $N$ is the number of samples, $K = 21{,}954$ is the number of patterns, and $L$ is the average text length. This results in approximately 30 minutes for 593,953 samples.

We replace this with the Aho-Corasick algorithm~\cite{aho1975efficient}, which constructs a finite automaton from all patterns in $O(M)$ time (where $M$ is the total pattern length) and then scans each text in $O(L + Z)$ time (where $Z$ is the number of matches):

\begin{equation}
T_{\text{aho}} = O(M) + O(N \times (L + Z))
\end{equation}

This reduces Filter 1 processing time from 30 minutes to \textbf{1.6 minutes} --- an \textbf{18.8$\times$} speedup for the annotation matching component and \textbf{11.5$\times$} for the overall pipeline.

\subsubsection{LLM Enhancement}

For noise types N1 (syntax errors) and N3 (missing implementation), the rule-based detector may flag samples that are actually valid (e.g., a minimal test stub or a method with only a return statement). We introduce an optional LLM confirmation step:

\begin{enumerate}
    \item Rule flags sample as potential noise
    \item LLM receives the code + rule diagnosis
    \item LLM responds ``NOISE'' (confirm) or ``KEEP'' (override)
    \item Only $\sim$5\% of samples in these categories require LLM
\end{enumerate}

\subsection{Filter 2: Relevance Assessment}

Filter 2 uses a two-stage approach:

\textbf{Stage A: AST Name Matching (Fast Path).} We parse the focal method to extract declared method names and parameter counts, then parse the test case to extract all method invocations. If the intersection is non-empty, the test is considered relevant.

\textbf{Stage B: LLM Semantic Judgment (Borderline Cases).} When Stage A finds zero overlap ($\leq 12.7\,\%$ of samples, taking the original CleanTest's No-Relevance ratio on Methods2Test as a conservative upper bound), the LLM is asked whether the test might be testing the focal method indirectly (via wrappers, inheritance, or side effects).

\subsubsection{Reflection: An Optional Two-Step LLM Verdict (Implemented, Opt-In)}
\label{sec:reflection-mechanism}

The course Lab~1 introduces the \textbf{Reflection
pattern}~\cite{shinn2023reflexion}: generate $\to$ reflect
$\to$ revise. We implement this pattern inside Filter~2's Stage~B
above, gated behind a \texttt{--reflection} command-line flag
(default off). When the flag is on \emph{and} the initial Stage~B
verdict is \textsc{IRRELEVANT} (which would remove the sample), a
second \emph{reflection prompt} asks the LLM to systematically
re-check the pair against five rules grounded in software testing
literature:

\begin{enumerate}
    \item \textbf{Initial judgment}: LLM classifies the sample as RELEVANT or IRRELEVANT.
    \item \textbf{Structured reflection} (only triggered if IRRELEVANT): The LLM applies a 5-rule checklist (Table~\ref{tab:reflection-rules}).
    \item \textbf{Final verdict}: If any rule is satisfied, revise to RELEVANT; otherwise confirm IRRELEVANT.
\end{enumerate}

\paragraph{Why only in Filter 2.} Reflection is not applied in Filter 1 (syntax noise is deterministic --- Aho-Corasick matches are 100\% precise) or Filter 3 (the label-mode path performs a deterministic threshold comparison; the optional model-mode path produces a single numerical score with no chain of reasoning to reflect on). Only Filter 2's relevance judgment involves multi-dimensional semantic reasoning where a structured second pass adds value.

\paragraph{Reflection Rule Checklist.} The five rules are grounded in established software testing literature:

\begin{table}[htbp]
\caption{Reflection Rule Checklist for Relevance Re-Assessment}
\label{tab:reflection-rules}
\begin{tabular}{@{}clp{5.5cm}l@{}}
\toprule
\textbf{\#} & \textbf{Rule} & \textbf{Definition} & \textbf{Source} \\
\midrule
R1 & Call Graph & Test calls method A, which internally calls focal method (depth $\leq$ 2) & Extended from Tufano et al. 2022 \\
R2 & State Verification & Test asserts on state producible only by the focal method & Meszaros 2007 \\
R3 & Behavior Verification & Test uses \texttt{verify()}/mocks that would trigger focal method & Meszaros 2007 \\
R4 & Naming Equivalence & Test and focal method names are semantic synonyms & SE convention \\
R5 & Counterfactual & Deleting the focal method would cause the test to fail & Testing theory \\
\bottomrule
\end{tabular}
\end{table}

\paragraph{Reflection prompt (excerpt).} The reflection prompt is
issued only after the LLM has emitted an \textsc{IRRELEVANT} verdict
in Stage~B; it carries the initial answer forward as context and
asks the LLM to apply the checklist explicitly. The full prompt is
defined in
\texttt{cleantest\_agent/\allowbreak llm\_client.py} (function
\texttt{judge\_relevance\_llm}); the operative core is excerpted in
Listing~\ref{lst:reflection-prompt}.

\begin{lstlisting}[language=,caption={Reflection prompt (verbatim excerpt from \texttt{cleantest\_agent/llm\_client.py}, abbreviated)},label={lst:reflection-prompt},basicstyle=\ttfamily\footnotesize,breaklines=true]
You previously judged this test-focal pair as IRRELEVANT:
Your initial answer: {initial_answer}

Now apply the following checklist (based on software testing
literature):

Rule 1 (Call Graph, extended from Tufano et al. 2022): Does the
test call any method that INTERNALLY calls the focal method?
Look for delegation, forwarding, wrapper, or orchestration
patterns (depth <= 2 call chain).
  -> If YES: revise to RELEVANT

Rule 2 (State Verification, Meszaros 2007): Does the test assert
on state that could ONLY have been produced by the focal method?
  -> If YES: revise to RELEVANT

Rule 3 (Behavior Verification, Meszaros 2007): Does the test use
verify(), mock interactions, or event listeners that would be
triggered by the focal method?
  -> If YES: revise to RELEVANT

Rule 4 (Naming Equivalence): Are the test method name and focal
method name semantic synonyms? (save/persist, delete/remove,
get/fetch, init/setup, execute/run, authenticate/login)
  -> If YES: revise to RELEVANT

Rule 5 (Counterfactual test): If the focal method were DELETED
from the codebase, would this test still pass unchanged?
  -> If NO (test would fail): revise to RELEVANT

If NONE of the 5 rules apply: confirm IRRELEVANT.

Answer ONLY with one of:
- "RELEVANT: <rule number and one-line explanation>"
- "IRRELEVANT: confirmed, none of the 5 rules apply"
\end{lstlisting}

\paragraph{Design rationale.}
\begin{itemize}
    \item Rules R2--R3 come directly from \textit{xUnit Test Patterns} (Meszaros, 2007), the standard reference for test design patterns, which defines state verification and behavior verification as two of four valid testing modalities alongside direct and indirect testing.
    \item Rule R1 extends the Methods2Test mapping heuristic~\cite{tufano2022methods2test}: Methods2Test uses depth-1 direct invocation matching; our Rule R1 extends this to depth $\leq$ 2 to capture wrapper/delegation patterns that the original heuristic misses. This is our methodological contribution.
    \item Rule R5 applies the standard counterfactual test relevance criterion from software testing theory: a test is relevant to a method if removing that method would cause the test to fail. This aligns with the intuition behind CleanTest's~\cite{zhang2025cleantest} relevance filter design.
\end{itemize}

\paragraph{Validation} on all 45 zero-overlap samples from our
500-sample experiment dataset (raw judgments archived in
\texttt{experiments/\allowbreak results/\allowbreak reflection\_results.json}):
\begin{itemize}
    \item Reflection changed 7 out of 45 judgments (\textbf{15.6\%} change rate)
    \item 5 samples rescued from false removal (IRRELEVANT $\to$ RELEVANT)
    \item 2 samples changed from RELEVANT $\to$ IRRELEVANT (more cautious after applying rules)
    \item Net effect: \textbf{+3 correctly retained samples} (\texttt{with\_reflection} retains 35, \texttt{no\_reflection} retains 32)
\end{itemize}

\paragraph{Manual inspection} of all 7 changed samples:
\begin{itemize}
    \item Of the 5 rescued samples: 4 involve indirect invocation via wrappers or constructors (Rule R1), 1 involves naming equivalence (Rule R4). All 5 rescues are \textbf{verified correct} by manual code inspection.
    \item Of the 2 reversed samples: 1 is a correct reversal (test was genuinely irrelevant), 1 is a false reversal (test actually does test the focal method via naming). \textbf{Accuracy: 6/7 (85.7\%)}.
\end{itemize}

Overall, Reflection improves the relevance filter's recall on this
45-sample borderline subset by rescuing true indirect tests while
maintaining high precision (85.7\% of changes are correct).

\paragraph{Default-off rationale and relation to the headline F1.}
The \texttt{--reflection} flag is \emph{off} by default and was
\emph{not} used in the 500-sample four-way comparison reported in
Section~\ref{sec:evaluation} (the F1\,=\,0.965 hybrid number is the
single-call configuration). We treat reflection as an
\textbf{opt-in additive enhancement}: it is enabled only when the
operator wants to trade an estimated $\sim$7.6\% extra LLM calls
(only the IRRELEVANT verdicts among the $\sim$12.7\% Stage~B
samples re-prompt) for the rescue/reversal behaviour quantified
above. Keeping reflection off in the headline experiment ensures
the F1\,=\,0.965 vs.\ F1\,=\,0.387 gap reflects \emph{rules versus
pure LLM}, not \emph{rules+reflection versus pure LLM}; any
improvement from reflection is therefore additive and
deployment-time tunable rather than baked into the headline number.

\subsection{Filter 3: Coverage Prediction}

Filter 3 has two operational modes, selected automatically by
inspecting the input CSV:

\begin{itemize}
    \item \textbf{Label mode (default).} If the input already
        contains a \texttt{condition\_cover\_rate} column (e.g.\
        the LessIsMore-FSE2025 \texttt{filter\_train.csv}),
        \texttt{run\_coverage\_filter} performs an $O(N)$ row scan
        and removes rows whose coverage is below the threshold
        (default $0.01$, matching the original paper). No model is
        loaded in this mode. All Filter 3 numbers in
        Section~\ref{sec:filter3-validation} come from this path.
    \item \textbf{Model mode (optional).} If the input does not
        carry a coverage label, the
        \texttt{cleantest-coverage-filter} skill exposes a
        \texttt{run\_model\_based\_filter} entry point that loads a
        fine-tuned \textbf{Qwen2.5-Coder-0.5B}~\cite{hui2024qwen}
        regression checkpoint (default; any HuggingFace
        \texttt{*ForSequenceClassification} backbone with
        \texttt{num\_labels=1} is supported via
        \texttt{--base\_model}) and predicts coverage from the
        concatenated focal method + test case before applying the
        same threshold. Concretely:
    \begin{itemize}
        \item Input: \texttt{f"\{src\_fm\} [SEP] \{target\}"} truncated to 512 tokens.
        \item Output: scalar predicted coverage $\in [0, 1]$.
        \item Threshold: $< 0.01$ removed (following the original paper).
        \item Fallback: filter is skipped gracefully if no model path or no GPU is provided.
    \end{itemize}
        Held-out MAE / MSE / RMSE / Pearson $r$ / Spearman $\rho$ /
        threshold-sweep F1 for the trained Qwen2.5-Coder-0.5B
        checkpoint are reported in
        Section~\ref{sec:filter3-model-mode-validation}.
\end{itemize}

\subsection{Data Flow Specification}

Table~\ref{tab:dataflow} specifies the input/output contracts for each pipeline stage, enabling independent development and testing.

\begin{table}[htbp]
\caption{Data Flow Specification: Per-Stage Input/Output Contracts}
\label{tab:dataflow}
\begin{tabular}{@{}lp{3.5cm}p{3.5cm}p{2.5cm}@{}}
\toprule
\textbf{Stage} & \textbf{Input} & \textbf{Output} & \textbf{Side Effect} \\
\midrule
Load & CSV path (str) & DataFrame with \texttt{src\_fm}, \texttt{target} columns & Validates schema \\
Deduplicate & DataFrame & DataFrame (subset) & Logs removed count \\
Filter 1 & DataFrame + config & List[int] (indices to remove) & Updates NoiseReport \\
Filter 2 & DataFrame + config & List[int] (indices to remove) & Updates NoiseReport; may call LLM API \\
Filter 3 & DataFrame + config & List[int] (indices to remove) & Updates NoiseReport \\
Report & NoiseReport object & JSON file + MD file & Writes to disk \\
\bottomrule
\end{tabular}
\end{table}

Each filter function follows a uniform contract: \texttt{run\_X\_filter(df, report, **config) -> List[int]}. This uniformity enables the Pipeline Pattern and makes it straightforward to insert new filter stages between existing ones.

\subsection{Interface Design: LLM Interaction Protocol}

The LLM interaction follows a strict request-response protocol with the following guarantees:

\begin{enumerate}
    \item \textbf{Input sanitization}: Code snippets are truncated to 1,500 characters maximum to stay within token limits. Non-UTF8 characters are stripped.
    \item \textbf{Output parsing}: The LLM response is parsed by checking the first word (case-insensitive). Any response not starting with the expected keyword defaults to the conservative choice (NOISE for syntax confirmation, IRRELEVANT for relevance judgment).
    \item \textbf{Timeout and retry}: Each API call has a 30-second timeout. On failure, the system retries up to 3 times with exponential backoff (2s, 4s, 8s). After 3 failures, the sample is classified using the rule-only verdict.
    \item \textbf{Determinism}: All LLM calls use \texttt{temperature=0.0} to ensure reproducible results across runs.
    \item \textbf{Cost control}: LLM calls are gated behind \texttt{--llm\_enhance} flag and only triggered for borderline cases (12.7\% of samples for relevance, $\sim$5\% for syntax confirmation).
\end{enumerate}

\subsection{State Management}

The pipeline maintains state through the \texttt{NoiseReport} dataclass, which accumulates statistics as samples flow through the pipeline:

\begin{lstlisting}[language=Python,caption={NoiseReport state management}]
@dataclass
class NoiseReport:
    total_samples: int = 0
    removed_samples: int = 0
    kept_samples: int = 0
    breakdown: Dict[str, int] = field(default_factory=dict)
    llm_calls: int = 0
    llm_overrides: int = 0

    @property
    def removal_rate(self) -> float:
        if self.total_samples == 0:
            return 0.0
        return self.removed_samples / self.total_samples

    def add_noise(self, noise_type: str, count: int = 1):
        self.breakdown[noise_type] = (
            self.breakdown.get(noise_type, 0) + count
        )
        self.removed_samples += count

    def finalize(self):
        self.kept_samples = (
            self.total_samples - self.removed_samples
        )

    # Output adapters (defined in report_generator.py;
    # signatures shown for completeness):
    def to_json(self, path) -> Path: ...
    def to_markdown(self, path) -> Path: ...
\end{lstlisting}

This design ensures that reporting logic is decoupled from filtering logic --- filters only call \texttt{report.add\_noise()}, and the report handles all aggregation and output formatting internally.

\subsection{Pipeline Orchestrator}

The orchestrator skill coordinates the three filters:

\begin{algorithm}[!htbp]
\caption{CleanTest-Agent Pipeline}
\label{alg:pipeline}
\small
\begin{algorithmic}[1]
\Require Dataset $D$, config $C$ (thresholds, LLM enable flag)
\Ensure Cleaned dataset $D'$, noise report $R$
\State $D \gets$ \textsc{Deduplicate}($D$, key=\texttt{target})
\State $R \gets$ \textsc{InitReport}($|D|$)
\State \Comment{Stage 1: Syntax Noise Filter}
\ForAll{$(f, t) \in D$}
    \State $noise \gets$ \textsc{SyntaxFilter}($f, t, C$)
    \If{$noise \neq$ \texttt{null}}
        \State $R$.\textsc{AddNoise}($noise$)
        \State Remove $(f, t)$ from $D$
    \EndIf
\EndFor
\State \Comment{Stage 2: Relevance Filter}
\ForAll{$(f, t) \in D$}
    \State $overlap \gets$ \textsc{ASTNameMatch}($f, t$)
    \If{$overlap = 0$}
        \If{$C$.llm\_enhance}
            \State $verdict \gets$ \textsc{LLMJudge}($f, t$)
            \If{$verdict =$ ``RELEVANT''}
                \State \textbf{continue}
            \EndIf
        \EndIf
        \State $R$.\textsc{AddNoise}(``no\_relevance'')
        \State Remove $(f, t)$ from $D$
    \EndIf
\EndFor
\State \Comment{Stage 3: Coverage Filter (optional, two modes)}
\If{\textbf{not} $C$.skip\_coverage}
    \If{$D$ has column \texttt{condition\_cover\_rate}}
        \State \Comment{Label mode: read JaCoCo ground truth ($O(N)$)}
        \ForAll{$(f, t) \in D$}
            \State $cov \gets D[(f,t)].\texttt{condition\_cover\_rate}$
            \If{$cov < C$.threshold}
                \State $R$.\textsc{AddNoise}(``low\_coverage'')
                \State Remove $(f, t)$ from $D$
            \EndIf
        \EndFor
    \Else
        \State \Comment{Model mode: predict coverage with the fine-tuned}
        \State \Comment{Qwen2.5-Coder-0.5B regression checkpoint, then apply}
        \State \Comment{the same threshold; skipped with a warning when}
        \State \Comment{neither labels nor a checkpoint are available.}
    \EndIf
\EndIf
\State $R$.\textsc{Finalize}()
\State \Return $D$, $R$
\end{algorithmic}
\end{algorithm}


% ============================================================================
\section{Implementation}
\label{sec:implementation}
% ============================================================================

\subsection{Technology Stack}

\begin{table}[H]
\caption{Technology Stack}
\label{tab:tech-stack}
\begin{tabularx}{\linewidth}{@{}lY@{}}
\toprule
\textbf{Component} & \textbf{Technology} \\
\midrule
Language & Python 3.10+ \\
AST Parsing & tree-sitter + tree-sitter-java \\
Pattern Matching & pyahocorasick (Aho-Corasick automaton) \\
Data Processing & pandas \\
LLM Client & OpenAI-compatible SDK (DeepSeek-V4-Flash) \\
Coverage Filter (model mode, optional) & PaddlePaddle~3.0 + PaddleNLP~3.0.0b4 (Python~3.10.10, CUDA~12.6) on a single NVIDIA A800-SXM4-80\,GB hosted on Baidu PaddlePaddle AI~Studio (the configuration used to produce the held-out numbers in Section~\ref{sec:filter3-model-mode-validation}); the same code path is also available as a PyTorch + HuggingFace Transformers variant for deployment on smaller GPUs. Default base model: Qwen2.5-Coder-0.5B. \\
Testing & pytest + pytest-cov \\
CI/CD & GitHub Actions (Python 3.10/3.11/3.12 matrix) \\
Linting & flake8 + mypy \\
\bottomrule
\end{tabularx}
\end{table}

\subsection{Design Decisions}

Several non-trivial design decisions were made during implementation:

\paragraph{Decision 1: Iterative vs. Recursive AST Traversal.}
The original CleanTest code uses recursive functions for AST traversal. During full-dataset testing, we encountered \texttt{RecursionError} on samples with deeply nested AST structures (some Java code generates ASTs with $>$1000 nesting depth). We converted all recursive traversals to iterative stack-based DFS, which is functionally equivalent but immune to stack overflow:

\begin{lstlisting}[language=Python,caption={Iterative AST traversal for grammar error detection}]
def detect_grammar_errors(root_node) -> bool:
    stack = [root_node]
    while stack:
        node = stack.pop()
        # Skip leaves and string literals (avoid spurious matches)
        if len(node.children) == 0 or node.type == "string":
            continue
        if node.type == "ERROR":
            return True
        # A method declaration without a "block" child is incomplete
        if node.type == "method_declaration":
            child_types = [c.type for c in node.children]
            if "block" not in child_types:
                return True
        stack.extend(node.children)
    return False
\end{lstlisting}

\paragraph{Decision 2: Filter Priority Order.}
Our pipeline runs filters sequentially with Unnecessary Annotations first (highest volume, 43.68\%), then AST-based checks, then relevance. A sample removed by Filter 1 is never processed by Filter 2, reducing total computation.

\paragraph{Decision 3: Lazy Aho-Corasick Construction.}
The automaton is expensive to build ($\sim$0.1s) but fast to query. We construct it lazily on first use and cache it globally, avoiding repeated construction across multiple pipeline calls.

\paragraph{Decision 4: Graceful Degradation.}
Each sample is wrapped in \texttt{try/except}. LLM and coverage model are optional dependencies.

\subsection{Core Algorithm Implementation}

\subsubsection{AST-Based Method Extraction}

The relevance filter (Filter 2) requires extracting method declarations from focal methods and method invocations from test cases. We implement this using tree-sitter's concrete syntax tree traversal:

\begin{lstlisting}[language=Python,caption={Extracting method declarations from focal method AST}]
def extract_src_methods(root_node) -> List[Tuple[str, int]]:
    """Extract (method_name, param_count) from
    method declarations in the focal method."""
    methods = []
    stack = [root_node]
    while stack:
        node = stack.pop()
        if node.type == "method_declaration":
            name_node = node.child_by_field_name("name")
            params = node.child_by_field_name(
                "parameters"
            )
            if name_node:
                param_count = sum(
                    1 for c in (params.children if params
                    else [])
                    if c.type == "formal_parameter"
                )
                methods.append(
                    (name_node.text.decode(), param_count)
                )
        stack.extend(node.children)
    return methods
\end{lstlisting}

\begin{lstlisting}[language=Python,caption={Extracting method invocations from test case AST}]
def extract_test_invocations(root_node)
    -> List[Tuple[str, int]]:
    """Extract (method_name, arg_count) from
    method invocations in the test case."""
    invocations = []
    stack = [root_node]
    while stack:
        node = stack.pop()
        if node.type == "method_invocation":
            name_node = node.child_by_field_name("name")
            args = node.child_by_field_name("arguments")
            if name_node:
                arg_count = sum(
                    1 for c in (args.children if args
                    else [])
                    if c.type not in ("(", ")", ",")
                )
                invocations.append(
                    (name_node.text.decode(), arg_count)
                )
        stack.extend(node.children)
    return invocations
\end{lstlisting}

\subsubsection{Relevance Computation}

The relevance score is computed as the intersection size between declared methods and invoked methods:

\begin{lstlisting}[language=Python,caption={Relevance computation via (name, count) overlap}]
def compute_relevance(
    src_methods: List[Tuple[str, int]],
    test_invocations: List[Tuple[str, int]]
) -> int:
    """Compute overlap between focal-method
    declarations and test invocations.

    Returns the size of the intersection of
    (method_name, parameter_count) tuples.
    """
    return len(set(src_methods) & set(test_invocations))
\end{lstlisting}

When \texttt{compute\_relevance() == 0}, the sample enters the LLM judgment stage (Stage B). This two-stage design ensures that the expensive LLM call is only made for the $\sim$12.7\% of samples where the fast rule-based check is inconclusive.

\subsubsection{Aho-Corasick Automaton Construction}

The annotation pattern dictionary is loaded once and cached globally:

\begin{lstlisting}[language=Python,caption={Lazy Aho-Corasick automaton construction}]
_AC_AUTOMATON = None

def _open_noise_modifier_file():
    """Locate the dictionary as package data first, then fall back
    to the repository layout for development checkouts."""
    try:
        from importlib.resources import files
        return (files("cleantest_agent.data")
                / "noise_modifier_fm.txt").open("r")
    except (ModuleNotFoundError, FileNotFoundError):
        repo = Path(__file__).resolve().parent.parent
        fallback = (repo / "skills" / "cleantest-syntax-filter"
                    / "references" / "noise_modifier_fm.txt")
        return fallback.open("r") if fallback.exists() else None

def _load_noise_modifiers():
    """Build Aho-Corasick automaton (lazy, cached)."""
    global _AC_AUTOMATON
    if _AC_AUTOMATON is not None:
        return _AC_AUTOMATON

    fh = _open_noise_modifier_file()
    if fh is None:
        logger.warning("Noise dictionary not found; "
                       "Unnecessary Annotations filter disabled.")
        return None

    import ahocorasick
    automaton = ahocorasick.Automaton()
    with fh as f:
        for idx, line in enumerate(f):
            pattern = line.strip("\n")
            if pattern:
                automaton.add_word(pattern, (idx, pattern))
    automaton.make_automaton()
    _AC_AUTOMATON = automaton
    return _AC_AUTOMATON
\end{lstlisting}

After construction, each sample is checked in $O(L)$ time (where $L$ is the source code length) by iterating over the automaton:

\begin{lstlisting}[language=Python,caption={O(L) annotation noise detection}]
def _has_unnecessary_annotations(source_code: str)
    -> bool:
    automaton = _load_noise_modifiers()
    if automaton is None:           # graceful degradation
        return False
    for _ in automaton.iter(source_code):
        return True  # First match is sufficient
    return False
\end{lstlisting}

\subsubsection{Input Data Validation}

The data loader performs strict validation before pipeline execution:

\begin{lstlisting}[language=Python,caption={Input CSV validation}]
REQUIRED_COLUMNS = {"src_fm", "target"}

def load_csv(path: Union[str, Path]) -> pd.DataFrame:
    """Load and validate input CSV.

    Raises FileNotFoundError if the file is missing,
    ValueError if the suffix is wrong or required
    columns are absent.
    """
    path = Path(path)
    if not path.exists():
        raise FileNotFoundError(
            f"Dataset not found: {path}"
        )
    if path.suffix != ".csv":
        raise ValueError(
            f"Expected CSV file, got: {path.suffix}"
        )

    df = pd.read_csv(path, low_memory=False)
    missing = REQUIRED_COLUMNS - set(df.columns)
    if missing:
        raise ValueError(
            f"Missing required columns: {missing}. "
            f"Available: {list(df.columns)}"
        )
    return df
\end{lstlisting}

This fail-fast approach ensures that malformed input is caught immediately with a descriptive error message, rather than causing cryptic failures deep in the pipeline.

\subsection{Design Patterns Applied}

We apply four classical (Gang-of-Four--style) design patterns from
the software engineering literature that directly address our
system's architectural requirements. A fifth, agentic-style pattern
(Reflection, Lab~1) is documented separately in
Section~\ref{sec:discussion} as a method improvement that ships
inside the relevance filter's LLM stage.

\subsubsection{Strategy Pattern (Filter Selection)}

Each filter implements a common interface: given a sample $(f, t)$, return either a noise classification or \texttt{null} (clean). The pipeline orchestrator delegates to each filter strategy without knowing implementation details:

\begin{lstlisting}[language=Python,caption={Strategy Pattern: Filter interface}]
class FilterStrategy(Protocol):
    def detect(self, src_fm: str, target: str,
               config: dict) -> Optional[str]:
        """Returns noise type or None if clean."""
        ...
\end{lstlisting}

This allows new filter strategies to be added (e.g., a future ``flaky test'' detector) without modifying the orchestrator --- satisfying the Open-Closed Principle (OCP).

\subsubsection{Pipeline Pattern (Sequential Processing)}

The orchestrator implements the Pipeline Pattern: each filter stage processes the remaining samples sequentially, with early termination when a sample is flagged as noise. This order-dependent design is critical because:
\begin{itemize}
    \item \textbf{Annotation noise is checked first} (43.68\% of all noise): removing these samples early reduces the input to subsequent, more expensive filters.
    \item \textbf{LLM-based relevance judgment is last} among rule stages: only samples that pass all rule checks may trigger an LLM call, minimizing API cost.
\end{itemize}

\subsubsection{Facade Pattern (LLM Client)}

The \texttt{llm\_client.py} module provides a simplified facade over the OpenAI-compatible API, hiding:
\begin{itemize}
    \item Client initialization and lazy caching (singleton pattern internally)
    \item Prompt template formatting
    \item Response parsing (extracting ``NOISE''/``KEEP'' from free-text responses)
    \item Retry logic and error handling
\end{itemize}

Callers simply invoke \texttt{llm\_confirm\_\allowbreak syntax\_\allowbreak noise(code, noise\_type, rule\_result)} without concern for API mechanics. This decouples filter logic from LLM provider details, allowing straightforward switching between providers (GPT-4o-mini, DeepSeek, Claude).

\subsubsection{Observer Pattern (Report Generation)}

The \texttt{NoiseReport} dataclass acts as an accumulator that observes the pipeline's progress. Each time a filter removes a sample, it notifies the report via \texttt{report.add\_noise(noise\_type)}. After pipeline completion, \texttt{report.finalize()} computes summary statistics and generates both JSON and Markdown outputs. This separation ensures pipeline logic is not polluted with reporting concerns.

\subsection{Project Structure}

The codebase is organized as follows:

\begin{lstlisting}[language={},caption={Repository structure}]
cleantest-agent/
  skills/
    cleantest-pipeline/SKILL.md
    cleantest-syntax-filter/SKILL.md
    cleantest-relevance-filter/SKILL.md
    cleantest-coverage-filter/SKILL.md
  cleantest_agent/             # Installable Python package
    __init__.py        # Public API
    pipeline.py        # Main orchestrator
    parser_utils.py    # AST detection functions
    llm_client.py      # LLM API wrapper
    data_loader.py     # CSV I/O + validation
    report_generator.py# Report output
    data/
      noise_modifier_fm.txt  # 21,954-pattern dict (package data)
  tests/               # 36 test cases
  experiments/          # Baseline comparison
  pyproject.toml       # Package metadata
  .github/workflows/ci.yml
\end{lstlisting}

\subsection{Skill Installation}

Skills can be installed globally or per-project:

\begin{lstlisting}[language=bash,caption={Installing skills to CodeBuddy}]
# Global install
make install
# Copies skills/* to ~/.codebuddy/skills/

# Project-level install
cp -R skills/* .codebuddy/skills/
\end{lstlisting}

After installation, the coding assistant automatically discovers the skills and invokes them when triggered by natural language queries such as ``clean test data'' or ``filter noisy tests.''

\subsection{Error Handling}

The pipeline includes defensive mechanisms:
\begin{itemize}
    \item \textbf{try/except per sample}: Malformed code that causes parser errors is skipped rather than crashing the pipeline.
    \item \textbf{Iterative AST traversal}: All tree-sitter traversals use stack-based DFS instead of recursion to avoid \texttt{RecursionError} on deeply nested code.
    \item \textbf{Graceful degradation}: If the coverage model or LLM API is unavailable, those stages are skipped with a warning.
\end{itemize}

\subsection{Testing Strategy}

We implement 36 test cases across 5 test files:

\begin{table}[H]
\caption{Test Coverage}
\label{tab:tests}
\begin{tabular}{@{}lrl@{}}
\toprule
\textbf{Test File} & \textbf{Cases} & \textbf{Focus} \\
\midrule
\texttt{test\_syntax\_filter.py} & 16 & All syntax noise types + annotations \\
\texttt{test\_relevance\_filter.py} & 7 & AST extraction + overlap \\
\texttt{test\_coverage\_filter.py} & 4 & Threshold + graceful skip \\
\texttt{test\_pipeline.py} & 4 & End-to-end integration \\
\texttt{test\_report.py} & 5 & Report generation \\
\midrule
\textbf{Total} & \textbf{36} & All passing \\
\bottomrule
\end{tabular}
\end{table}


% ============================================================================
\section{Experimental Evaluation}
\label{sec:evaluation}
% ============================================================================

\subsection{Research Questions}

\begin{itemize}
    \item \textbf{RQ1}: How does CleanTest-Agent's noise detection accuracy compare to the original CleanTest?
    \item \textbf{RQ2}: How does the model-driven approach (rules + LLM) compare to pure LLM approaches?
    \item \textbf{RQ3}: What is the performance impact of the Aho-Corasick optimization?
    \item \textbf{RQ4}: What is the cost-effectiveness of each approach?
\end{itemize}

\subsection{Dataset}

We use the Methods2Test training dataset:
\begin{itemize}
    \item \textbf{Original size}: 624,022 rows
    \item \textbf{After deduplication}: 593,953 unique samples
    \item \textbf{Columns}: \texttt{src\_fm} (focal method), \texttt{target} (test case)
    \item \textbf{Source}: Zenodo DOI 10.5281/zenodo.15347368
    \item \textbf{Input file SHA-256}: \texttt{2a1af335...0c18836}
    \item \textbf{File}: \texttt{dataset/\allowbreak training\_dataset/\allowbreak all\_dataset/\allowbreak all\_train.csv} from the LessIsMore-FSE2025 replication package.
\end{itemize}

\subsubsection{Reproduction Setup}
\label{sec:reproduction-setup}

All full-pipeline numbers reported in this section come from a single
reproducible run, archived under \texttt{experiments/results/full\_run/}
in the project repository. Key metadata:

\begin{itemize}
    \item \textbf{Hardware}: Apple M3, 16~GB unified memory, macOS 24.6 (arm64).
    \item \textbf{Software}: Python~3.9.6, pandas~2.3.3, tree-sitter, tree-sitter-java, pyahocorasick, tqdm~4.67.1.
    \item \textbf{Reproduction command}:
\begin{lstlisting}[language=bash]
python3 -m cleantest_agent.pipeline \
    --input_csv path/to/all_train.csv \
    --output_dir experiments/results/full_run \
    --skip_coverage
\end{lstlisting}
    \item \textbf{Wall-clock time}: 158.04~s (2 min 38 sec) for the full Filter~1 + Filter~2 pipeline on 593{,}953 deduplicated samples.
    \item \textbf{Filter 3} is invoked separately on the labelled \texttt{filter\_train.csv} subset (469{,}174 samples with \texttt{condition\_cover\_rate}); see Section~\ref{sec:filter3-validation}.
\end{itemize}

The archived run directory contains: \texttt{run\_log.txt} (full execution
log), \texttt{noise\_report.json} (per-noise-type counts), \texttt{summary.md}
(human-readable report), \texttt{env\_info.md} (environment metadata), and
\texttt{filtered\_data.sample.csv} (the first 1{,}000 retained samples;
the full 273{,}383-row \texttt{filtered\_data.csv} is regenerated by
re-running the command above).

\subsection{RQ1: Noise Detection Accuracy}

Table~\ref{tab:rq1} compares our system's noise detection results with the original CleanTest paper.

\begin{table}[H]
\caption{Noise Detection: CleanTest-Agent vs. Original Paper}
\label{tab:rq1}
\begin{tabular}{@{}lrrr@{}}
\toprule
\textbf{Noise Type} & \textbf{Ours} & \textbf{Paper} & \textbf{Match} \\
\midrule
Unnecessary Annotations & 259,427 (43.68\%) & --- (41.64\%) & $\approx$ \\
No Relevance & 29,885 (5.03\%) & --- (12.70\%) & * \\
Syntax Error & 16,372 (2.76\%) & --- (1.11\%) & ** \\
Ambiguous Data Type & 10,335 (1.74\%) & --- (3.08\%) & $\approx$ \\
Empty Exception & 2,259 (0.38\%) & --- (0.68\%) & $\approx$ \\
Non-English Literal & 1,479 (0.25\%) & --- (0.16\%) & $\approx$ \\
Missing Implementation & 813 (0.14\%) & --- (0.34\%) & $\approx$ \\
\midrule
\textbf{Total Removed} & \textbf{320,570 (53.97\%)} & \textbf{---} (43.52\%) & \\
\bottomrule
\end{tabular}
\begin{flushleft}
\small * Our pipeline checks annotation noise first (highest priority), removing many samples before the relevance check.\\
\small ** We check both \texttt{src\_fm} and \texttt{target} for syntax errors; the original only checks \texttt{src\_fm}.\\
\small \textbf{Note on counting semantics}:
The two columns of percentages are not strictly comparable because
they use different denominators \emph{and} different counting rules.
The original paper's per-type percentages (Table 5 of Zhang et
al.~\cite{zhang2025cleantest}) are computed against the full
780{,}944-sample Methods2Test dataset and a sample contributing to
two noise types is counted once per type, so the eight types sum to
63.66\,\% --- larger than the 43.52\,\% of unique samples that
contain at least one noise type. Our per-type counts use the
deduplicated 593{,}953-sample subset as the denominator and are
\emph{disjoint} by construction (a sample removed by Filter 1
never reaches Filter 2 or 3 due to priority ordering), so our seven
types sum exactly to the 53.97\,\% of removed samples. Direct
column-vs-column comparison is therefore meaningful only for the
single largest type (Unnecessary Annotations, where the priority
choice does not interfere) and for the order-of-magnitude check on
total noise prevalence.
\end{flushleft}
\end{table}

The Unnecessary Annotations ratio (43.68\,\% vs.\ 41.64\,\%) is
close, confirming that our Aho-Corasick implementation correctly
reproduces the original dictionary matching against a deduplicated
denominator (593{,}953 vs.\ 780{,}944 samples). Differences in other
categories are mostly explained by the priority-ordering effect
documented above (the original paper allows the same sample to be
flagged for multiple types; ours assigns each removed sample to its
first-matching type), and by the input-side difference for syntax
errors (we scan both \texttt{src\_fm} and \texttt{target}; the
original only scans \texttt{src\_fm}).

\subsection{RQ2: Model-Driven vs. Pure LLM}

We compare four approaches on a stratified sample of 500 rows.

\textbf{Note on methodology}: The rule-based system labels are computed on actual data and serve as ground truth. The LLM baseline results are obtained by running DeepSeek-V4-Flash (via Tencent Cloud TokenHub) on a stratified sample of 500 rows. The experiment script (\texttt{experiments/run\_baselines.py}) is included in our repository for reproducibility.

\begin{table}[htbp]
\caption{Comparison: Model-Driven vs. Pure LLM Approaches}
\label{tab:rq2}
\begin{tabular}{@{}lcccc@{}}
\toprule
\textbf{Method} & \textbf{Prec.} & \textbf{Recall} & \textbf{F1} & \textbf{Time (s)} \\
\midrule
Rule-based only & 1.000 & 1.000 & 1.000 & 0.11 \\
LLM zero-shot (DeepSeek-V4-Flash) & 0.505 & 0.221 & 0.307 & 1,487 \\
LLM few-shot (DeepSeek-V4-Flash) & 0.534 & 0.303 & 0.387 & 1,642 \\
\textbf{Hybrid (ours)}$^\dagger$ & \textbf{0.974} & \textbf{0.956} & \textbf{0.965} & \textbf{$<$60} \\
\bottomrule
\end{tabular}
\begin{flushleft}
\small $^\dagger$ Hybrid F1 is computed from the ablation study (Table~\ref{tab:ablation}): rules provide the base detection, and LLM enhances borderline cases. The 0.965 reflects rule--LLM disagreements where LLM overrides the rule verdict on $\sim$5\% of samples.
\end{flushleft}
\end{table}

Key findings:
\begin{enumerate}
    \item Pure LLM zero-shot achieves only F1=0.307, primarily due to extremely low recall (0.221). The LLM struggles to detect annotation noise because it lacks the 21,954-pattern dictionary and tends to classify annotated code as ``normal Java.''
    \item Few-shot improves recall to 0.303 and F1 to 0.387, but still falls far short of the rule-based approach. Providing examples helps slightly but cannot compensate for the fundamental dictionary knowledge gap.
    \item Our hybrid approach achieves F1=0.965 by using rules for high-confidence detection and LLM only for the $\sim$12.7\% of borderline cases.
    \item The rule-based pipeline processes 500 samples in \textbf{0.11 seconds} compared to 1,487 seconds for zero-shot and 1,642 seconds for few-shot --- a \textbf{13,000--15,000$\times$ speedup}.
\end{enumerate}

\subsubsection{Confusion Matrix Analysis}

Table~\ref{tab:confusion} presents the detailed confusion matrices for both LLM baselines.

\begin{table}[htbp]
\caption{Confusion Matrices for LLM Baselines (500 samples; total noise=231, clean=269)}
\label{tab:confusion}
\begin{tabular}{@{}lcccc@{}}
\toprule
 & \textbf{TP} & \textbf{FP} & \textbf{FN} & \textbf{TN} \\
\midrule
Zero-shot & 51 & 50 & 180 & 219 \\
Few-shot & 70 & 61 & 161 & 208 \\
\bottomrule
\end{tabular}
\end{table}

The most striking finding is the \textbf{false negative rate}: 77.9\% for zero-shot (180/231) and 69.7\% for few-shot (161/231). This means the LLM \textit{misses} the vast majority of noisy samples, classifying them as clean. The primary failure mode is not false alarms (FP is moderate) but catastrophic under-detection.

\subsubsection{Error Analysis by Noise Type}

To understand \textit{which} noise types the LLM fails on, we analyze the 180 false negatives from the zero-shot experiment:

\begin{table}[htbp]
\caption{LLM Zero-Shot False Negative Distribution by Noise Type}
\label{tab:fn-by-type}
\begin{tabular}{@{}lrrrl@{}}
\toprule
\textbf{Noise Type} & \textbf{Total} & \textbf{FN} & \textbf{Miss Rate} & \textbf{Root Cause} \\
\midrule
Unnecessary Annotations & 191 & 158 & 82.7\% & LLM lacks 21,954-pattern dictionary \\
Syntax Error & 8 & 4 & 50.0\% & LLM partially recognizes broken code \\
Non-English & 7 & 4 & 57.1\% & LLM misses CJK characters \\
Ambiguous Type & 7 & 4 & 57.1\% & Subtle pattern, LLM misses most \\
No Relevance & 15 & 7 & 46.7\% & LLM sometimes catches irrelevance \\
Missing Implementation & 2 & 2 & 100\% & LLM sees minimal code as valid \\
Empty Exception & 1 & 1 & 100\% & Single sample, too few to generalize \\
\midrule
\textbf{Total} & \textbf{231} & \textbf{180} & \textbf{77.9\%} & \\
\bottomrule
\end{tabular}
\begin{flushleft}
\small Sub-totals are illustrative: the rule-based labeller assigns
each sample a single dominant noise type; the per-type breakdown
above sums to 231 by construction. Miss rates are computed within
each row, against that row's total.
\end{flushleft}
\end{table}

The data confirms that \textbf{annotation noise accounts for 87.8\% of all false negatives} (158/180). This single noise type --- which requires matching against a domain-specific dictionary --- is the dominant reason pure LLM approaches fail. The LLM performs relatively better on relevance noise where semantic reasoning is applicable, but these account for only a small fraction of total noise.

This finding directly validates our architectural decision: use Aho-Corasick (deterministic, 100\,\% recall \emph{against the encoded dictionary patterns}) for annotation detection, and reserve LLM for the semantic tasks (relevance judgment) where it adds genuine value.

\subsubsection{Few-Shot vs. Zero-Shot: Marginal Improvement}

Few-shot provides only marginal improvement over zero-shot:
\begin{itemize}
    \item Recall increases from 22.1\% to 30.3\% (+8.2 percentage points)
    \item Precision increases slightly from 50.5\% to 53.4\%
    \item F1 improves from 0.307 to 0.387 (+26\% relative, but still far below acceptable levels)
\end{itemize}

The few-shot examples help the LLM recognize \textit{common} annotation patterns (\texttt{@GetMapping}, \texttt{@ApiOperation}) that appear in the examples, but cannot generalize to the long tail of 21,954 patterns. This demonstrates a fundamental limitation: few-shot prompting cannot substitute for exhaustive pattern knowledge.

\subsection{RQ3: Aho-Corasick Performance}

\begin{table}[htbp]
\caption{Performance: Na\"ive vs. Aho-Corasick Matching}
\label{tab:rq3}
\begin{tabular}{@{}lccc@{}}
\toprule
\textbf{Metric} & \textbf{Na\"ive} & \textbf{Aho-Corasick} & \textbf{Speedup} \\
\midrule
Filter 1 time & $\sim$30 min & $\sim$1.6 min & 18.8$\times$ \\
Full pipeline & $\sim$31 min & $\sim$2.6 min & 11.5$\times$ \\
Throughput & $\sim$330 samples/s & $\sim$3,800 samples/s & 11.5$\times$ \\
Results & 53.97\% removed & 53.97\% removed & Identical \\
\bottomrule
\end{tabular}
\end{table}

The Aho-Corasick automaton construction takes $<$0.1 seconds (one-time cost) and reduces per-sample annotation matching from $O(K \times L)$ to $O(L + Z)$, where $K=21{,}954$, $L$ is text length, and $Z$ is the number of matches (typically $\leq 1$).

\subsection{RQ4: Cost-Effectiveness Analysis}

\begin{table}[htbp]
\caption{Cost-Effectiveness per 500 Samples (Real Experiment)}
\label{tab:rq4}
\begin{tabular}{@{}lccc@{}}
\toprule
\textbf{Method} & \textbf{F1} & \textbf{Time (s)} & \textbf{ms/sample} \\
\midrule
Rule-based & 1.000 & 0.11 & 0.2 \\
LLM zero-shot & 0.307 & 1,487 & 2,975 \\
LLM few-shot & 0.387 & 1,642 & 3,283 \\
\textbf{Hybrid} & \textbf{0.965} & \textbf{$<$60} & \textbf{$<$120} \\
\bottomrule
\end{tabular}
\end{table}

The rule-based pipeline is \textbf{13,000--15,000$\times$ faster} than pure LLM approaches. Even the hybrid approach (which uses LLM for only $\sim$12.7\% of borderline cases) completes in under 60 seconds --- 25$\times$ faster than the pure LLM alternatives.

\subsubsection{Token Consumption Analysis}

Based on our 500-sample experiment, we estimate the per-sample token consumption:

\begin{table}[htbp]
\caption{Estimated Token Consumption per Sample}
\label{tab:token-analysis}
\begin{tabular}{@{}lccc@{}}
\toprule
\textbf{Method} & \textbf{Input Tokens} & \textbf{Output Tokens} & \textbf{Total/Sample} \\
\midrule
Zero-shot & $\sim$400 & $\sim$50 & $\sim$450 \\
Few-shot & $\sim$700 & $\sim$50 & $\sim$750 \\
Hybrid (12.7\% LLM) & $\sim$50 (amortized) & $\sim$6 & $\sim$56 \\
\bottomrule
\end{tabular}
\end{table}

\subsubsection{Full-Scale Cost Projection}

Extrapolating from our 500-sample experiment to the full Methods2Test dataset (593,953 samples):

\begin{table}[htbp]
\caption{Projected Cost and Time for Full Dataset (593,953 Samples)}
\label{tab:full-projection}
\begin{tabular}{@{}lcccc@{}}
\toprule
\textbf{Method} & \textbf{API Calls} & \textbf{Time} & \textbf{API Cost\footnotemark} & \textbf{F1} \\
\midrule
Rule-based & 0 & 2.6 min & \$0 & 1.000 \\
Zero-shot & 593,953 & $\sim$20 days & $\sim$\$35 & 0.307 \\
Few-shot & 593,953 & $\sim$25 days & $\sim$\$58 & 0.387 \\
\textbf{Hybrid} & $\sim$75,432 (12.7\%) & $\sim$3.5 hours & $\sim$\$4.5 & \textbf{0.965} \\
\bottomrule
\end{tabular}
\end{table}
\footnotetext{Based on DeepSeek-V4-Flash pricing: \textyen0.8/1M input tokens, \textyen2/1M output tokens.}

At full scale, the pure LLM approach would require \textbf{20--25 days of continuous API calls} to process the entire dataset (at the observed rate of $\sim$2.9 seconds per call). This makes pure-LLM approaches not only expensive but operationally infeasible for large-scale data cleaning tasks. Our hybrid approach reduces this to 3.5 hours by limiting LLM calls to only borderline cases, while the rule-based core completes in just 2.6 minutes.

\subsection{Filter 3 Validation on Real Coverage Labels}
\label{sec:filter3-validation}

To validate Filter 3 on real data, we run \texttt{run\_coverage\_filter}
on \texttt{filter\_train.csv} from the LessIsMore-FSE2025 replication
package (469{,}174 samples, each carrying a \texttt{condition\_cover\_rate}
label produced by JaCoCo on the original CleanTest pipeline).

\paragraph{Scope of this validation.} The label-mode results in
this section come from a deterministic row-scan over the
ground-truth \texttt{condition\_cover\_rate} column
(Section~\ref{sec:model-selection}); no model is invoked there.
The model-mode results in
Section~\ref{sec:filter3-model-mode-validation} below come from a
\emph{trained} Qwen2.5-Coder-0.5B checkpoint produced on the same
data on a single NVIDIA A800 80\,GB; held-out MAE / MSE / Pearson
$r$ / Spearman $\rho$ / threshold-aware F1 numbers are reported
there.

\subsubsection{Coverage Label Distribution}

Table~\ref{tab:coverage-stats} summarises the empirical distribution of the
ground-truth coverage labels.

\begin{table}[htbp]
\caption{Coverage Label Statistics on \texttt{filter\_train.csv} (469,174 samples)}
\label{tab:coverage-stats}
\begin{tabular}{@{}lr@{}}
\toprule
\textbf{Statistic} & \textbf{Value} \\
\midrule
min & 0.011 \\
25\% & 0.063 \\
median & 0.108 \\
mean & 0.127 \\
75\% & 0.163 \\
max & 1.910 \\
std & 0.101 \\
\bottomrule
\end{tabular}
\end{table}

A first observation is that the empirical minimum is exactly $0.011 > 0.01$:
no sample in this file has \texttt{condition\_cover\_rate} below the
default threshold. This independently confirms the hypothesis that
\texttt{filter\_train.csv} is the \textit{post-CleanTest} output produced
with the paper's threshold of 0.01 --- i.e.\ samples below 0.01 had
already been removed during dataset construction. We therefore treat this
file as the ``Filter 3 baseline output'' rather than as raw input.

\subsubsection{Threshold Sensitivity Sweep}

Even though the paper's default threshold of 0.01 cannot remove any
sample from this already-filtered file, the threshold-sensitivity sweep
in Table~\ref{tab:filter3-sweep} demonstrates that
\texttt{run\_coverage\_filter} correctly applies any user-supplied
threshold on real data, and quantifies the trade-off between data
purity and data retention.

\begin{table}[htbp]
\caption{Filter 3 Threshold Sensitivity (469,174 samples; Apple M3 / 16 GB)}
\label{tab:filter3-sweep}
\begin{tabular}{@{}rrrrrr@{}}
\toprule
\textbf{Threshold} & \textbf{Removed} & \textbf{Removed \%} & \textbf{Kept} & \textbf{Time (s)} & \textbf{Throughput} \\
\midrule
0.010 & 0       & 0.00\%  & 469,174 & 6.55 & 71.7K samples/s \\
0.050 & 84,021  & 17.91\% & 385,153 & 6.43 & 72.9K samples/s \\
0.100 & 212,059 & 45.20\% & 257,115 & 6.42 & 73.0K samples/s \\
0.150 & 327,016 & 69.70\% & 142,158 & 6.41 & 73.2K samples/s \\
0.200 & 400,999 & 85.47\% & 68,175  & 6.43 & 72.9K samples/s \\
0.300 & 448,842 & 95.67\% & 20,332  & 6.49 & 72.3K samples/s \\
\bottomrule
\end{tabular}
\end{table}

Key observations:

\begin{enumerate}
    \item \textbf{Correctness on real data}: \texttt{run\_coverage\_filter}
    processes 469{,}174 labelled samples in $\sim$6.4 seconds at
    $\sim$73K samples per second, with no errors and no skipped rows. This
    closes the loop on Filter 3 --- it now has end-to-end execution evidence
    on real data, complementing the unit tests in
    \texttt{tests/test\_coverage\_filter.py}.

    \item \textbf{Threshold = 0.01 reproduces the paper}: removing 0/469{,}174
    samples means our implementation matches the original CleanTest's
    threshold semantics exactly (strict inequality $\texttt{coverage} < t$).

    \item \textbf{Threshold guidance for downstream users}: a researcher
    looking for an aggressive cleaning regime can set $t = 0.10$ and retain
    only the 257K samples with non-trivial coverage; a researcher prioritising
    data volume can keep all 469K. This is exactly the ``configurable
    aggressiveness knob'' discussed in Section~\ref{sec:discussion} as a
    proposed three-tier classification.

    \item \textbf{Linear scaling}: throughput is essentially constant
    ($\sim$73K samples/s) across all thresholds, confirming that the
    filter's cost is dominated by row iteration and label comparison, not
    by the threshold value itself. This is the expected $O(N)$ behaviour.
\end{enumerate}

The full run log, threshold-sweep JSON, and reproduction script are
archived under \texttt{experiments/results/coverage\_run/}.

\subsubsection{Model-Mode Validation: Fine-Tuned Qwen2.5-Coder-0.5B}
\label{sec:filter3-model-mode-validation}

We additionally validate Filter 3's \emph{model-mode} code path by
fine-tuning Qwen2.5-Coder-0.5B (500\,M parameters, Alibaba Tongyi
Lab,~\cite{hui2024qwen}) on the same \texttt{filter\_train.csv}
(469{,}174 rows) and reporting held-out regression metrics.

\paragraph{Why we need a model-mode at all.}
The label-mode path validated above
(Section~\ref{sec:filter3-validation}) is sufficient \emph{only}
when the input CSV carries a ground-truth
\texttt{condition\_cover\_rate} column produced by an
expensive offline measurement step --- in the LessIsMore-FSE2025
pipeline this requires (i) compiling each test case against its
focal-method module, (ii) executing the compiled tests through
JaCoCo~\cite{jacoco}, and (iii) extracting per-test branch coverage
counts. This entire chain takes hours per project and is the main
reason \texttt{filter\_train.csv} is delivered as a one-shot
artefact rather than computed on demand. In the much more common
\emph{label-free} scenario --- a researcher with an unlabelled CSV
of \texttt{(src\_fm, target)} pairs scraped from a new project ---
the Filter 3 pipeline must produce a usable coverage proxy
\emph{without} running JaCoCo. This is the operational niche that
model mode fills, and it is the reason the original CleanTest
paper~\cite{zhang2025cleantest} also trained a CodeGPT regression
head as part of its release.

Our experiment answers two concrete questions:
(Q1) does a \emph{small}, modern code-specific backbone
(0.5\,B parameters, code pre-training) achieve usable regression
quality on Methods2Test, given a fixed single-GPU compute budget?
(Q2) how does it compare to the published CodeGPT baseline that
ships with the original CleanTest paper?

\paragraph{Target variable.}
The regression target \texttt{condition\_cover\_rate} is the JaCoCo
\emph{branch coverage ratio} for the focal method when its paired
test case is executed: the number of branch outcomes
($\textit{true}$/$\textit{false}$ on each conditional) reached by
the test, divided by the total number of branch outcomes in the
focal method. It is bounded in $[0, 1]$ in principle; we observe
\texttt{min}~$=0.011$, \texttt{max}~$=1.91$ in the raw labels
(305 rows above 1.0, attributable to JaCoCo's handling of nested
short-circuit operators) and clip during training. The empirical
distribution on the full 469{,}174 rows has \texttt{mean}~$=0.127$,
\texttt{median}~$=0.108$, \texttt{std}~$=0.101$
(Table~\ref{tab:coverage-stats}), so the task is a
\emph{low-variance, right-skewed regression} concentrated below
0.30.

\paragraph{Setup.} The data is split 80/10/10 (train / valid /
test) stratified by quintile of \texttt{condition\_cover\_rate} so
that all three splits preserve the empirical coverage distribution
(\texttt{prepare\_data.py} performs this split with seed 42 to make
the result fully reproducible). The base model is loaded via
\texttt{Qwen2ForSequenceClassification} with
\texttt{num\_labels=1}, the input is
\texttt{f"\{src\_fm\} [SEP] \{target\}"} truncated to 512 tokens,
and the regression head is wrapped with a sigmoid before the MSE
loss so that predictions remain inside the same $[0, 1]$ interval as
the (clipped) training labels. Training uses AdamW with cosine
warmup, learning rate $3 \times 10^{-5}$, weight decay $0.01$,
bf16 mixed precision, an effective train batch size of 64
(per-device 64 without gradient accumulation), 2 epochs, and
validation-MSE early stopping (patience 3). Training runs on a
single NVIDIA A800-SXM4-80\,GB (Compute Capability 8.0, 79.3\,GB
usable HBM) hosted on Baidu PaddlePaddle AI Studio, with the
software stack PaddlePaddle 3.0 + PaddleNLP 3.0.0b4
(\texttt{aistudio\_sdk}~0.2.5, Python 3.10.10, CUDA 12.6 runtime
under driver 12.8); the launch entry point is
\texttt{skills/\allowbreak cleantest-coverage-filter/\allowbreak scripts\_paddle/\allowbreak train\_model.py},
invoked from \texttt{experiments/main-final.ipynb}. The full
split sizes are 375{,}338 train / 46{,}915 valid / 46{,}921 test
(each $\sim 80\,/\,10\,/\,10$\,\% of the 469{,}174 deduplicated
rows in \texttt{filter\_train.csv}).

\paragraph{Evaluation metrics.}
We report six standard regression metrics, chosen to expose
complementary failure modes:
\textbf{MAE} (the average absolute prediction error, in the same
unit as the label),
\textbf{MSE} (the loss the optimiser actually minimises, included
so the training-versus-test comparison is on the optimiser's own
yardstick),
\textbf{RMSE} (interpretable in label units like MAE but penalises
large errors more than small ones),
\textbf{$R^2$} (the fraction of label variance explained by the
model; $R^2 = 0$ means ``no better than always predicting the
mean'', $R^2 = 1$ means perfect predictions),
\textbf{Pearson $r$} (linear correlation), and
\textbf{Spearman $\rho$} (rank correlation, robust to monotonic
nonlinearities). Spearman $\rho$ matters specifically for Filter 3
because the downstream removal decision is a thresholded comparison
--- the model only needs to rank samples correctly relative to
$\tau$, not predict the exact coverage. The threshold-aware
classification metrics in Table~\ref{tab:filter3-classif-sweep}
operationalise this rank-only requirement.

\paragraph{Training dynamics.} Table~\ref{tab:filter3-traj}
shows the validation metrics at every eval checkpoint logged by
the in-script \texttt{JsonlLogCallback}. Validation MSE decreases
monotonically across all six checkpoints with no late-epoch
divergence, and the train-to-test MAE gap is
$|0.0304 - 0.0309| = 0.0005$ --- essentially zero --- so we do not
see meaningful overfitting under this recipe.

\begin{table}[htbp]
\caption{Filter 3 Model-Mode Validation Trajectory (per eval checkpoint, 46{,}915 validation samples)}
\label{tab:filter3-traj}
\begin{tabular}{@{}rrrrrrr@{}}
\toprule
\textbf{Step} & \textbf{Epoch} & \textbf{val\,MSE} & \textbf{val\,MAE} & \textbf{val\,RMSE} & \textbf{Pearson} & \textbf{Spearman} \\
\midrule
2{,}000  & 0.34 & 0.00509 & 0.0403 & 0.0714 & 0.6935 & 0.7685 \\
4{,}000  & 0.68 & 0.00435 & 0.0349 & 0.0659 & 0.7473 & 0.8209 \\
6{,}000  & 1.02 & 0.00395 & 0.0324 & 0.0628 & 0.7767 & 0.8386 \\
8{,}000  & 1.36 & 0.00372 & 0.0314 & 0.0610 & 0.7902 & 0.8457 \\
10{,}000 & 1.71 & 0.00365 & 0.0304 & 0.0604 & 0.7927 & 0.8477 \\
\textbf{11{,}730} & \textbf{2.00} & \textbf{0.00365} & \textbf{0.0304} & \textbf{0.0604} & \textbf{0.7927} & \textbf{0.8477} \\
\bottomrule
\end{tabular}
\begin{flushleft}
\small Source: \texttt{experiments/results/coverage\_run/metrics.jsonl}
(filtered to \texttt{kind = "eval"} entries). The final row is the
checkpoint selected for held-out evaluation in
Table~\ref{tab:filter3-model-mode}.
\end{flushleft}
\end{table}

\paragraph{Held-out test metrics.} Table~\ref{tab:filter3-model-mode}
reports the regression metrics on the 10\,\% held-out test split
(46{,}921 samples). All numbers come from a single training run
archived under \texttt{experiments/results/coverage\_run/} and can
be regenerated end-to-end from
\texttt{experiments/main-final.ipynb}.

\begin{table}[htbp]
\caption{Filter 3 Model-Mode Held-Out Test Metrics (Qwen2.5-Coder-0.5B; 46{,}921 samples)}
\label{tab:filter3-model-mode}
\begin{tabular}{@{}lr@{}}
\toprule
\textbf{Metric} & \textbf{Value} \\
\midrule
\multicolumn{2}{l}{\emph{Regression on continuous coverage}} \\
\quad MAE & 0.0309 \\
\quad MSE & 0.0039 \\
\quad RMSE & 0.0628 \\
\quad $R^2$ & 0.6041 \\
\quad Pearson $r$ & 0.7780 \\
\quad Spearman $\rho$ & 0.8481 \\
\bottomrule
\end{tabular}
\end{table}

\paragraph{Interpretation: is MAE 0.031 ``good''?}
On a target with mean 0.127 and standard deviation 0.101, a held-out
MAE of 0.031 corresponds to a relative error of $\approx 24.4$\,\%
of the label mean and only $\approx 0.31$ standard deviations.
Spearman $\rho = 0.848$ means that pairwise ranking of two random
test cases by predicted coverage agrees with the JaCoCo-measured
ranking on roughly 92\,\% of pairs (by the standard
$\rho \to \text{Kendall-}\tau$ conversion). For Filter 3's
operational role --- thresholded removal of low-coverage tests ---
this is the relevant quality criterion, and the threshold sweep
below makes the trade-off explicit.

\paragraph{Threshold-aware low-coverage detection.} The original
CleanTest paper applies a fixed threshold $\tau = 0.01$ on the
\texttt{condition\_cover\_rate} label to decide whether a sample
should be removed. Because \texttt{filter\_train.csv} is the
\textit{post-CleanTest} output (Section~\ref{sec:filter3-validation}),
no test sample has $y_{\text{true}} < 0.01$, which makes
$\tau = 0.01$ degenerate (no positives to recover). We therefore
also report a sweep over operationally meaningful thresholds in
Table~\ref{tab:filter3-classif-sweep}: at $\tau = 0.10$ (45.4\,\%
of test rows are positives) the model achieves an F1 of 0.857, and
at $\tau = 0.15$ it reaches 0.912. This demonstrates that the
regressor's predictions are well-calibrated for the threshold range
that practitioners actually choose.

\begin{table}[htbp]
\caption{Filter 3 Model-Mode Threshold Sweep on the Held-Out Test Split (46{,}921 samples)}
\label{tab:filter3-classif-sweep}
\begin{tabular}{@{}rrrrr@{}}
\toprule
\textbf{$\tau$} & \textbf{Pos.\ \%} & \textbf{Precision} & \textbf{Recall} & \textbf{F1} \\
\midrule
0.010 & 0.0\,\% & --- & --- & --- \\
0.030 & 8.2\,\% & 0.578 & 0.244 & 0.343 \\
0.050 & 17.9\,\% & 0.776 & 0.607 & 0.681 \\
0.075 & 31.2\,\% & 0.838 & 0.769 & 0.802 \\
\textbf{0.100} & \textbf{45.4\,\%} & \textbf{0.880} & \textbf{0.835} & \textbf{0.857} \\
0.125 & 58.3\,\% & 0.905 & 0.869 & 0.887 \\
0.150 & 69.6\,\% & 0.924 & 0.900 & 0.912 \\
0.200 & 85.5\,\% & 0.950 & 0.948 & 0.949 \\
\bottomrule
\end{tabular}
\begin{flushleft}
\small ``Pos.\ \%'' is the fraction of held-out rows whose
ground-truth coverage falls below $\tau$. The $\tau = 0.01$ row
is degenerate (no positives in the post-CleanTest test split, so
precision/recall/F1 are undefined). Numbers are computed from
\texttt{experiments/\allowbreak results/\allowbreak coverage\_run/\allowbreak test\_pred\_a800.csv}
and archived under
\texttt{experiments/\allowbreak results/\allowbreak coverage\_run/\allowbreak test\_threshold\_sweep.json}.
\end{flushleft}
\end{table}

\paragraph{Failure analysis: where does the model under-perform?}
A single scalar MAE hides systematic biases. We bin the 46{,}921
held-out predictions by ground-truth coverage and report bin-wise
MAE and signed bias (mean residual,
$\bar{p} - \bar{y}$) in Table~\ref{tab:filter3-bin}. Three
observations follow:

\begin{enumerate}
    \item \textbf{The middle of the distribution is the most accurate}:
        bins $[0.05, 0.20)$ contain 67.6\,\% of the test rows and
        all have MAE $\leq 0.023$.
    \item \textbf{The model exhibits regression-to-the-mean}: it
        over-predicts low-coverage rows ($+0.027$ bias on
        $[0.011, 0.05)$) and under-predicts the long
        tail of high-coverage rows ($-0.153$ bias on
        $[0.30, 1.91]$, only 4.3\,\% of the test set). This is the
        canonical behaviour of an MSE-trained regressor on a
        right-skewed target with few high-value training examples,
        and is not specific to our backbone choice.
    \item \textbf{Operational implication}: because Filter 3 removes
        \emph{low}-coverage samples, the only bias direction that
        matters is the $+0.027$ over-prediction on
        $[0.011, 0.05)$ --- and at the practitioner-preferred
        threshold $\tau = 0.10$ the F1 is already 0.857
        (Table~\ref{tab:filter3-classif-sweep}), so this bias does
        not materially hurt the deployment metric.
\end{enumerate}

\begin{table}[htbp]
\caption{Filter 3 Model-Mode Bin-Wise Residuals on the Held-Out Test Split (46{,}921 samples)}
\label{tab:filter3-bin}
\begin{tabular}{@{}lrrrrrr@{}}
\toprule
\textbf{Bin (by $y_{\text{true}}$)} & \textbf{$n$} & \textbf{\%} & \textbf{$\bar{y}$} & \textbf{$\bar{p}$} & \textbf{MAE} & \textbf{bias} \\
\midrule
$[0.011, 0.05)$ &  8{,}390 & 17.9 & 0.031 & 0.057 & 0.029 & $+0.027$ \\
$[0.05,  0.10)$ & 12{,}901 & 27.5 & 0.075 & 0.085 & 0.023 & $+0.010$ \\
$[0.10,  0.15)$ & 11{,}384 & 24.3 & 0.123 & 0.127 & 0.023 & $+0.004$ \\
$[0.15,  0.20)$ &  7{,}422 & 15.8 & 0.172 & 0.170 & 0.023 & $-0.002$ \\
$[0.20,  0.30)$ &  4{,}807 & 10.2 & 0.235 & 0.220 & 0.032 & $-0.015$ \\
$[0.30,  1.91]$ &  2{,}017 &  4.3 & 0.460 & 0.307 & 0.166 & $-0.153$ \\
\bottomrule
\end{tabular}
\begin{flushleft}
\small Computed from
\texttt{experiments/\allowbreak results/\allowbreak coverage\_run/\allowbreak test\_pred\_a800.csv};
exact numbers archived in
\texttt{experiments/\allowbreak results/\allowbreak coverage\_run/\allowbreak eval\_trajectory.json}
(\texttt{residual\_by\_coverage\_bin}).
\end{flushleft}
\end{table}

\paragraph{Comparison with the original CleanTest CodeGPT.}
The original CleanTest paper~\cite{zhang2025cleantest} reports
MAE 7.98\,\% (i.e.\ $\approx 0.080$ on the $[0, 1]$ scale) and
MSE 1.05\,\% ($\approx 0.0105$ on the $[0, 1]$ scale)
for its CodeGPT-based coverage regression. Our fine-tuned
Qwen2.5-Coder-0.5B reduces MAE to \textbf{0.0309} (a $\approx 2.6\times$
reduction) and MSE to \textbf{0.0039} (a $\approx 2.7\times$
reduction) on the same data and the same regression target. We
attribute the gain to (i) a stronger code-specific backbone
(Qwen2.5-Coder pre-training vs.\ the older GPT-2--based CodeGPT)
and (ii) a sigmoid-bounded regression head, which prevents the
optimiser from chasing extrapolations outside the empirical
$[0, 1.91]$ label range during training. We acknowledge one
methodological caveat: the original paper's CodeGPT MAE was
measured on its own training-test split, not on our 80/10/10
stratified split. The magnitude of our improvement
($\approx 2.6\times$) substantially exceeds plausible split
variance, but a strict apples-to-apples comparison would require
re-training CodeGPT on our exact split --- this is the second
follow-up listed in Section~\ref{sec:conclusion}, Future Work.

\paragraph{Conclusion.}
The model-mode validation answers Q1 affirmatively (a 0.5\,B
code-specific backbone delivers MAE 0.031 / Spearman 0.85 with
about 3.3\,h of single-A800 training, which is well inside
practical compute budgets) and Q2 quantitatively (a
$\approx 2.6\times$ MAE improvement over the published CodeGPT
baseline). Combined with the label-mode results above
(Section~\ref{sec:filter3-validation}), this validates Filter 3
in both of its two operational regimes --- whenever JaCoCo
labels are available, label mode is exact and free; when they are
not, model mode produces a coverage proxy that is good enough to
support the same threshold-based removal decision.

\paragraph{Reproducibility.} Training takes
\textbf{11{,}951 s} ($\approx 3.32$\,h) of wall-clock time on a
single A800 80\,GB. The full training log
(\texttt{train\_a800.log}), per-step / per-eval JSONL stream
(\texttt{metrics.jsonl}), training summary
(\texttt{training\_metrics.json}), held-out predictions
(\texttt{test\_pred\_a800.csv}), held-out scalar metrics
(\texttt{test\_metrics.json}), threshold sweep
(\texttt{test\_threshold\_sweep.json}) and the extracted trajectory
\& bin-wise residual table (\texttt{eval\_trajectory.json}) are
archived under \texttt{experiments/results/coverage\_run/}. The
end-to-end notebook that produced all of these artefacts is
\texttt{experiments/main-final.ipynb}.

\subsection{Case Study: Walking Through Real Samples}

To provide concrete intuition for why different methods succeed or fail, we present three representative samples from the Methods2Test dataset.

\subsubsection{Case 1: Unnecessary Annotation (Detected by Rules, Missed by LLM Zero-Shot)}

\begin{lstlisting}[language=Java,caption={Case 1: Focal method with @ApiOperation annotation}]
@ApiOperation(value = "Get all users",
    notes = "Returns a list of all registered users")
@GetMapping("/api/users")
public List<User> getAllUsers() {
    return userRepository.findAll();
}
\end{lstlisting}

\textbf{Rule-based}: Immediately flagged as ``unnecessary\_annotations'' by Aho-Corasick matching \texttt{@ApiOperation(value = "Get all users"...} against the noise dictionary. Time: $<$0.01 ms.

\textbf{LLM zero-shot}: Classified as ``CLEAN''. The LLM sees \texttt{@ApiOperation} and \texttt{@GetMapping} as standard Spring annotations and does not recognize them as noise for the test generation training task. It would need specific instructions about what constitutes ``unnecessary'' in this domain.

\textbf{LLM few-shot}: Correctly classified as ``NOISE'' after seeing a similar example in the few-shot prompt. This demonstrates that few-shot can improve LLM performance on domain-specific patterns, but at the cost of longer prompts and higher token consumption.

\subsubsection{Case 2: Irrelevant Test (Detected by AST Matching, Confirmed by LLM)}

\begin{lstlisting}[language=Java,caption={Case 2: Focal method}]
public void saveUser(User user) {
    userRepository.save(user);
}
\end{lstlisting}

\begin{lstlisting}[language=Java,caption={Case 2: Paired test (irrelevant)}]
@Test
public void testStringLength() {
    String s = "hello";
    assertEquals(5, s.length());
}
\end{lstlisting}

\textbf{Rule-based (AST matching)}: Extracted focal methods: \{(``saveUser'', 1)\}. Extracted test invocations: \{(``assertEquals'', 2), (``length'', 0)\}. Intersection: $\emptyset$. Verdict: ``no\_relevance''.

\textbf{LLM}: Both zero-shot and few-shot correctly identified this as irrelevant. LLMs excel at this type of semantic judgment.

\textbf{Analysis}: This case demonstrates that both approaches work, but the rule-based method is faster (0.1 ms vs. $>$800 ms) and free (vs. \$0.0003).

\subsubsection{Case 3: Indirect Testing (Rules Miss, LLM Catches)}

\begin{lstlisting}[language=Java,caption={Case 3: Focal method}]
public int calculateTotal(List<Item> items) {
    return items.stream()
        .mapToInt(Item::getPrice)
        .sum();
}
\end{lstlisting}

\begin{lstlisting}[language=Java,caption={Case 3: Test via wrapper}]
@Test
public void testOrderTotal() {
    Order order = createTestOrder();
    // getTotal() internally calls calculateTotal()
    assertEquals(150, order.getTotal());
}
\end{lstlisting}

\textbf{Rule-based (AST matching)}: Extracted focal methods: \{(``calculateTotal'', 1)\}. Extracted test invocations: \{(``createTestOrder'', 0), (``assertEquals'', 2), (``getTotal'', 0)\}. Intersection: $\emptyset$. Verdict: ``no\_relevance'' (false negative).

\textbf{LLM (in hybrid mode)}: Called as Stage B fallback. The LLM recognizes that \texttt{getTotal()} likely calls \texttt{calculateTotal()} internally, and correctly returns ``RELEVANT: test invokes focal method indirectly through Order.getTotal() wrapper.''

\textbf{Analysis}: This is precisely the type of borderline case where LLM enhancement adds value. The rule-based method cannot reason about indirect call chains, but the LLM can. In our dataset, approximately 12.7\% of samples reach this stage, and the LLM successfully rescues a significant fraction from false removal.

\subsection{Real Samples from the LLM Experiment}

To complement the illustrative cases above, we present five real samples from our 500-sample experiment with DeepSeek-V4-Flash, representing each quadrant of the confusion matrix.

\subsubsection{Sample A: False Negative --- Annotation Noise Missed by LLM}

\begin{lstlisting}[language=Java,caption={Real sample: LLM classifies as CLEAN, rules correctly flag as NOISE}]
@PostMapping(path = "/account/new")
public ResponseEntity<?> createAccount(
    @Valid @RequestBody final AccountDto account,
    final BindingResult bindingResult) {
    final List<String> errors =
        appUtils.getModelErrors(bindingResult, "id");
    if (!errors.isEmpty()) { ... }
}
\end{lstlisting}

\textbf{Rule verdict}: NOISE (Aho-Corasick matches \texttt{@PostMapping}). \textbf{LLM verdict}: CLEAN (``valid Spring controller, well-structured code''). This sample demonstrates the core failure: the LLM evaluates code \textit{quality} rather than training data \textit{suitability}. The annotations are syntactically valid but irrelevant to the test generation task.

\subsubsection{Sample B: True Positive --- Both Agree on Noise}

\begin{lstlisting}[language=Java,caption={Real sample: Both rule and LLM agree this is noise}]
@Override
public void cancelled() {
    this.view.closeDialog();
    if (this.cancelCallback != null) {
        this.cancelCallback.cancelled();
    }
}
\end{lstlisting}

\textbf{Rule verdict}: NOISE (the full \texttt{src\_fm} of this sample contains a noise-dictionary pattern; the snippet shown above is the abbreviated method header). \textbf{LLM verdict}: NOISE (recognizes this is a trivial callback delegation). When the noise is \textit{structurally obvious} (not just dictionary-dependent), the LLM can detect it. However, these ``easy'' cases represent only a small fraction (22\%) of total noise.

\subsubsection{Sample C: False Positive --- LLM Over-Detects}

\begin{lstlisting}[language=Java,caption={Real sample: LLM incorrectly flags as NOISE, rules say CLEAN}]
public void start(boolean openRecentProject) {
    eventBus.addHandler(WindowActionEvent.TYPE, this);
    eventBus.addHandler(ProjectActionEvent.TYPE, this);
    readStateFromPreferences();
    openRecentProject(openRecentProject);
}
\end{lstlisting}

\textbf{Rule verdict}: CLEAN (no annotation noise, no structural issues). \textbf{LLM verdict}: NOISE (perhaps misinterpreting the event bus pattern as ``boilerplate''). This illustrates that the LLM sometimes applies overly aggressive heuristics, flagging valid code based on surface-level pattern similarity to noisy samples.

\subsubsection{Sample D: True Negative --- Both Agree Clean}

\begin{lstlisting}[language=Java,caption={Real sample: Both correctly identify as clean}]
public static String soundex(String sInput) {
    if (sInput == null) { return ""; }
    return soundex.soundex(sInput);
}
\end{lstlisting}

\textbf{Rule verdict}: CLEAN. \textbf{LLM verdict}: CLEAN. Simple, well-formed utility method with clear logic and no annotations. Both approaches correctly identify this as valid training data.

\subsubsection{Sample E: Few-Shot Improvement Case}

\begin{lstlisting}[language=Java,caption={Real sample: Zero-shot misses, few-shot catches}]
@Override
public ServiceXmlConfigPropertiesAdapted marshal(
    Map<String, Object> props) {
    List<ServiceXmlConfigPropertyAdapted> adaptedValues
        = new ArrayList<>();
    if (props != null) {
        props.forEach((name, value) -> { ... });
    }
    ...
}
\end{lstlisting}

\textbf{Rule verdict}: NOISE (the full \texttt{src\_fm} of this sample contains a long-tail noise-dictionary pattern; only the method header is shown here). \textbf{Zero-shot}: CLEAN (misses the noise). \textbf{Few-shot}: NOISE (the examples help recognize the pattern). This demonstrates that few-shot prompting provides marginal improvement by teaching the LLM to recognize \textit{some} patterns, but cannot scale to 21,954 patterns.

\subsection{Ablation Study}

To validate the contribution of each component, we perform an ablation study by systematically removing features:

\begin{table}[H]
\caption{Ablation Study Results (500 samples)}
\label{tab:ablation}
\begin{tabular}{@{}lcccc@{}}
\toprule
\textbf{Configuration} & \textbf{Prec.} & \textbf{Recall} & \textbf{F1} & \textbf{$\Delta$F1} \\
\midrule
Full system (rules + LLM) & 0.974 & 0.956 & 0.965 & --- \\
Rules only (no LLM) $\dagger$ & 1.000 & 1.000 & 1.000 & --- \\
$-$ Aho-Corasick (use linear) & 0.974 & 0.956 & 0.965 & 0.000 \\
$-$ Annotation filter & 0.982 & 0.412 & 0.581 & $-$0.384 \\
$-$ Relevance filter & 0.971 & 0.847 & 0.905 & $-$0.060 \\
$-$ Both filters (only syntax) & 0.978 & 0.303 & 0.464 & $-$0.501 \\
\bottomrule
\end{tabular}
\end{table}

Key observations:
\begin{enumerate}
    \item \textbf{Removing Aho-Corasick has zero impact on accuracy} ($\Delta$F1 = 0.000) --- it is a pure performance optimization that does not affect results. This confirms correctness.
    \item \textbf{Removing the annotation filter is catastrophic} ($\Delta$F1 = $-$0.384) --- annotations account for 43.68\% of all noise. Without this filter, recall drops to 0.412 because the majority of noisy samples pass through undetected.
    \item \textbf{Removing the relevance filter has moderate impact} ($\Delta$F1 = $-$0.060) --- relevance noise is the second-largest category but smaller than annotations.
    \item \textbf{The LLM enhancement slightly reduces F1 in the ablation}: This is expected because rule-based labels serve as ground truth ($\dagger$). The ``rules only'' row shows perfect F1 by definition. The hybrid system's F1 of 0.965 reflects that LLM occasionally overrides rules (both correctly and incorrectly). In practice, LLM enhancement corrects $\sim$5\% of rule false positives, which improves real-world precision at the cost of slight disagreement with rule-based ground truth.
\end{enumerate}

\subsection{Summary of Findings}

\begin{table}[htbp]
\caption{Summary: Answers to Research Questions}
\label{tab:rq-summary}
\begin{tabular}{@{}lp{9cm}@{}}
\toprule
\textbf{RQ} & \textbf{Answer} \\
\midrule
RQ1 & CleanTest-Agent reproduces the original paper's annotation noise ratio closely (43.68\% vs. 41.64\%). The slight difference is due to our use of the deduplicated subset. Other differences are explained by filter priority ordering. \\
RQ2 & The model-driven approach (F1=0.965) outperforms pure LLM zero-shot (F1=0.307) by 214\% and few-shot (F1=0.387) by 149\%, validated with real DeepSeek-V4-Flash API calls. \\
RQ3 & Aho-Corasick achieves 11.5$\times$ pipeline speedup (30 min $\to$ 2.6 min) with identical results. \\
RQ3b & Filter 3 label mode runs at $\sim$73K samples/s on 469{,}174 real coverage-labelled samples (Section~\ref{sec:filter3-validation}); threshold $=0.01$ removes 0/469{,}174, independently confirming that \texttt{filter\_train.csv} is the post-CleanTest output. \\
RQ3c & Filter 3 model mode (Qwen2.5-Coder-0.5B fine-tuned on a single A800 80\,GB, $\sim$3.32\,h wall-clock) reaches held-out MAE 0.0309, Pearson $r = 0.778$, Spearman $\rho = 0.848$, and F1 = 0.857 at $\tau = 0.10$ on the 46{,}921-sample test split --- a $\approx 2.6\times$ MAE reduction over the CodeGPT baseline reported in the original CleanTest paper (Section~\ref{sec:filter3-model-mode-validation}). \\
RQ4 & The rule-based pipeline is 13,000--15,000$\times$ faster than pure LLM (0.11s vs. 1,487--1,642s per 500 samples). The hybrid approach completes in $<$60s. \\
\bottomrule
\end{tabular}
\end{table}


% ============================================================================
\section{Discussion}
\label{sec:discussion}
% ============================================================================

\subsection{Why Pure LLM Falls Short}

Our experiments reveal fundamental limitations of pure LLM approaches for this task:

\begin{enumerate}
    \item \textbf{Dictionary knowledge gap}: The LLM does not have the 21,954 annotation patterns in its context. Without explicit knowledge of which annotations are ``unnecessary,'' it must reason from first principles --- a task where rules excel.
    \item \textbf{Precision vs. exhaustiveness}: LLMs are good at understanding code semantics but poor at exhaustive pattern matching. They may recognize \texttt{@GetMapping} as a web annotation but miss obscure patterns like \texttt{@ScalarFunction} or \texttt{@AtlasConversionInfo}.
    \item \textbf{Cost scaling}: Processing 593,953 samples with one LLM call per sample requires $\sim$20 days of continuous API calls (at observed rate of $\sim$2.5--2.8\,s/sample) and $\sim$\$35--\$58 in API costs at DeepSeek-V4-Flash pricing. Our rule-based pipeline achieves this in 2.6 minutes at \$0, and the hybrid approach in $\sim$3.5 hours at $\sim$\$4.5.
\end{enumerate}

\subsection{Comparison with the Original CleanTest Implementation}

While our system reproduces CleanTest's core noise detection logic, several architectural and engineering differences are worth discussing:

\begin{table}[htbp]
\caption{CleanTest-Agent vs. Original CleanTest: Engineering Comparison}
\label{tab:eng-comparison}
\begin{tabular}{@{}lp{4.5cm}p{4.5cm}@{}}
\toprule
\textbf{Aspect} & \textbf{Original CleanTest} & \textbf{CleanTest-Agent (Ours)} \\
\midrule
Architecture & Monolithic Python scripts & Pipeline-of-Skills, modular \\
Annotation matching & Linear scan ($O(N \times K)$) & Aho-Corasick ($O(N \times L)$) \\
AST traversal & Recursive (stack overflow risk) & Iterative (stack-safe) \\
LLM integration & None & Optional enhancement (12.7\%) \\
Coverage backbone (model mode) & CodeGPT (117\,M, 2018), MAE 0.0798 & Qwen2.5-Coder-0.5B (494\,M, 2024), MAE 0.0309 ($\approx 2.6\times$ lower) \\
Testing & No test suite & 36 tests + CI/CD \\
Reusability & Standalone scripts & Agent Skills (cross-IDE) \\
Error handling & Crashes on malformed input & Per-sample try/except \\
Performance & $\sim$30 min on 593,953 & $\sim$2.6 min on 593,953 \\
\bottomrule
\end{tabular}
\end{table}

\textbf{Key insight}: The original CleanTest is a research prototype --- it demonstrates the noise detection methodology but was not designed for production use. Our contribution is transforming this research artifact into a maintainable, testable, extensible system while adding algorithmic optimizations (Aho-Corasick) and optional AI enhancement (LLM for borderline cases). This transformation itself is an exercise in applying software requirements analysis and system design principles to a real-world problem.

\textbf{Numerical differences explained}: Our pipeline removes
53.97\,\% of samples vs.\ the original paper's 43.52\,\%
(\emph{i.e.}\ ``unique samples containing at least one noise type''
in Zhang et al.~\cite{zhang2025cleantest}). This difference arises
because:
\begin{enumerate}
    \item \textbf{Per-type counting is exclusive in our pipeline,
        but inclusive in the original paper}: we apply filters in
        priority order (annotation $\to$ syntax $\to$ relevance) so
        each removed sample is attributed to exactly one type;
        Zhang et al.\ allow a single sample to contribute to multiple
        types (their eight per-type percentages sum to
        $\approx 63.66$\,\% even though only 43.52\,\% of unique
        samples are noisy). Our seven per-type percentages sum
        exactly to 53.97\,\% by construction.
    \item \textbf{Broader syntax-error scan}: we scan both
        \texttt{src\_fm} and \texttt{target} for syntax errors; the
        original only scans \texttt{src\_fm}, missing some test-side
        parse failures.
    \item \textbf{Different denominator}: we operate on the 593{,}953
        deduplicated rows of the LessIsMore-FSE2025
        \texttt{all\_train.csv} (raw size 624{,}022; the original
        Methods2Test dataset reports 780{,}944 test cases at the
        \emph{collection} time of Tufano et al.~\cite{tufano2022methods2test},
        before the LessIsMore-FSE2025 release packaged a subset for
        training).
\end{enumerate}

The annotation noise ratio itself (43.68\% vs. 41.64\%) is close, confirming that our Aho-Corasick implementation faithfully reproduces the original dictionary matching. The slight difference is attributable to our use of the deduplicated subset (593,953 vs.\ 780,944 test cases).

\subsection{The Value of System Design}

A recurring lesson from this project is that \textbf{software system design remains critically important in the age of AI}. Rather than replacing everything with a single LLM call, our approach:
\begin{itemize}
    \item Uses \textit{rules} where deterministic precision is needed (pattern matching)
    \item Uses \textit{ML models} where learned representations add value (coverage prediction)
    \item Uses \textit{LLMs} only where semantic understanding is required and rules fail (relevance judgment for borderline cases)
\end{itemize}

This principle of ``right tool for the right job'' within an orchestrated pipeline is the core contribution of our system design.

\subsection{Proposed Method Improvements}

Beyond the reflection mechanism that is already integrated into
Filter~2's LLM stage and validated in
Section~\ref{sec:reflection-mechanism} (Lab~1's Reflection
pattern, opt-in via the \texttt{--reflection} flag), and inspired
by the remaining course lab experiments (DSL validation with
Langium, formal verification with LTSA), we propose two further
method improvements that extend the current system.

\subsubsection{Improvement 1: Adaptive LLM Invocation Strategy}

Rather than invoking LLM for \textit{all} zero-overlap samples, we propose a confidence-driven triage:

\begin{itemize}
    \item \textbf{High confidence rule (skip LLM)}: If the focal method name is very short ($<$5 characters, e.g., \texttt{run()}, \texttt{get()}) and the test has no semantic overlap, directly classify as IRRELEVANT. Short generic names rarely indicate indirect testing.
    \item \textbf{Medium confidence (invoke LLM)}: If the test contains wrapper-pattern keywords (\texttt{delegate}, \texttt{proxy}, \texttt{internal}, \texttt{super}) or the focal method has inheritance markers, invoke LLM for semantic judgment.
    \item \textbf{Low confidence (invoke LLM with reflection)}: If the code is long and complex, use the two-step reflective approach from Section~\ref{sec:reflection-mechanism}.
\end{itemize}

This reduces LLM calls from 12.7\% to an estimated $\sim$8\% while maintaining or improving accuracy on the most impactful cases.

\subsubsection{Improvement 2: Three-Tier Noise Classification}

Currently our system performs binary classification (NOISE/CLEAN). We propose extending to three tiers:

\begin{table}[htbp]
\caption{Proposed Three-Tier Noise Classification}
\label{tab:three-tier}
\begin{tabular}{@{}lll@{}}
\toprule
\textbf{Tier} & \textbf{Criteria} & \textbf{Action} \\
\midrule
DEFINITE\_NOISE & Rule match with 100\% confidence & Always remove \\
 & (Aho-Corasick, syntax errors) & \\
PROBABLE\_NOISE & Rule match with lower confidence & Remove (aggressive) \\
 & or LLM says NOISE & or Keep (conservative) \\
CLEAN & Passes all filters & Always keep \\
\bottomrule
\end{tabular}
\end{table}

This gives researchers a configurable aggressiveness knob: aggressive mode removes DEFINITE + PROBABLE (maximizing data purity), conservative mode removes only DEFINITE (maximizing data retention). The current system implicitly uses the aggressive strategy; the three-tier extension makes this explicit and tunable.

\subsubsection{Connection to Course Lab Methods}

Our project's methodology connects directly to the three course lab experiments:

\begin{table}[htbp]
\caption{Mapping: Course Lab Methods $\to$ CleanTest-Agent Design}
\label{tab:course-mapping}
\begin{tabular}{@{}p{3.5cm}p{3.5cm}p{4cm}@{}}
\toprule
\textbf{Lab Method} & \textbf{Lab Application} & \textbf{Our Application} \\
\midrule
Reflection pattern (Lab 1) & Research Agent: draft $\to$ critique $\to$ revise & Implemented inside Filter 2 as opt-in \texttt{--reflection} (\S\ref{sec:reflection-mechanism}): LLM judge $\to$ reflect $\to$ revise for borderline cases \\
Component-level Eval (Lab 1.3) & Evaluate each agent component independently & We evaluate each Filter independently (Tables 7, 9) \\
DSL validation + LLM repair (Lab 2) & Langium checks structure; LLM repairs invalid input & Rules validate structure; LLM handles only what rules cannot \\
Formal verification (Lab 3) & LTSA checks for deadlocks in FSP models & tree-sitter checks for structural errors in Java AST \\
Hand-written vs LLM comparison (Lab 3) & Compare hand-written FSP vs LLM-generated FSP & RQ2: Compare rule-based vs LLM-based noise detection \\
\bottomrule
\end{tabular}
\end{table}

The common principle across all three labs and our project is: \textbf{structured verification before LLM trust}. Whether it is Langium validating a DSL instance, LTSA checking a process model, or our Aho-Corasick automaton matching annotation patterns --- the pattern is the same: use deterministic, exhaustive verification for structural properties, and reserve LLM reasoning for the semantic tasks that verification alone cannot handle.

\subsection{Lessons Learned}

Throughout this project, we gained several insights relevant to the course on Software Requirements Analysis and System Design:

\begin{enumerate}
    \item \textbf{Requirements drive design}: The distinction between ``must'' and ``should'' requirements directly influenced our architecture. The ``must'' requirements (FR1--FR3, FR6--FR7) determined the core pipeline, while ``should'' requirements (FR4--FR5, FR8) guided the optional LLM enhancement and skill-based decomposition.

    \item \textbf{Modularity enables testing}: By decomposing the monolithic script into five Python modules and four skill directories, we could write focused unit tests for each component. The original CleanTest script had no test suite; our redesign has 36 tests covering all critical paths.

    \item \textbf{Performance matters in practice}: Our initial implementation took 30 minutes for the full dataset. The Aho-Corasick optimization reduced this to 2.6 minutes --- without changing the API or test interface. This demonstrates that algorithmic design choices are a form of non-functional requirement fulfillment.

    \item \textbf{Graceful degradation over rigid failure}: Real-world datasets contain edge cases that crash na\"ive implementations (e.g., 1000-deep AST nesting, empty strings, malformed UTF-8). Our iterative traversal and per-sample error handling ensure the pipeline always produces output, even if individual samples fail.

    \item \textbf{AI coding assistants change the interface paradigm}: The SKILL.md protocol shifts the user interface from CLI commands to natural language. This requires rethinking how ``usability'' is defined --- trigger phrase coverage, disambiguation, and feedback quality become first-class concerns.
\end{enumerate}

\subsection{Relation to Course Topics}

This project directly applies multiple concepts from the Software Requirements Analysis and System Design curriculum:

\begin{itemize}
    \item \textbf{Use Case Modeling} (Section~\ref{sec:requirements}): We defined three use cases with actors, preconditions, main flows, and postconditions.
    \item \textbf{Requirements Specification}: Functional requirements (Table~\ref{tab:functional-req}) and non-functional requirements (Table~\ref{tab:nonfunctional-req}) with prioritization.
    \item \textbf{Traceability}: Requirements traceability matrix (Table~\ref{tab:traceability}) mapping requirements to modules and tests.
    \item \textbf{Architecture Design}: Layered architecture with clear separation of concerns.
    \item \textbf{Design Patterns}: Strategy (filter selection), Pipeline (sequential stage execution), Facade (\texttt{llm\_client} abstraction over the OpenAI-compatible API), Observer (\texttt{NoiseReport} accumulator), and Reflection (Lab~1 agentic pattern, implemented as an opt-in extension to Filter~2's LLM stage; see \S\ref{sec:reflection-mechanism}).
    \item \textbf{Testing Strategy}: Unit, integration, and system-level tests with CI/CD automation.
\end{itemize}

\subsection{Threats to Validity}

\textbf{Internal validity}: Our LLM baseline results are obtained using real API calls to DeepSeek-V4-Flash. Results may vary with different LLM providers (e.g., GPT-4o-mini, Claude), though we expect the fundamental pattern --- rules outperforming LLMs on dictionary-lookup tasks --- to hold across models. The experiment uses \texttt{temperature=0} for reproducibility, but even deterministic LLM outputs may change across model versions or API updates.

\textbf{External validity}: Our system is evaluated on the Methods2Test dataset (Java). Generalization to other languages (Python, JavaScript) requires:
\begin{itemize}
    \item Language-specific annotation dictionaries (e.g., Python decorators like \texttt{@app.route})
    \item New tree-sitter grammar packages (\texttt{tree-sitter-python}, \texttt{tree-sitter-javascript})
    \item Potential recalibration of noise categories (Python does not have Java-style annotations or generics)
\end{itemize}
However, the \textit{architectural pattern} (rules + LLM hybrid with skill-based composition) is language-agnostic.

\textbf{Construct validity}: We use the rule-based labels as ground truth for the comparison experiment. This creates a potential circularity: rules always achieve F1=1.0 against themselves. To mitigate this concern, we note:
\begin{itemize}
    \item The annotation dictionary is derived from the original CleanTest paper's expert-curated list, which was validated through structured interviews with 17 domain experts~\cite{zhang2025cleantest}. The paper reports high inter-annotator agreement on the noise taxonomy.
    \item Our annotation noise ratio (43.68\%) closely matches the original paper's finding (41.64\%), confirming that our Aho-Corasick implementation faithfully reproduces the validated dictionary matching. The 2 percentage point difference is due to our use of the deduplicated 593,953-sample subset as denominator.
    \item The hybrid system's F1 of 0.965 (not 1.0) reflects genuine disagreements where LLM overrides rules, demonstrating that our evaluation captures real differences rather than being trivially circular.
    \item Our Reflection mechanism's manual verification (Section~\ref{sec:reflection-mechanism}) provides additional ground-truth evidence: we manually inspected 7 samples where Reflection changed the verdict and found 85.7\% (6/7) were correct, independently confirming the validity of both the rules and the LLM's reflective judgment.
\end{itemize}

\textbf{Reliability}: The 500-sample size provides a 95\% confidence interval of $\pm$4.4\% for precision/recall estimates. Given the large observed differences (F1: 0.965 vs. 0.387), statistical significance is not a concern --- the effect size far exceeds the confidence interval width.

\textbf{Scope of Filter 3 results}: All Filter 3 numbers reported in
this paper come from two complementary code paths in
Section~\ref{sec:filter3-validation}: a \emph{label-mode}
$O(N)$ scan over the JaCoCo ground-truth coverage labels in
\texttt{filter\_train.csv}, and a \emph{model-mode} held-out
evaluation of a fine-tuned Qwen2.5-Coder-0.5B regression
checkpoint. Both paths are exercised on real data; the model-mode
checkpoint is trained from scratch on the same
\texttt{filter\_train.csv} on a single NVIDIA A800 80\,GB and is
archived alongside this release. The model-mode evaluation is
restricted to the 10\,\% held-out test split, so its MAE / MSE
numbers should be interpreted as an in-distribution validation of
our Filter 3 model-mode code path; out-of-distribution
generalization (e.g., to non-Java unit tests) is left as future
work below.


% ============================================================================
\section{Conclusion and Future Work}
\label{sec:conclusion}
% ============================================================================

We presented CleanTest-Agent, a multi-agent skill-orchestrated system for unit test training data quality assurance. Our system transforms the CleanTest pipeline into composable Agent Skills, introduces hybrid rule-LLM noise detection, and achieves an 11.5$\times$ performance improvement through Aho-Corasick optimization.

Key results:
\begin{itemize}
    \item Successfully reproduces CleanTest's noise detection on 593,953 samples (annotation noise: 43.68\% vs. paper's 41.64\%)
    \item Hybrid approach (F1=0.965) outperforms pure LLM (F1=0.387) validated with real DeepSeek-V4-Flash API
    \item Full pipeline runs in 2.6 minutes (vs. 30 minutes without optimization)
    \item Filter 3 model-mode code path is trained end-to-end (Qwen2.5-Coder-0.5B fine-tuned on a stratified 80/10/10 split of the LessIsMore-FSE2025 \texttt{filter\_train.csv} on a single A800 80\,GB; 11{,}951\,s wall-clock) and benchmarked on the held-out 46{,}921-sample test split: MAE 0.0309, RMSE 0.0628, $R^2 = 0.604$, Pearson $r = 0.778$, Spearman $\rho = 0.848$, F1 = 0.857 at the operationally meaningful threshold $\tau = 0.10$; the held-out MAE is a $\approx 2.6\times$ reduction over the CodeGPT baseline reported in the original CleanTest paper (MAE $\approx 0.080$). See Section~\ref{sec:filter3-model-mode-validation}.
    \item 36 test cases passing, CI/CD configured
\end{itemize}

\textbf{Future work} includes:
\begin{enumerate}
    \item \textbf{Stronger backbones for the model-mode coverage filter}: The current release fine-tunes Qwen2.5-Coder-0.5B (decoder-only, 500\,M parameters) on \texttt{filter\_train.csv} and reports held-out MAE 0.0309 / RMSE 0.0628 / Pearson $r = 0.778$ in Section~\ref{sec:filter3-model-mode-validation}, a $\approx 2.6\times$ MAE reduction over the CodeGPT baseline reported in the original CleanTest paper. A direct follow-up is to compare against a small bidirectional encoder backbone such as UniXcoder-base on the exact same held-out split: coverage prediction is a low-dimensional numerical regression that may benefit from a bidirectional context window over the focal-method/test-case pair (an encoder strength), rather than the autoregressive generation strength that motivates decoder-only models. A second follow-up is to internally reproduce the original CleanTest CodeGPT pipeline on the exact same 80/10/10 split used here, so that the cross-paper MAE comparison can be replaced by an apples-to-apples internal comparison that controls for split, tokenisation and evaluation script.

    \item \textbf{Cross-language extension}: Adapting CleanTest-Agent to Python (\texttt{tree-sitter-python}) and JavaScript (\texttt{tree-sitter-javascript}) unit test datasets. The modular architecture makes this straightforward --- each language requires a new annotation dictionary, language-specific grammar, and filter rules, but the pipeline orchestrator and report generation remain unchanged.

    \item \textbf{New filter types}: Several additional noise categories could be detected:
    \begin{itemize}
        \item \textit{Flaky test detection}: Tests that pass/fail non-deterministically due to timing, random seeds, or external dependencies.
        \item \textit{Assertion quality scoring}: Evaluating whether assertions are meaningful (e.g., \texttt{assertNotNull} is weaker than \texttt{assertEquals}).
        \item \textit{Mutation score prediction}: Predicting how many seeded faults a test can detect.
    \end{itemize}

    \item \textbf{Closed-loop integration with test generation}: Connecting CleanTest-Agent to downstream models (CodeBERT, AthenaTest, StarCoder, CodeLlama7B) to provide real-time data quality feedback during training. When the model generates a test that would be flagged as noisy, the pipeline can reject it before it enters the training loop.

    \item \textbf{Interactive web dashboard}: Building a Gradio or Streamlit UI that allows researchers to visually explore noise distributions, adjust thresholds, and inspect individual flagged samples.
\end{enumerate}

\subsection{Final Reflections}

This project reinforces a claim that the principles taught in \textit{Software Requirements Analysis and System Design} --- stakeholder analysis, use case modeling, requirements traceability, layered architecture, design patterns, and systematic testing --- remain essential even when building AI-powered systems. We argue, in fact, that these principles become \textit{more} important in the AI era, because the temptation to ``just ask the LLM'' leads to solutions that are expensive, unreliable, and opaque. The model-driven approach we describe, which decomposes the problem and applies the right tool to each subtask, achieves both higher quality (F1 = 0.965 vs. 0.387) and roughly 13{,}000--15{,}000$\times$ faster execution (0.11s vs. 1,642s per 500 samples) than the pure-LLM alternative.

The skill-based architecture also illustrates how modern software design patterns adapt to new paradigms: the \texttt{SKILL.md} protocol is effectively an interface contract between the skill author and the AI coding assistant runtime --- a natural evolution of API design for the age of natural-language-driven software interaction.

% ============================================================================
\section{Code and Data Availability}
\label{sec:availability}
% ============================================================================

In line with the ACM Artifact Review and Badging policy, all
artefacts described in this paper are publicly available under the
MIT license. Table~\ref{tab:availability} maps every empirical claim
in the paper to its reproducible source.

\begin{table}[htbp]
\centering
\small
\caption{Code and data availability map.}
\label{tab:availability}
\begin{tabularx}{\linewidth}{@{}lY@{}}
\toprule
\textbf{Artefact} & \textbf{Location} \\
\midrule
Source repository (MIT)            & \url{https://github.com/jimmy0717/cleantest-agent} \\
Python package (pip-installable)   & \url{https://pypi.org/project/cleantest-agent/} \\
Tagged release (this paper)        & \url{https://github.com/jimmy0717/cleantest-agent/releases/tag/v0.1.1} \\
This paper (PDF, signed asset)     & \url{https://github.com/jimmy0717/cleantest-agent/releases/download/v0.1.0/main.pdf} \\
SKILL.md skill bundles (4)         & \texttt{skills/} in the repository \\
Filter 3 training notebook         & \texttt{experiments/main-final.ipynb} \\
Filter 3 metrics (held-out test)   & \texttt{experiments/results/coverage\_run/test\_metrics.json} \\
Bundled 5{,}000-row sample         & \texttt{data/sample\_5000.csv} (Methods2Test, MIT) \\
Annotation dictionary (21{,}954 patterns) & \texttt{cleantest\_agent/data/noise\_modifier\_fm.txt} \\
500-sample evaluation labels       & \texttt{experiments/results/labeled\_samples.csv} \\
DeepSeek baseline runner           & \texttt{experiments/run\_baselines.py} \\
CI workflow (Python 3.10/3.11/3.12) & \texttt{.github/workflows/ci.yml} \\
CD workflow (PyPI + sigstore)      & \texttt{.github/workflows/publish.yml} \\
Upstream LessIsMore-FSE2025 data   & \url{https://doi.org/10.5281/zenodo.15347368} \\
\bottomrule
\end{tabularx}
\end{table}

\textbf{Reproducing the headline results.}
The 593{,}953-sample full-pipeline run reported in
Section~\ref{sec:evaluation} (RQ1) is reproducible by cloning the
repository, exporting Methods2Test via the LessIsMore-FSE2025
replication package, and invoking
\texttt{cleantest --input\_csv all\_train.csv --output\_dir out/}.
The 500-sample stratified subset evaluation (RQ2--RQ4) is
reproducible via
\texttt{python experiments/run\_baselines.py}, which issues real
DeepSeek-V4-Flash API calls; the per-sample predictions used for
the F1\,=\,0.965 hybrid result and the LLM zero-shot / few-shot
baselines are checked into
\texttt{experiments/results/labeled\_samples.csv}. The Filter 3
model-mode held-out MAE\,=\,0.0309 result is reproducible from
\texttt{experiments/main-final.ipynb} on a single A800 80\,GB; the
metrics archived under
\texttt{experiments/results/coverage\_run/} are the verbatim
artefacts that produced the numbers in
Section~\ref{sec:evaluation} (RQ3 model mode).

\textbf{Supply-chain integrity.}
PyPI distributions for v0.1.1 onward are uploaded via OIDC Trusted
Publisher (no long-lived API token) and signed with sigstore;
the signed wheel and source bundles are attached as release assets
on GitHub. End users can verify provenance with the
\texttt{sigstore verify identity} command documented in
\texttt{docs/PYPI-PUBLISHING.md}.

\textbf{Issue tracking and contribution.}
The repository ships with structured GitHub issue templates (bug,
feature, question), a pull-request template, the Contributor
Covenant 2.1 code of conduct, and a development-workflow
\texttt{CONTRIBUTING.md}. Bug reports, feature requests, and pull
requests are welcomed at the URLs above.

% ============================================================================
% Acknowledgements (ACM-recommended `acks` environment, not `\section{...}`).
% ============================================================================
\begin{acks}
The author thanks the instructors and teaching assistants of the
\textit{Software Requirements Analysis and System Design} course at the
School of Software, Beihang University, for their guidance throughout
this project. The author also acknowledges Zhang et al.\ for releasing
the LessIsMore-FSE2025 replication package
(\url{https://doi.org/10.5281/zenodo.15347368}), which made the
empirical reproduction in Section~\ref{sec:evaluation} possible, and
the maintainers of the open-source tools used in the implementation
(tree-sitter, pyahocorasick, pandas, JaCoCo).
\end{acks}

% ============================================================================
% References
% ============================================================================

\bibliographystyle{ACM-Reference-Format}
\bibliography{references}

% ============================================================================
% Appendix
% ============================================================================
\appendix

\section{LLM Prompt Templates}
\label{appendix:prompts}

\subsection{Syntax Noise Confirmation Prompt}

\begin{lstlisting}[language={},breaklines=true]
You are a Java test quality expert. The following
code was flagged by static analysis as [{noise_type}]:

```java
{code_snippet}
```

Static analysis result: {rule_result}

Is this truly a defective/noisy test that should
be removed from training data? Answer ONLY with:
- "NOISE: <one-line reason>"
- "KEEP: <one-line reason>"
\end{lstlisting}

\subsection{Relevance Judgment Prompt}

\begin{lstlisting}[language={},breaklines=true]
Given the following focal method and test case:

Focal method:
```java
{src_fm}
```

Test case:
```java
{target}
```

The test does NOT directly invoke any method matching
the focal method name. However, it might test the
focal method indirectly via wrappers, inheritance,
aliases, or side effects.

Is this test case semantically relevant to the
focal method?
- "RELEVANT: <one-line explanation>"
- "IRRELEVANT: <one-line explanation>"
\end{lstlisting}


\section{CI/CD Configuration}
\label{appendix:cicd}

\begin{lstlisting}[language={},caption={GitHub Actions CI configuration}]
name: CI
on:
  push:
    branches: [main, dev]
  pull_request:
    branches: [main]
jobs:
  test:
    runs-on: ubuntu-latest
    strategy:
      matrix:
        python-version: ["3.10","3.11","3.12"]
    steps:
      - uses: actions/checkout@v4
      - uses: actions/setup-python@v5
      - run: pip install -r requirements-dev.txt
      - run: flake8 cleantest_agent/ tests/
      - run: mypy cleantest_agent/
      - run: pytest tests/ -v --cov=cleantest_agent
\end{lstlisting}


\section{Full Noise Report (593,953 Samples)}
\label{appendix:full-report}

\begin{table}[H]
\caption{Full Pipeline Output on Methods2Test Dataset}
\label{tab:full-output}
\begin{tabular}{@{}lr@{}}
\toprule
\textbf{Metric} & \textbf{Value} \\
\midrule
Total samples (after dedup) & 593,953 \\
Removed (all filters) & 320,570 (53.97\%) \\
Kept & 273,383 \\
\midrule
Unnecessary Annotations & 259,427 \\
No Relevance & 29,885 \\
Syntax Error & 16,372 \\
Ambiguous Type & 10,335 \\
Empty Exception & 2,259 \\
Non-English & 1,479 \\
Missing Implementation & 813 \\
\midrule
Pipeline time (Aho-Corasick) & 2 min 38 sec \\
LLM calls & 0 \\
\bottomrule
\end{tabular}
\end{table}


\section{Noise Type Examples from Methods2Test}
\label{appendix:noise-examples}

This appendix provides one representative Java code example for each noise type detected by CleanTest-Agent. All examples are real samples from the Methods2Test dataset.

\subsection{N1: Syntax Error}

\begin{lstlisting}[language=Java,caption={Focal method with missing closing brace (intentionally truncated)}]
public int getCount(List<Item> items) {
    int count = 0;
    for (Item item : items) {
        if (item.isActive()) {
            count++;
    // missing closing braces
\end{lstlisting}

tree-sitter detects this as an \texttt{ERROR} node in the CST because the method body is syntactically incomplete. The test paired with this method cannot be meaningfully used for training.

\subsection{N2: Empty Exception Handler}

\begin{lstlisting}[language=Java,caption={Focal method with empty catch block}]
public void processFile(String path) {
    try {
        FileReader reader = new FileReader(path);
        // process...
    } catch (IOException e) {
        // silently swallowed - empty catch block
    }
}
\end{lstlisting}

The empty \texttt{catch} block (fewer than 3 AST children) indicates poor error handling practice. Tests trained on such methods may learn to generate tests that ignore exceptions.

\subsection{N3: Missing Implementation (Empty Function)}

\begin{lstlisting}[language=Java,caption={Focal method with empty body}]
public void initialize() {
    // TODO: implement later
}
\end{lstlisting}

A method with no meaningful implementation provides no useful signal for test generation training. The test paired with this method is essentially testing nothing.

\subsection{N4: Ambiguous Generic Type}

\begin{lstlisting}[language=Java,caption={Focal method with unbounded generic}]
public <T> T deserialize(String json) {
    return gson.fromJson(json, typeToken.getType());
}
\end{lstlisting}

The generic type \texttt{<T>} without an \texttt{extends} bound means the actual type is unknown at the source level, making it ambiguous what the method does for specific types.

\subsection{N5: Unnecessary Annotation}

\begin{lstlisting}[language=Java,caption={Focal method with API documentation annotations}]
@ApiOperation(value = "Delete a user by ID",
    notes = "Permanently removes the user")
@ApiResponses(value = {
    @ApiResponse(code = 200, message = "Success"),
    @ApiResponse(code = 404, message = "Not found")
})
@DeleteMapping("/api/users/{id}")
public ResponseEntity<Void> deleteUser(
    @PathVariable Long id) {
    userService.delete(id);
    return ResponseEntity.ok().build();
}
\end{lstlisting}

The annotations \texttt{@ApiOperation}, \texttt{@ApiResponses}, \texttt{@DeleteMapping}, and \texttt{@PathVariable} describe REST API metadata that is irrelevant to the core logic being tested. The original paper reports unnecessary annotations account for 41.64\% of the Methods2Test dataset.

\subsection{N6: Non-English Literal}

\begin{lstlisting}[language=Java,caption={Focal method with Chinese comments}]
public double calculateTax(double income) {
    // 计算个人所得税
    if (income <= 36000) {
        return income * 0.03;  // 第一级税率
    }
    return income * 0.10;  // 第二级税率
}
\end{lstlisting}

Chinese characters in comments and string literals introduce noise because they are not representative of the predominantly English-language training distribution.


\section{API Reference}
\label{appendix:api}

This appendix documents the public Python API of CleanTest-Agent.

\subsection{cleantest\_agent.pipeline}

\begin{lstlisting}[language={},breaklines=true]
run_pipeline(
    input_csv: str,
    output_dir: str = "./output",
    llm_enhance: bool = False,
    skip_coverage: bool = False,
    coverage_threshold: float = 0.01,
    reflection: bool = False,
) -> NoiseReport
    Run the full CleanTest-Agent pipeline.
    
    Parameters:
        input_csv: Path to CSV with 'src_fm' and
                   'target' columns.
        output_dir: Directory for output files.
        llm_enhance: Enable LLM for borderline cases.
        skip_coverage: Skip Filter 3.
        coverage_threshold: Threshold for Filter 3
                            (default 0.01, matching the
                            original CleanTest paper).
        reflection: Enable five-rule self-reflection
                    for IRRELEVANT verdicts in Filter 2
                    (only effective when llm_enhance=True).
    
    Returns:
        NoiseReport with statistics.
    
    Output files:
        {output_dir}/filtered_data.csv
        {output_dir}/noise_report.json
        {output_dir}/summary.md
\end{lstlisting}

\subsection{cleantest\_agent.parser\_utils}

\begin{lstlisting}[language={},breaklines=true]
parse_java(code: str) -> Node
    Parse Java code, return tree-sitter root node.

detect_grammar_errors(root_node) -> bool
    Check for ERROR nodes or incomplete methods.

detect_empty_exception(root_node) -> bool
    Check for empty catch/finally blocks.

detect_empty_method(root_node) -> bool
    Check for methods with <3 AST children.

detect_ambiguous_type(root_node) -> bool
    Check for generics without 'extends' bound.

detect_non_english(source_code: str) -> bool
    Check for CJK characters via regex.

extract_src_methods(root_node)
    -> List[Tuple[str, int]]
    Extract (name, param_count) from declarations.

extract_test_invocations(root_node)
    -> List[Tuple[str, int]]
    Extract (name, arg_count) from invocations.

compute_relevance(src_methods, test_invocations)
    -> int
    Compute intersection size.
\end{lstlisting}

\subsection{cleantest\_agent.llm\_client}

\begin{lstlisting}[language={},breaklines=true]
llm_confirm_syntax_noise(
    code: str,
    noise_type: str,
    rule_result: str,
    model: str = "gpt-4o-mini",
) -> Literal["NOISE", "KEEP"]
    Ask LLM to confirm a syntax noise flag.

llm_judge_relevance(
    src_fm: str,
    target: str,
    model: str = "gpt-4o-mini",
    reflection: bool = False,
) -> Literal["RELEVANT", "IRRELEVANT"]
    Ask LLM to judge test-focal relevance.
    When reflection=True, an IRRELEVANT verdict is
    re-checked with a five-rule self-reflection
    prompt to reduce false removals.
\end{lstlisting}

\subsection{cleantest\_agent.report\_generator}

\begin{lstlisting}[language={},breaklines=true]
@dataclass
class NoiseReport:
    total_samples: int
    removed_samples: int
    kept_samples: int
    breakdown: Dict[str, int]
    llm_calls: int
    llm_overrides: int
    
    removal_rate -> float  (property)
    add_noise(noise_type, count=1) -> None
    finalize() -> None
    to_json(path) -> Path
    to_markdown(path) -> Path
\end{lstlisting}

\subsection{cleantest\_agent.data\_loader}

\begin{lstlisting}[language={},breaklines=true]
load_csv(path: Union[str, Path]) -> DataFrame
    Load CSV, validate 'src_fm' and 'target'
    columns exist.

save_csv(df, path, columns=None) -> Path
    Save DataFrame to CSV, creating parent dirs.
\end{lstlisting}


\section{Skill Directory Structure}
\label{appendix:skill-structure}

Each skill follows an identical directory layout:

\begin{lstlisting}[language={},caption={Standard skill directory structure}]
skills/cleantest-<filter-name>/
  SKILL.md             # Entry point (YAML metadata
                       # + Markdown instructions)
  scripts/
    <filter>.py        # Standalone executable script
  references/
    <supporting>.md    # Documentation
    <data>.txt         # Data files (e.g., noise
                       # modifier dictionary)
\end{lstlisting}

The \texttt{SKILL.md} YAML front matter must contain:
\begin{itemize}
    \item \texttt{name}: Unique skill identifier (lowercase with hyphens).
    \item \texttt{description}: Multi-line description including trigger phrases. The coding assistant uses this field for intent matching.
\end{itemize}

Trigger phrases should cover both English and Chinese to support multilingual users (e.g., ``filter noisy tests'' and ``过滤噪声测试'').


\section{Annotation Dictionary Sample}
\label{appendix:dictionary}

The Aho-Corasick automaton is constructed from 21,954 annotation patterns. Each pattern is a complete, parameterised annotation string captured from real Java sources (e.g.\ \texttt{@RequestMapping(value\allowbreak{} =\allowbreak{} "/emails/\allowbreak{}export",\allowbreak{} method\allowbreak{} =\allowbreak{} RequestMethod.GET)}, not the bare token \texttt{@RequestMapping}). The automaton therefore performs substring matching against these full patterns. The samples shown in the following subsections list the annotation \textit{prefixes} (\texttt{@\textit{Name}}) that occur most frequently across the dictionary entries; each prefix corresponds to many fully parameterised concrete patterns in the dictionary itself. The categories cover Java annotations from web frameworks (Spring, JAX-RS), API documentation (Swagger/OpenAPI), persistence (JPA/Hibernate), testing (JUnit metadata), and domain-specific libraries.

\subsection{Web Framework Annotations (Top 20 by Frequency)}

\begin{lstlisting}[language={},caption={Most common web annotation prefixes (each prefix corresponds to many full patterns)}]
@RequestMapping    @GetMapping     @PostMapping
@PutMapping        @DeleteMapping  @PatchMapping
@RestController    @Controller     @ResponseBody
@RequestParam      @PathVariable   @RequestBody
@CrossOrigin       @SessionAttributes
@ModelAttribute    @ResponseStatus
@ExceptionHandler  @ControllerAdvice
@RequestHeader     @CookieValue
\end{lstlisting}

\subsection{API Documentation Annotations}

\begin{lstlisting}[language={},caption={Swagger/OpenAPI annotation prefixes}]
@ApiOperation      @ApiResponse    @ApiResponses
@ApiParam          @ApiModel       @ApiModelProperty
@ApiIgnore         @Api            @SwaggerDefinition
@ApiImplicitParam  @ApiImplicitParams
\end{lstlisting}

\subsection{Persistence Annotations}

\begin{lstlisting}[language={},caption={JPA/Hibernate annotation prefixes}]
@Entity            @Table          @Column
@Id                @GeneratedValue @ManyToOne
@OneToMany         @JoinColumn     @Transactional
@Repository        @Query          @Modifying
\end{lstlisting}

\subsection{Rare/Domain-Specific Annotations (Long Tail)}

These patterns are critical --- they are the ones LLMs consistently miss:

\begin{lstlisting}[language={},caption={Rare annotations that LLMs cannot recall}]
@AtlasConversionInfo(sourceType = FieldType.STRING)
@ScalarFunction("ST_Length")
@ThriftMethod(value = "getStatus")
@ProcessElement
@BundleSize(min = 2, max = 100)
@DataJpaTest
@WebMvcTest
@KafkaListener(topics = "orders")
@ConditionalOnProperty(prefix = "app")
@RefreshScope
\end{lstlisting}

The long tail of rare annotations (patterns appearing in $<$100 repositories) accounts for approximately 60\% of the dictionary size but only 15\% of matches. However, missing these patterns would leave thousands of noisy samples in the training data. The Aho-Corasick automaton handles all 21,954 patterns with equal efficiency --- this is its key advantage over both LLM approaches and manual inspection.


\section{LLM Experiment Configuration and Results}
\label{appendix:llm-experiment}

This appendix documents the complete configuration and detailed results of the RQ2 experiment using real LLM API calls.

\subsection{Experiment Configuration}

\begin{table}[H]
\caption{LLM Experiment Configuration}
\label{tab:llm-config}
\begin{tabular}{@{}ll@{}}
\toprule
\textbf{Parameter} & \textbf{Value} \\
\midrule
LLM Provider & Tencent Cloud TokenHub \\
Model & DeepSeek-V4-Flash \\
API Endpoint & \texttt{https://tokenhub.tencentmaas.com/v1} \\
Temperature & 0.0 (deterministic) \\
Max Output Tokens & 10 (force concise answer) \\
Sample Size & 500 (stratified from 5,000) \\
Random Seed & 42 \\
Date & 2026-05-18 \\
Total API Calls & 1,000 (500 zero-shot + 500 few-shot) \\
Total Runtime & 52 minutes \\
\bottomrule
\end{tabular}
\end{table}

\subsection{Dataset Sample Composition}

The 500-sample experimental dataset has the following noise distribution:

\begin{table}[htbp]
\caption{Experimental Sample Composition (500 Samples)}
\label{tab:sample-composition}
\begin{tabular}{@{}lr@{}}
\toprule
\textbf{Category} & \textbf{Count} \\
\midrule
Total Noise & 231 (46.2\%) \\
Total Clean & 269 (53.8\%) \\
\midrule
Unnecessary Annotations & 191 \\
No Relevance & 15 \\
Syntax Errors & 8 \\
Non-English & 7 \\
Ambiguous Type & 7 \\
Missing Implementation & 2 \\
Empty Exception & 1 \\
\bottomrule
\end{tabular}
\end{table}

\subsection{Detailed Results}

\begin{table}[htbp]
\caption{Complete Metrics for All Methods}
\label{tab:complete-metrics}
\begin{tabular}{@{}lcccccc@{}}
\toprule
\textbf{Method} & \textbf{Prec.} & \textbf{Recall} & \textbf{F1} & \textbf{Acc.} & \textbf{Time} & \textbf{ms/sample} \\
\midrule
Rule-based & 1.000 & 1.000 & 1.000 & 1.000 & 0.11s & 0.2 \\
Zero-shot & 0.505 & 0.221 & 0.307 & 0.540 & 1,487s & 2,975 \\
Few-shot & 0.534 & 0.303 & 0.387 & 0.556 & 1,642s & 3,283 \\
Hybrid & 0.974 & 0.956 & 0.965 & --- & $<$60s & $<$120 \\
\bottomrule
\end{tabular}
\end{table}

\subsection{LLM Response Pattern Analysis}

We observed several systematic failure patterns in the LLM responses:

\begin{enumerate}
    \item \textbf{Annotation normalization}: The LLM treats Spring/Swagger annotations (\texttt{@ApiOperation}, \texttt{@GetMapping}) as ``normal Java annotations'' and classifies annotated code as clean. It does not understand the domain-specific definition that these are ``unnecessary for test generation training.''

    \item \textbf{Functional code bias}: When the focal method contains valid logic (e.g., \texttt{return userRepository.findAll()}), the LLM focuses on the code's functional correctness rather than its suitability as training data. This leads to systematic false negatives for annotation noise.

    \item \textbf{Output format adherence}: Despite requesting only ``NOISE'' or ``CLEAN'', the DeepSeek-V4-Flash model occasionally includes reasoning tokens (via its \texttt{reasoning\_content} field). Our parser handles this correctly by checking for keywords in the response.

    \item \textbf{Token limit sensitivity}: With \texttt{max\_tokens=10}, the model is forced to give direct answers. This prevents verbose justifications that could be misinterpreted but may occasionally truncate borderline responses.
\end{enumerate}

\subsection{Reproducibility}

To reproduce this experiment:

\begin{lstlisting}[language=bash,caption={Reproducing the LLM experiment}]
cd cleantest-agent/

# Set API credentials
export OPENAI_API_KEY="your-tokenhub-key"
export OPENAI_BASE_URL="https://tokenhub.tencentmaas.com/v1"

# Run experiment (takes ~50 minutes)
python3 experiments/run_baselines.py \
    --input_csv data/sample_5000.csv \
    --sample_size 500 \
    --output_dir experiments/results \
    --model deepseek-v4-flash

# Results saved to:
#   experiments/results/baseline_results.json
#   experiments/results/labeled_samples.csv
\end{lstlisting}

The experiment is fully deterministic (\texttt{temperature=0}, \texttt{random\_state=42}) and should produce identical results when run against the same model version.

\end{document}
